### 2017-01-05 paper.tex
Draft of problem setup and proof.

\documentclass[conference]{IEEEtran}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}

\graphicspath{{images/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\interdisplaylinepenalty=2500

% Math commands for matrix and vector fonts
\providecommand{\v}{}
\renewcommand{\v}[1]{\underline{#1}}
\providecommand{\vhat}{}
\renewcommand{\vhat}[1]{\underline{\hat{#1}}}
\providecommand{\m}{}
\renewcommand{\m}[1]{{\bf #1}}
\providecommand{\j}{}
\renewcommand{\j}{\jmath}

% Custom math operators
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\newcommand{\Phiorho}{\Phi\!\circ\!\rho}

\renewcommand*\ttdefault{lmtt}

% Theorems, lemmas, etc.
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}   % Shares numbering with theorem
\newtheorem{definition}{Definition}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\title{Minimax lower bounds for source localization}

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh\IEEEauthorrefmark{1}
		and Pulkit Grover\IEEEauthorrefmark{2}
	}
	\IEEEauthorblockA{
		Electrical \& Computer Engineering,
		and the Center for the Neural Basis of Cognition,
		Carnegie Mellon University \\
		\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
		\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	}
}

\begin{document}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}

The ``source localization'' problem is one that arises in several fields. For
instance, in neuroscience, one might wish to use electroencephalography (EEG)
measurements to locate the source of brain activity.
\textcolor{red}{<Briefly mention other applications>}.

The common underlying factor in each of these problems is the presence of a
point source, whose signal passes through a diffusive medium and is sensed by
an array of sensors. We then wish to recover the location of the source using
noisy sensed values. The diffusive medium is modeled as acting like a low-pass
filter. The noise is taken to be additive gaussian noise \textcolor{red}{which
may have a non-diagonal covariance matrix}.

\textcolor{red}{Rephrase this para.}
We give minimax lower bounds on the squared error in estimating the location of
the source, which applies to all estimators, when using unformly distributed
sensors and for certain classes of impulse response of the low-pass filter. Our
bounds are the first to give a scaling in terms of sensor density.

\end{abstract}

\section{Introduction}

\textcolor{red}{Introduction needs to be re-written.}

Electroencephalograhy (EEG) is a system used to record the electrical activity
of the brain. It is a non-invasive system, which may use anywhere from around
10 to 250 electrodes placed on the scalp, to sense electric potentials. These
potentials are generated by neuronal activity within the
brain~\cite{Buzsaki2012Origin}. These sources of neural activity -- neurons or
groups of neurons -- are usually modeled as current
dipoles~\cite{Nunez2006Electric}.

Often, it is of clinical or scientific interest to reconstruct brain activity
patterns from EEG sensor measurements. This process is what is broadly referred
to when we speak of the term ``source localization''. In this paper, I restrict
the discussion to that of localizing a \emph{single} dipole, and refer to this
process as ``dipole source localization''. Several algorithms for source
localization have been proposed over the years
(see~\cite{Baillet2001Electromagnetic} for an excellent review). However, until
recently, there has been only one work that has theoretically examined the
fundamental limits of source localization accuracy.

Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
for unbiased source localization algorithms. Their work also forms the basis
for setting up the source localization problem and deriving more universally
applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
completely satisfactory answer to the question of fundamental limits for source
localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
estimators (or to estimators of \emph{known} bias). In practice, however, many
popular source localization algorithms have been shown to be biased, for e.g.\
the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
is also known that unbiased estimators can have worse mean-squared-error
performance than biased estimators. So Cramer-Rao bounds are useful only to a
degree, and there may be benefit in deriving bounds that hold for all
estimators.

To this end, Grover~\cite{Grover2016Fundamental} recently proposed a new lower
bound for the error in localizing a single dipole. This bound used techniques
from information theory, for bounding the source localization error by
expressing it in terms of the mutual information across some channel, and then
bounding the mutual information by the capacity of the channel. In deriving
this bound, however, the scalp potential was never sampled; equivalently, it
was assumed that an \emph{infinite} number of sensors was available to sample
the EEG signal at every point on the scalp. Clearly, this is a poor assumption
and could result in a very loose bound, because it allows for more information
to be available at the receiver than otherwise possible. The lower bound also
relies on certain relaxations that allow the dipole to distribute its power in
non-physical ways in frequency domain. This once again makes the bound loose by
assigning the channel a higher capacity than what it could otherwise have.

To address the shortcomings of the Cramer-Rao and information theoretic lower
bounds, I apply two minimax methods to the problem of computing a lower bound
for localization error in the idealized EEG dipole source localization problem.
I briefly review two minimax methods -- Le Cam's, and Fano's local
method~\cite{Duchi2015Information} -- and describe my approach in deriving the
minimax lower bound using each of these for spherical and one-dimensional head
models.

\section{The source localization problem}
\label{sec:source-localization}

We start by giving a detailed description of the one-dimensional setting of the
source localization problem. Recall that, in this problem, we're trying to
determine the location of a point source by observing it through a diffusive
medium using a sensor array.

\subsection{Description of the domain}

We assume that the point source is located on a circle of circumference $T$ (a
circular domain enables us to use symmetry arguments to simplify the proof). We
can view this domain as a line, on which signals are periodic with period $T$.
The point source is therefore located somewhere within one period. We denote
the set of possible locations by $\Theta = [0, T)$. Due to the periodic nature
of the domain, a source located at position $\theta \in \Theta$ implies the
presence of sources at $t = \theta + kT$,~$\forall \, k \in \mathbb Z$.

\subsection{Sensor configuration}

Sensors are assumed to be uniformly distributed over the domain, i.e., if there
are $m$ sensors, they are placed at locations $t = 0$, $T/m$, $2T/m$,~\dots,
$(m{-}1)T/m$ (the offset of the first sensor is arbitrary, so without loss of
generality we take it to be 0). The periodicity of the space ensures that we
automatically also have sensors at $T$, $T{+}T/m$,~\dots\@ The lower bounds we
provide, therefore, are for \emph{this specific sensor configuration}. For a
discussion on why this configuration might be an appropriate choice in the
minimax setting, and on non-uniform sensor placement, see
section~\ref{sec:discussion}.

\subsection{Signal model}
\label{sec:signal-model}

All signals on the aforementioned circular domain are of the form
$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
represented by the impulse signal, $f(t;\theta) = \delta(t - \theta)$, where
$\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
through the diffusive medium, which, intuitively speaking, blurs the impulse.
More concretely, we assume that the medium is linear and shift-invariant, so
that it can be represented by a spatial impulse response (blurring would then
correspond to low-pass filtering). Let this impulse response be given by
$g(t)$. Then, the noiseless, continuous-space signal (post-filtering and
pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
\theta)$. Here, we further make the simplifying assumption that $g(t)$ has
restricted support, so that aliasing effects are avoided, and $x(t; \theta)$ is
always well-defined. To be precise, $g(t) = 0$ when $\abs{t} > w/2$, where the
``width'' $w$ of the impulse response satisfies $w < T / 2$ (the reason for the
factor of $1/2$ will become clear in a later section).

The sensors sample this continuous-space shifted impulse response, with some
additive noise. We denote the noiseless sampled version of $x(t; \theta)$ by
the $m$-length vector $\v x(\theta)$:
\begin{equation} \label{eq:sampled-signal}
	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kT}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)T}{m}; \theta\Big)\bigg]^T
\end{equation}
where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
additive noise is given by $\v \epsilon$ (to be described shortly), and the
noisy samples are represented by $\v y$:
\begin{equation} \label{eq:sensor-obs}
	\v y = \v x(\theta) + \v \epsilon
\end{equation}
The complete signal model described in this section is summarized in
Fig.~\ref{fig:signal-model}.

\subsection{Channel model}
\label{sec:channel-model}

The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is
the only source of uncertainty in the problem. For our purposes, we assume that
$\v \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
\Sigma)$. Two kinds of covariance matrices are of particular interest. The
first is dubbed the ``sensor noise'' setting, wherein $\m\Sigma = \sigma^2 \m
I$, i.e. the sensors are afflicted by i.i.d.\ noise. The second is called the
``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms.
\textcolor{red}{Insert description of source noise.}

With the addition of Gaussian noise, each possible source location $\theta$
gives rise to a different distribution at the sensors, denoted by
\begin{equation} \label{eq:p-theta}
	P(\theta) = \mathcal{N}(\v x(\theta), \m \Sigma).
\end{equation}
$\v y$ is therefore one sample from $P(\theta)$. The space of distributions
produced by all possible source locations is $\mathcal{P} = \{P(\theta) :
\theta \in \Theta \}$. We are interested in computing lower bounds for the loss
function $\Phi(\rho(\theta, \hat\theta)) = \abs{\theta - \hat\theta}^2$, where
$\hat\theta$ is some estimate of the location based on $n$ trials (i.e. $n$
realizations) of the noisy sensor observations $\v y$.

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=3.5in]{block-diagram}
	\caption{A diagramatic representation of the signal model described in
	section~\ref{sec:signal-model}.}
	\label{fig:signal-model}
\end{figure}

\section{Minimax lower bounds for the one-dimensional model}

\subsection{Preliminaries}

We follow the excellent tutorial given in~\cite{Duchi2015Information} to
outline the preliminary steps in deriving bounds on the minimax risk.

Consider the following estimation problem: we have $n$ i.i.d.\ random samples
$Y^n$ from a distribution $P$, which is indexed by a parameter $\theta \in
\Theta$.  Denote the set of these distributions by $\mathcal{P} = \{P(\theta) :
\theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
Define a loss metric $\rho(\theta, \hat\theta)$. For this metric, we can define
the minimax risk over all possible estimators $\hat\theta(Y^n)$ and all
possible $\theta \in \Theta$:
\begin{equation} \label{eq:minimax-expr}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \inf_{\hat\theta} \sup_{\theta \in \Theta} \mathbb E[\Phiorho (\hat\theta(Y^n), \theta)]
\end{equation}
where $\Phi$ is any non-decreasing function (e.g. $\Phi(\rho) = \rho^2$) and
$Y^n$ is the random vector corresponding to a noisy realization of sensor
values.

We start by lower bounding the minimax risk of the estimation problem with the
risk incurred in a multiple hypothesis testing problem. For this, we first need
to define a $2\delta$-packing:%
\begin{definition}
	A set $\Theta_{\mathcal{V}} = \{ \theta_v : v \in \mathcal{V} \}$ for some
	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
	$2\delta$-packing in the $\rho$-metric if $\rho(\theta_i, \theta_j) \geq
	2\delta \, \forall \, \theta_i, \theta_j \in \Theta_{\mathcal{V}}$.
\end{definition}
\begin{theorem} \label{thm:est-to-testing}%
	If we can find a $2\delta$-packing $\Theta_{\mathcal{V}}$ of $\Theta$, then
	we can lower bound the minimax estimation risk by the average testing risk:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) \inf_\psi \mathbb P (\psi(Y^n) \neq V)
	\end{equation}
	where $V$ is the unknown, true hypothesis, and $\psi$ is our estimate of
	the hypothesis.
\end{theorem}
For a proof of this theorem, we refer the reader to Proposition~13.3
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
says that the error in estimating $\theta_i$ is likely to be more if it is
difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
of error is high (where $\theta_j$ has been selected to be suitably close).

We now need to lower bound the probability of error in the hypothesis testing
problem. The simplest way to do this is to consider a binary hypothesis test
($\abs{\mathcal{V}} = 2$) and use what is known as Le Cam's method:
\begin{theorem} \label{thm:le-cam}
	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
	\begin{equation}
		\inf_\psi \mathbb P(\psi(Y^n) \neq V) = 1 - \norm{P_0 - P_1}_{TV}
	\end{equation}
	where $P_i$ is short-hand for $P(\theta_i)$ and $\norm{P_0 - P_1}_{TV}$ is
	the total variation distance between the two distributions, defined as
	$\norm{\cdot}_{TV} = \frac{1}{2} \norm{\cdot}_1$.
\end{theorem}
For a proof, we refer the reader to Proposition~2.11
in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
that the minimum probability of error that any estimator must make in a binary
hypothesis testing problem is related to the distance between the distributions
corresponding to the two hypotheses. The closer the two distributions, the
higher the chance of making an error in distinguishing between them.

Thus, the final lower bound can be written as:
\begin{equation} \label{eq:le-cam-bound}
	\mathfrak{M}_n(\mathcal P, \Phiorho) \geq \frac{\Phi(\delta)}{2} \big(1 - \norm{P_1^n - P_0^n}_{TV}\big)
\end{equation}
The superscripts ``$n$'' remind us that these are $n$-fold product
distributions, since we have $n$ i.i.d. trials used in the estimate.  The
difficulty in Le Cam's method lies in selecting the two hypotheses to trade-off
the effect due to a small value of $\delta$ and a large value of $\norm{P_1^n -
P_0^n}_{TV}$ appropriately, to derive the tightest possible bound.

\subsection{Lower bounds using Le Cam's method}

We now state the main result of this paper.
\begin{theorem}
	For a source localization problem as defined in
	section~\ref{sec:source-localization} with sensor noise and a spatial
	impulse response that is $\kappa$-Lipschitz continuous and has restricted
	support of width $w$, the minimax risk in estimating the location of a
	point source is lower bounded by:
	\begin{equation}
		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
	\end{equation}
\end{theorem}

\begin{IEEEproof}
Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
described in Section~\ref{sec:source-localization}, we proceed to derive the
total variation distance for the distributions of interest. Using Pinsker's
inequality~\cite{Pinsker} and the convenient tensorization of the KL
divergence~\cite{tensorization}, we see that:
\begin{equation} \label{eq:pinsker-tensorization}
	\norm{P_1^n - P_0^n}_{TV} \geq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
\end{equation}
For multivariate normal distributions with the same covariance, the KL
divergence is given by
\begin{equation} \label{eq:kl-div-normal}
	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
\end{equation}
where $\v \mu_0$ and $\v \mu_1$ are the means of the two Gaussians~\cite{KLDivNormal}.

For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
I)$, as described in section~\ref{sec:channel-model}. Hence, combining
equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
\eqref{eq:kl-div-normal}, we see that
\begin{equation} \label{eq:lb-after-pinsker}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
\end{equation}
Let $\v \Delta = \v x(\theta_0) - \v x(\theta_1)$ for brevity. Denoting the
$k$-th component of $\v\Delta$ as $\Delta(k)$, we see that
\begin{align}
	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
\end{align}
where $x(t;\theta_i)$ is the continuous-space filtered signal described in
section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
continuous with parameter $\kappa$, we can upper bound the term within the
summation:
\begin{equation}
	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
\end{equation}
since $\theta_1 = \theta_0 + 2\delta$ (by virtue of the $2\delta$ packing).
Hence,
\begin{equation}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
\end{equation}
$\norm{\v\Delta}_0$ counts the number of non-zero elements in $\v\Delta$, which
is equal to the number of sensors in the total region covered by the signals
$x(t;\theta_0)$ and $x(t;\theta_1)$ (see figures~\ref{fig:overlap-middle} and
\ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
+ 2\delta)m}{T}}$, since at most a fraction $(w + 2\delta) / T$ of sensors can
lie in the region covered by the two impulse responses. The final upper bound
on $\norm{\v\Delta}^2$ is therefore
\begin{equation} \label{eq:delta-bound}
	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T}} \leq 4 \kappa^2 \delta^2 \frac{m (w + 2\delta)}{T}.
\end{equation}
Since sensors are uniformly distributed, and since the domain is periodic, this
holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
e.g.). One part of the signal $x(t;\theta_0)$ will appear at the left edge of
the domain, and the repetition from the period $[T, 2T)$ will appear at the
right edge of the domain. Also note that the two signals $x(t;\theta_0)$ and
$x(t;\theta_1)$ overlap at most once, since $w < T/2$, as stated in
section~\ref{sec:signal-model}.

\begin{figure}[tp] %  figure placement: here, top, bottom, or page
	\centering
	\includegraphics[width=2.8in]{overlap-middle-pics}
	\caption{Depiction of the impulse responses corresponding to two
	hypotheses, $\theta_0$ and $\theta_1$. Note that each impulse response has
a support of size $w$, and the two are separated by a distance $2\delta$. The
total size of the support of the difference signal (subtracting one impulse
response from the other, pointwise) $\Delta(t)$ is therefore at most $w +
2\delta$.}
	\label{fig:overlap-middle}
\end{figure}

The upper bound in equation~\eqref{eq:delta-bound} translates into a lower
bound for equation~\eqref{eq:lb-after-pinsker}:
\begin{align}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n}{2\sigma^2 T} 4 \kappa^2 \delta^2 (w + 2\delta) m} \Bigg] \\
	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2nm \kappa^2 \delta^2 (w + 2\delta)}{\sigma^2 T}} \Bigg] \label{eq:lb-after-delta-bound}
\end{align}

Asymptotically, we choose smaller values of $\delta$ for larger number of
sensors. Hence, neglecting terms of order $\delta^3$, we tighten the bound by
choosing $\delta$ as a function of the remaining variables in order to have
$\sqrt{\frac{2nm\kappa^2\delta^2 }{\sigma^2}} = \frac{1}{2}$. This is achieved
for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2 w}.
\end{equation}
This completes the proof.
\end{IEEEproof}

\section{Discussion}
\label{sec:discussion}

\textcolor{red}{Needs rewrite.}

The reason that the local Fano method gives a poorer bound than Le Cam's method
is that we're using the local Fano method on a bounded domain, making $V$ as a
function of the packing size $\delta$.  It is evident even from examining
equations \eqref{eq:fano-lb} and \eqref{eq:mutual-info-kl-reln} that taking
just two hypotheses with a suitable separation will yield tighter bounds, since
the cardinality of the packing set $V$ will no longer be dependent on $\delta$.
This will allow us to make use of the expression in equation
\eqref{kl-vi-vj-final} to choose $\delta$, which will yield the rate we saw in
Le Cam's method. It is to be seen whether using the global Fano
method~\cite{Duchi2015Information} will improve the rate, or at least, the
constants that we attained with Le Cam's technique. A more rigorous treatment,
which finds an upper bound for the sum, rather than using integrals, so as to
give bounds for even moderate numbers of sensors is also delegated to future
work.

%\IEEEtriggeratref{8}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

\end{document}

### 2017-01-05 paper.tex
Make fixes to caption, add new figure.

@@
 \usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
+%\usepackage{caption}
+%\usepackage{subcaption}
+
+%\captionsetup[figure]{textfont=footnotesize,labelfont=footnotesize}
 
@@
 	impulse response that is $\kappa$-Lipschitz continuous and has restricted
-	support of width $w$, the minimax risk in estimating the location of a
-	point source is lower bounded by:
+	support of width $w$, the asymptotic minimax risk in estimating the
+	location of a point source is lower bounded by:
 	\begin{equation}
@@
 
-\begin{figure}[tp] %  figure placement: here, top, bottom, or page
+\begin{figure}[tbp]
 	\centering
 	\includegraphics[width=2.8in]{overlap-middle-pics}
-	\caption{Depiction of the impulse responses corresponding to two
-	hypotheses, $\theta_0$ and $\theta_1$. Note that each impulse response has
-a support of size $w$, and the two are separated by a distance $2\delta$. The
-total size of the support of the difference signal (subtracting one impulse
-response from the other, pointwise) $\Delta(t)$ is therefore at most $w +
-2\delta$.}
+	\caption{Depiction of the continuous-space signals produced by two
+		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
+		shifted impulse response, and therefore has a support of size $w$.
+		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
+		$\Theta$, so the signals are separated by a distance $2\delta$.}
 	\label{fig:overlap-middle}
+\end{figure}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=2.8in]{delta-sampled-pics}
+	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
+		total size of the support of the difference signal is $w+2\delta$,
+		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
+		$\Delta(k)$ are non-zero.}
+	\label{fig:delta-sampled}
 \end{figure}

### 2017-01-05 src/delta-image/delta-sampled.tex
Make fixes to caption, add new figure.

\documentclass[border=12pt]{standalone}

\usepackage{auto-pst-pdf}
\usepackage{pst-plot}
\usepackage{pstricks-add}

\begin{document}

\begin{pspicture}(-3, -2)(9, 2)
	% x-axis
	\psaxes[yAxis=false,ticks=none,labels=none]{->}(-0.5, 0)(5.5, 0)
	\rput(5.7, 0){$k$}
	\psxTick[linewidth=3\pslinewidth, ticksize=0pt 0pt](0){0}
	\psxTick[linewidth=3\pslinewidth, ticksize=0pt 0pt](1){1}
	\psxTick[linewidth=3\pslinewidth, ticksize=-2pt 2pt](2){2}
	\psxTick[linewidth=3\pslinewidth, ticksize=-2pt 2pt](3){3}
	\psxTick[linewidth=3\pslinewidth, ticksize=0pt 0pt](4){4}
	\psxTick[linewidth=3\pslinewidth, ticksize=-4pt 4pt](5){m}

	% Region before start of signal
	\psplot[plotstyle=dots,plotpoints=5]{0}{0.8}{0}
	% Region with only g_0(t)
	\psplot[plotstyle=dots,linecolor=blue,plotpoints=3]{1.0}{1.4}{x 180 mul cos 1 add 0.5 mul}
	% Overlapping region
	\psplot[plotstyle=dots,linecolor=green,plotpoints=8]{1.6}{3.0}{x 180 mul cos 1 add 0.5 mul x 0.6 sub 180 mul cos 1 add 0.5 mul sub}
	% Region with only g_1(t)
	\psplot[plotstyle=dots,linecolor=red,plotpoints=3]{3.2}{3.6}{x 0.6 sub 180 mul cos 1 add -0.5 mul}
	% Region after end of signal
	\psplot[plotstyle=dots,plotpoints=6]{3.8}{4.8}{0}

	% Tick labels and function annotations
	\rput(1, 0.8){$\Delta(k)$}

	% Width specification
	\pnode(1, -1.2){wll}
	\pnode(1.7, -1.2){wl}
	\ncline{<-}{wll}{wl}
	\ncline{|-}{wll}{wl}
	\pnode(2.9, -1.2){wr}
	\pnode(3.6, -1.2){wrr}
	\ncline{->}{wr}{wrr}
	\ncline{-|}{wr}{wrr}
	\rput(2.3, -1.2){$w+2\delta$}
\end{pspicture}

\end{document}

### 2017-01-08 paper.tex
Fix figure positions; add extensions section.

@@
 estimators (or to estimators of \emph{known} bias). In practice, however, many
-popular source localization algorithms have been shown to be biased, for e.g.\
+popular source localization algorithms have been shown to be biased, e.g.\
 the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
@@
 pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
-\theta)$. Here, we further make the simplifying assumption that $g(t)$ has
-restricted support, so that aliasing effects are avoided, and $x(t; \theta)$ is
-always well-defined. To be precise, $g(t) = 0$ when $\abs{t} > w/2$, where the
-``width'' $w$ of the impulse response satisfies $w < T / 2$ (the reason for the
-factor of $1/2$ will become clear in a later section).
+\theta)$. Here, we further make the simplifying assumption that $g(t)$ has a
+sufficiently restricted support, so that aliasing effects are avoided, and
+$x(t; \theta)$ is always well-defined. To be precise, $g(t) = 0$ when $\abs{t}
+> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < T / 2$
+(the reason for the factor of $1/2$ will become clear in a later section).
 
@@
 \theta \in \Theta\}$. Suppose we now wish to estimate $\theta$ from $Y^n$.
-Define a loss metric $\rho(\theta, \hat\theta)$. For this metric, we can define
-the minimax risk over all possible estimators $\hat\theta(Y^n)$ and all
-possible $\theta \in \Theta$:
+Define a loss metric $\rho(\theta, \hat\theta)$ (e.g.\ $\rho(\theta,
+\hat\theta) = \abs{\theta - \hat\theta}$). For this metric, we can define the
+minimax risk over all possible estimators $\hat\theta(Y^n)$ and all possible
+$\theta \in \Theta$:
 \begin{equation} \label{eq:minimax-expr}
@@
 \end{equation}
-where $\Phi$ is any non-decreasing function (e.g. $\Phi(\rho) = \rho^2$) and
+where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$) and
 $Y^n$ is the random vector corresponding to a noisy realization of sensor
@@
 \begin{theorem} \label{thm:le-cam}
-	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
+	For a binary hypothesis test, i.e., when $\mathcal{V} = \{0, 1\}$,
 	\begin{equation}
@@
 total variation distance for the distributions of interest. Using Pinsker's
-inequality~\cite{Pinsker} and the convenient tensorization of the KL
-divergence~\cite{tensorization}, we see that:
+inequality~\cite{Pinsker} and the convenient tensorization of the
+KL-divergence~\cite{tensorization}, we see that:
 \begin{equation} \label{eq:pinsker-tensorization}
-	\norm{P_1^n - P_0^n}_{TV} \geq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
+	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
 \end{equation}
-For multivariate normal distributions with the same covariance, the KL
-divergence is given by
+For multivariate normal distributions with the same covariance, the
+KL-divergence is given by
 \begin{equation} \label{eq:kl-div-normal}
@@
 \end{equation}
-where $\v \mu_0$ and $\v \mu_1$ are the means of the two Gaussians~\cite{KLDivNormal}.
+where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
+respectively~\cite{KLDivNormal}.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=2.8in]{overlap-middle-pics}
+	\caption{Depiction of the continuous-space signals produced by two
+		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
+		shifted impulse response, and therefore has a support of size $w$.
+		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
+		$\Theta$, so the signals are separated by a distance $2\delta$.}
+	\label{fig:overlap-middle}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=2.8in]{delta-sampled-pics}
+	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
+		total size of the support of the difference signal is $w+2\delta$,
+		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
+		$\Delta(k)$ are non-zero.}
+	\label{fig:delta-sampled}
+\end{figure}
 
@@
 \end{equation}
-Let $\v \Delta = \v x(\theta_0) - \v x(\theta_1)$ for brevity. Denoting the
-$k$-th component of $\v\Delta$ as $\Delta(k)$, we see that
+Let $\v \Delta \overset{\text{def.}}{=} \v x(\theta_0) - \v x(\theta_1)$ for
+brevity. Also, let $\Delta(k)$ denote the $k$-th element of $\v\Delta$, and
+$\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
+(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
 \begin{align}
@@
 \end{equation}
-since $\theta_1 = \theta_0 + 2\delta$ (by virtue of the $2\delta$ packing).
+since $\abs{\theta_0 - \theta_1} = 2\delta$ by virtue of the $2\delta$ packing.
 Hence,
@@
 \end{equation}
-$\norm{\v\Delta}_0$ counts the number of non-zero elements in $\v\Delta$, which
-is equal to the number of sensors in the total region covered by the signals
-$x(t;\theta_0)$ and $x(t;\theta_1)$ (see figures~\ref{fig:overlap-middle} and
+$\norm{\v\Delta}_0$ is the number of non-zero elements in $\v\Delta$, which is
+equal to the number of sensors in the total region covered by the signals
+$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
 \ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
-+ 2\delta)m}{T}}$, since at most a fraction $(w + 2\delta) / T$ of sensors can
-lie in the region covered by the two impulse responses. The final upper bound
-on $\norm{\v\Delta}^2$ is therefore
++ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
+sensors (plus 1, to account for edge-effects) can lie in the region covered by
+the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
+hence
 \begin{equation} \label{eq:delta-bound}
-	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T}} \leq 4 \kappa^2 \delta^2 \frac{m (w + 2\delta)}{T}.
+	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
 \end{equation}
@@
 holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
-e.g.). One part of the signal $x(t;\theta_0)$ will appear at the left edge of
-the domain, and the repetition from the period $[T, 2T)$ will appear at the
-right edge of the domain. Also note that the two signals $x(t;\theta_0)$ and
-$x(t;\theta_1)$ overlap at most once, since $w < T/2$, as stated in
-section~\ref{sec:signal-model}.
+example). In such a case, one part of the signal $x(t;\theta_0)$ will appear at
+the left edge of the domain, and the repetition from the period $[T, 2T)$ will
+appear at the right edge of the domain. Also note that the two signals
+$x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most once, since $w < T/2$, as
+stated in section~\ref{sec:signal-model}.
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=2.8in]{overlap-middle-pics}
-	\caption{Depiction of the continuous-space signals produced by two
-		hypotheses, $\theta_0$ and $\theta_1$. Note that each signal is a
-		shifted impulse response, and therefore has a support of size $w$.
-		The set $\{\theta_0, \theta_1\}$ is a $2\delta$-packing of
-		$\Theta$, so the signals are separated by a distance $2\delta$.}
-	\label{fig:overlap-middle}
-\end{figure}
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=2.8in]{delta-sampled-pics}
-	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
-		total size of the support of the difference signal is $w+2\delta$,
-		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
-		$\Delta(k)$ are non-zero.}
-	\label{fig:delta-sampled}
-\end{figure}
-
-The upper bound in equation~\eqref{eq:delta-bound} translates into a lower
-bound for equation~\eqref{eq:lb-after-pinsker}:
+The upper bound in~\eqref{eq:delta-bound} translates into a lower
+bound for~\eqref{eq:lb-after-pinsker}:
 \begin{align}
@@
 \end{align}
-
 Asymptotically, we choose smaller values of $\delta$ for larger number of
@@
 choosing $\delta$ as a function of the remaining variables in order to have
-$\sqrt{\frac{2nm\kappa^2\delta^2 }{\sigma^2}} = \frac{1}{2}$. This is achieved
-for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
+$\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} = \frac{1}{2}$. This is
+achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
 $\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
@@
 \end{IEEEproof}
+
+\section{Extensions}
+
+\subsection{Linear domain (in place of a circle)}
+
+So far, we've relied on the presence of a circular domain for to make the
+arguments in the proof. However, the most important requirement was that
+\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
+So, if $\theta$ were restricted to the region $[0, T)$ (now on a linear,
+non-periodic domain), and if sensors were available to sense the signal from
+$[-w/2, T{+}w/2)$ (for an impulse response with restricted support as described
+in section~\ref{sec:signal-model}), then the proof for sensor noise would still
+fall through, albeit with slightly different constants.
+
+\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}
+
+We can trivially expand the domain of impulse responses to which the lower
+bound applies to include $\alpha$-Holder continuous functions. These are
+functions which satisfy
+\begin{equation}
+	\abs{g(u) - g(v)} \leq \kappa \norm{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
+\end{equation}
+for some constant $\kappa$, and for $\alpha > 0$.
+
+\subsection{From a one-dimensional domain to a $d$-dimensional domain}
+
+Another simple extension takes our problem from a one-dimensional setting to a
+$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
+$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
+\vhat\theta}^2$. Then, using Assouad's method~\cite{Duchi2015Information}, we
+can split the minimax risk along each of the $d$ dimensions, and bound each
+separately using Le Cam's method.
 

### 2017-01-10 paper.tex
Add first draft of introduction.

@@
 \usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
+
+\urlstyle{tt}
+
 %\usepackage{caption}
@@
 
-\textcolor{red}{Introduction needs to be re-written.}
+%- The source localization problem is one that occurs in several fields
+%  - Brain activity measurement, in the form of localizing brain activity
+%    - Possible applications are epilepsy focus localization
+%    - Neuroscientific experiments - locating the source of activity at certain
+%      points in time, for understanding brain function
+%  - Need to read Vetterli's papers on acoustic source localization-type things
+%  - Need to read up linear inverse problems literature
 
-Electroencephalograhy (EEG) is a system used to record the electrical activity
-of the brain. It is a non-invasive system, which may use anywhere from around
-10 to 250 electrodes placed on the scalp, to sense electric potentials. These
-potentials are generated by neuronal activity within the
-brain~\cite{Buzsaki2012Origin}. These sources of neural activity -- neurons or
-groups of neurons -- are usually modeled as current
-dipoles~\cite{Nunez2006Electric}.
+%- Previous work
+%  - In the brain activity localization side of things, lots of algorithms, but
+%    not much understanding of bounds (Mosher, Grover).
+%    - These have their own issues: CRLB does not apply to all estimators, info
+%      theoretic bound does not give scaling with sensors
+%  - Other work on minimax bounds and estimators for linear inverse problems
+%    concentrate on function estimation (with smoothness constraints on the
+%    function being estimated)
+%    - e.g. Tsybakov, Efromovich, Ibragimov \& Has'minskii, and references
+%      therein
+%    - Obviously, bounds for function estimation will look radically different
+%      from bounds for a location parameter
+%    - Location-parameter based work appears to exist in Ibragimov-Has'minskii,
+%      but they treat it as an exercise, without seriously considering
+%      extensions, and looking at scaling with number of sensors
 
-Often, it is of clinical or scientific interest to reconstruct brain activity
-patterns from EEG sensor measurements. This process is what is broadly referred
-to when we speak of the term ``source localization''. In this paper, I restrict
-the discussion to that of localizing a \emph{single} dipole, and refer to this
-process as ``dipole source localization''. Several algorithms for source
-localization have been proposed over the years
-(see~\cite{Baillet2001Electromagnetic} for an excellent review). However, until
-recently, there has been only one work that has theoretically examined the
-fundamental limits of source localization accuracy.
+%- Cite Fisher's book on circular domain signals somewhere (statistical analysis
+%  of circular data)
 
-Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
-for unbiased source localization algorithms. Their work also forms the basis
-for setting up the source localization problem and deriving more universally
-applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
-completely satisfactory answer to the question of fundamental limits for source
-localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
-estimators (or to estimators of \emph{known} bias). In practice, however, many
-popular source localization algorithms have been shown to be biased, e.g.\
-the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
-bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
-is also known that unbiased estimators can have worse mean-squared-error
-performance than biased estimators. So Cramer-Rao bounds are useful only to a
-degree, and there may be benefit in deriving bounds that hold for all
-estimators.
+The source localization problem is one that appears in many fields where it is
+of interest to find the position of a source (which emits some kind of signal)
+using an array of sensors.
 
-To this end, Grover~\cite{Grover2016Fundamental} recently proposed a new lower
-bound for the error in localizing a single dipole. This bound used techniques
-from information theory, for bounding the source localization error by
-expressing it in terms of the mutual information across some channel, and then
-bounding the mutual information by the capacity of the channel. In deriving
-this bound, however, the scalp potential was never sampled; equivalently, it
-was assumed that an \emph{infinite} number of sensors was available to sample
-the EEG signal at every point on the scalp. Clearly, this is a poor assumption
-and could result in a very loose bound, because it allows for more information
-to be available at the receiver than otherwise possible. The lower bound also
-relies on certain relaxations that allow the dipole to distribute its power in
-non-physical ways in frequency domain. This once again makes the bound loose by
-assigning the channel a higher capacity than what it could otherwise have.
+Our principal motivation comes from an application in brain activity
+measurement, where one wishes to use modalities such as electroencephalography
+(EEG) and magnetoencephalography (MEG) to record the activity inside the
+brain~\cite{Baillet2001Electromagnetic}.  For example, current EEG systems use
+anywhere between 10 and 250 sensors (electrodes), placed on the scalp, to sense
+electric potentials produced by neuronal activity within the
+brain~\cite{Nunez2006Electric}.
 
-To address the shortcomings of the Cramer-Rao and information theoretic lower
-bounds, I apply two minimax methods to the problem of computing a lower bound
-for localization error in the idealized EEG dipole source localization problem.
-I briefly review two minimax methods -- Le Cam's, and Fano's local
-method~\cite{Duchi2015Information} -- and describe my approach in deriving the
-minimax lower bound using each of these for spherical and one-dimensional head
-models.
+Recent developments~\cite{Grover2016Information} have suggested that source
+localization can benefit greatly from an increase in sensor density. This
+conclusion is based primarily on a Nyquist rate analysis, and on
+information-theoretic bounds (which are possibly very loose) on the accuracy of
+source localization algorithms. These bounds, first derived
+in~\cite{Grover2016Fundamental}, do not capture scaling in number of sensors,
+however, as the derivation effectively assumes the presence of an infinite
+number of sensors to derive the bound.
+
+Earlier work by Mosher et al.~\cite{Mosher1993Error}, which seeks to address
+this issue by deriving Cramer-Rao lower bounds, is also not completely
+satisfactory because these bounds do not apply to biased estimators. Commonly
+used source localization algorithms (such as the Minimum Norm
+Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are known to be
+biased~\cite{Lin2006Assessing}.
+
+This paper seeks to address the shortcomings of earlier methods by deriving
+minimax lower bounds for the source localization problem, which apply to
+\emph{all} estimators (biased \emph{and} unbiased), and which can give a
+scaling in terms of the number of sensors used (for a fixed sensor placement
+configuration). Computing the lower bound for the ``real brain model'' (where
+the complete geometry of the brain surface is accounted for) is rendered very
+difficult since analytical solutions for the EEG signal, given the brain
+activity, do not exist. ``Spherical head
+models''~\cite{Nunez2006Electric,Grover2016Information} \emph{do} have
+analytical solutions, but are still not easily amenable to analytical lower
+bounds because the spherical surface does not permit uniform
+sampling~\cite{ImpossibilityOfSphereSampling}, and because the solution is
+expressed in terms of special functions. We therefore restrict our analysis to
+a source localization problem on a one-dimensional domain (to be described in
+detail in Section~\ref{sec:source-localization}).
+
+The one-dimensional toy problem is an effective tool for understanding bounds
+on source localization accuracy in other settings as well, such as
+\textcolor{red}{<insert other applications>}. A vast literature on linear
+inverse problems (refer~\cite{Bal2012Introduction} for an introduction to this
+field) and deconvolution algorithms exists, and has addressed the reduced
+one-dimensional problem in broad settings
+(see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
+references therein). However, our setting and interpretation appears to be
+unique, since most prior work focuses on recovering a whole function (given
+certain smoothness constraints), rather than locating a point source. Work that
+does address point sources, to our knowledge, does not address scaling in the
+number of sensors, since their problem setting and application is very
+different.
+
+Hence, we believe that this paper is the first to give lower bounds on source
+localization error (measured in an $ell_2$-distance sense) in estimating the
+location of a one-dimensional point source, which is observed by sensors
+through a diffusive medium (treated as a low-pass filter), and corrupted by
+additive Gaussian noise. We describe the problem setting in detail in
+Section~\ref{sec:source-localization}, describe the minimax technique used and
+give our main result in Section~\ref{sec:minimax-lower-bounds}, describe a few
+straightforward extensions in Section~\ref{sec:extensions}, and conclude with a
+discussion on implications for sensor placement and future work in
+Section~\ref{sec:discussion}.
+
+%\textcolor{red}{Introduction needs to be re-written.}
+
+%Electroencephalograhy (EEG) is a system used to record the electrical activity
+%of the brain. It is a non-invasive system, which may use anywhere from around
+%10 to 250 electrodes placed on the scalp, to sense electric potentials. These
+%potentials are generated by neuronal activity within the
+%brain~\cite{Buzsaki2012Origin}. These sources of neural activity -- neurons or
+%groups of neurons -- are usually modeled as current
+%dipoles~\cite{Nunez2006Electric}.
+
+%Often, it is of clinical or scientific interest to reconstruct brain activity
+%patterns from EEG sensor measurements. This process is what is broadly referred
+%to when we speak of the term ``source localization''. In this paper, I restrict
+%the discussion to that of localizing a \emph{single} dipole, and refer to this
+%process as ``dipole source localization''. Several algorithms for source
+%localization have been proposed over the years
+%(see~\cite{Baillet2001Electromagnetic} for an excellent review). However, until
+%recently, there has been only one work that has theoretically examined the
+%fundamental limits of source localization accuracy.
+
+%Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
+%for unbiased source localization algorithms. Their work also forms the basis
+%for setting up the source localization problem and deriving more universally
+%applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
+%completely satisfactory answer to the question of fundamental limits for source
+%localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
+%estimators (or to estimators of \emph{known} bias). In practice, however, many
+%popular source localization algorithms have been shown to be biased, e.g.\
+%the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
+%bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
+%is also known that unbiased estimators can have worse mean-squared-error
+%performance than biased estimators. So Cramer-Rao bounds are useful only to a
+%degree, and there may be benefit in deriving bounds that hold for all
+%estimators.
+
+%To this end, Grover~\cite{Grover2016Fundamental} recently proposed a new lower
+%bound for the error in localizing a single dipole. This bound used techniques
+%from information theory, for bounding the source localization error by
+%expressing it in terms of the mutual information across some channel, and then
+%bounding the mutual information by the capacity of the channel. In deriving
+%this bound, however, the scalp potential was never sampled; equivalently, it
+%was assumed that an \emph{infinite} number of sensors was available to sample
+%the EEG signal at every point on the scalp. Clearly, this is a poor assumption
+%and could result in a very loose bound, because it allows for more information
+%to be available at the receiver than otherwise possible. The lower bound also
+%relies on certain relaxations that allow the dipole to distribute its power in
+%non-physical ways in frequency domain. This once again makes the bound loose by
+%assigning the channel a higher capacity than what it could otherwise have.
+
+%To address the shortcomings of the Cramer-Rao and information theoretic lower
+%bounds, I apply two minimax methods to the problem of computing a lower bound
+%for localization error in the idealized EEG dipole source localization problem.
+%I briefly review two minimax methods -- Le Cam's, and Fano's local
+%method~\cite{Duchi2015Information} -- and describe my approach in deriving the
+%minimax lower bound using each of these for spherical and one-dimensional head
+%models.
 
@@
 \section{Minimax lower bounds for the one-dimensional model}
+\label{sec:minimax-lower-bounds}
 
@@
 \section{Extensions}
+\label{sec:extensions}
 
-\subsection{Linear domain (in place of a circle)}
+\subsection{From a circular (periodic) domain to a linear (aperiodic) domain}
 
@@
 $\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
-\vhat\theta}^2$. Then, using Assouad's method~\cite{Duchi2015Information}, we
-can split the minimax risk along each of the $d$ dimensions, and bound each
-separately using Le Cam's method.
+\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov} in the manner
+described in~\cite{Duchi2015Information}, we can split the minimax risk
+along each of the $d$ dimensions, and bound each separately using Le Cam's
+method.
 

### 2017-01-10 paper.tex
Add missing references.

@@
 \usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
-
-\urlstyle{tt}
 
@@
 bounds because the spherical surface does not permit uniform
-sampling~\cite{ImpossibilityOfSphereSampling}, and because the solution is
-expressed in terms of special functions. We therefore restrict our analysis to
-a source localization problem on a one-dimensional domain (to be described in
-detail in Section~\ref{sec:source-localization}).
+sampling~\cite{Heath1956Thirteen}, and because the solution is expressed in
+terms of special functions. We therefore restrict our analysis to a source
+localization problem on a one-dimensional domain (to be described in detail in
+Section~\ref{sec:source-localization}).
 
@@
 total variation distance for the distributions of interest. Using Pinsker's
-inequality~\cite{Pinsker} and the convenient tensorization of the
-KL-divergence~\cite{tensorization}, we see that:
+inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
+KL-divergence~\cite{Duchi2015Information}, we see that:
 \begin{equation} \label{eq:pinsker-tensorization}
@@
 where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
-respectively~\cite{KLDivNormal}.
+respectively~\cite{DuchiDerivation}.
 
@@
 $\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
-\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov} in the manner
-described in~\cite{Duchi2015Information}, we can split the minimax risk
-along each of the $d$ dimensions, and bound each separately using Le Cam's
+\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
+the manner described in~\cite{Duchi2015Information}, we can split the minimax
+risk along each of the $d$ dimensions, and bound each separately using Le Cam's
 method.

### 2017-01-11 paper.tex
Add discussions; edit intro; fix +1 issue.

@@
 The source localization problem is one that appears in many fields where it is
-of interest to find the position of a source (which emits some kind of signal)
-using an array of sensors.
+of interest to find the position of a source using an array of sensors.
 
@@
 measurement, where one wishes to use modalities such as electroencephalography
-(EEG) and magnetoencephalography (MEG) to record the activity inside the
+(EEG) and magnetoencephalography (MEG) to record activity inside the
 brain~\cite{Baillet2001Electromagnetic}.  For example, current EEG systems use
-anywhere between 10 and 250 sensors (electrodes), placed on the scalp, to sense
+anywhere between 10 and 250 sensors (electrodes) placed on the scalp, to sense
 electric potentials produced by neuronal activity within the
-brain~\cite{Nunez2006Electric}.
+brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
+produce this activity are frequently modeled as current dipoles. For a single
+activated dipole within the brain (which is modeled as being localized to a
+point), the electrodes effectively sense a diffuse (blurred-out) representation
+of the point source, as a result of the spatial low-pass filtering effect of
+the different layers between the brain surface and scalp surface (cerebrospinal
+fluid, skull and skin).
 
@@
 localization can benefit greatly from an increase in sensor density. This
-conclusion is based primarily on a Nyquist rate analysis, and on
-information-theoretic bounds (which are possibly very loose) on the accuracy of
-source localization algorithms. These bounds, first derived
-in~\cite{Grover2016Fundamental}, do not capture scaling in number of sensors,
-however, as the derivation effectively assumes the presence of an infinite
-number of sensors to derive the bound.
+conclusion is based primarily on a Nyquist rate analysis, and on an
+information-theoretic bound (which are possibly very loose) on the accuracy of
+source localization algorithms. In deriving this bound, however, the scalp
+potential was never sampled; equivalently, it was assumed that an
+\emph{infinite} number of sensors was available to sample the EEG signal at
+every point on the scalp. Hence, the dependence of the bound on the number of
+sensors is lost.
 
@@
 used source localization algorithms (such as the Minimum Norm
-Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are known to be
-biased~\cite{Lin2006Assessing}.
+Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
+to be biased~\cite{Lin2006Assessing}.
 
@@
 \textcolor{red}{<insert other applications>}. A vast literature on linear
-inverse problems (refer~\cite{Bal2012Introduction} for an introduction to this
+inverse problems (see~\cite{Bal2012Introduction} for an introduction to this
 field) and deconvolution algorithms exists, and has addressed the reduced
@@
 does address point sources, to our knowledge, does not address scaling in the
-number of sensors, since their problem setting and application is very
-different.
+number of sensors, since problem settings and applications differ greatly.
 
 Hence, we believe that this paper is the first to give lower bounds on source
-localization error (measured in an $ell_2$-distance sense) in estimating the
+localization error (measured in an $\ell_2$-distance sense) in estimating the
 location of a one-dimensional point source, which is observed by sensors
@@
 additive Gaussian noise. We describe the problem setting in detail in
-Section~\ref{sec:source-localization}, describe the minimax technique used and
-give our main result in Section~\ref{sec:minimax-lower-bounds}, describe a few
-straightforward extensions in Section~\ref{sec:extensions}, and conclude with a
+Section~\ref{sec:source-localization}, the minimax techniques and our main
+result in Section~\ref{sec:minimax-lower-bounds} and a few straightforward
+extensions in Section~\ref{sec:extensions}. Finally, we conclude with a
 discussion on implications for sensor placement and future work in
@@
 
-We follow the excellent tutorial given in~\cite{Duchi2015Information} to
-outline the preliminary steps in deriving bounds on the minimax risk.
+\textcolor{blue}{
+Several techniques for deriving lower bounds on the minimax risk are described
+in~\cite{Tsybakov2009Introduction}. We follow the excellent tutorial written by
+John Duchi~\cite{Duchi2015Information} to briefly outline the steps involved in
+deriving these bounds.
+}
 
@@
 	finite index set $\mathcal{V} \subset \mathbb N$ is said to be a
-	$2\delta$-packing in the $\rho$-metric if $\rho(\theta_i, \theta_j) \geq
-	2\delta \, \forall \, \theta_i, \theta_j \in \Theta_{\mathcal{V}}$.
+	$2\delta$-packing in the $\rho$-metric if
+	\begin{equation}
+		\rho(\theta_i, \theta_j) \geq 2\delta \qquad \forall \;\; \theta_i, \theta_j \in \Theta_{\mathcal{V}}.
+	\end{equation}
 \end{definition}
@@
 We now state the main result of this paper.
-\begin{theorem}
+\begin{theorem} \label{thm:main-lb}
 	For a source localization problem as defined in
@@
 	impulse response that is $\kappa$-Lipschitz continuous and has restricted
-	support of width $w$, the asymptotic minimax risk in estimating the
+	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
 	location of a point source is lower bounded by:
-	\begin{equation}
+	\begin{equation} \label{eq:main-lower-bound}
 		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
@@
 + 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
-sensors (plus 1, to account for edge-effects) can lie in the region covered by
+sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
 the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
@@
 holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
-example). In such a case, one part of the signal $x(t;\theta_0)$ will appear at
-the left edge of the domain, and the repetition from the period $[T, 2T)$ will
-appear at the right edge of the domain. Also note that the two signals
-$x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most once, since $w < T/2$, as
-stated in section~\ref{sec:signal-model}.
+example). \textcolor{blue}{In such a case, one part of the signal $x(t;\theta_0)$ will appear at
+the left edge of the domain, and the remaining part will appear as the
+repetition from the period $[T, 2T)$, at the right edge of the domain.} Also
+note that the two signals $x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most
+once, since $w < T/2$, as stated in section~\ref{sec:signal-model}.
 
@@
 \begin{align}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n}{2\sigma^2 T} 4 \kappa^2 \delta^2 (w + 2\delta) m} \Bigg] \\
-	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2nm \kappa^2 \delta^2 (w + 2\delta)}{\sigma^2 T}} \Bigg] \label{eq:lb-after-delta-bound}
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \\
+	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
 \end{align}
-Asymptotically, we choose smaller values of $\delta$ for larger number of
-sensors. Hence, neglecting terms of order $\delta^3$, we tighten the bound by
-choosing $\delta$ as a function of the remaining variables in order to have
-$\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} = \frac{1}{2}$. This is
-achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2 w}}$, so that for
-$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
+Asymptotically, we choose smaller values of $\delta$ as the number of sensors
+grows large. Hence, \textcolor{blue}{neglecting edge effects} and terms of order $\delta^3$, we
+tighten the bound by choosing $\delta$ as a function of the remaining variables
+in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} =
+\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2
+w}}$, so that for $\Phi(\delta) = \delta^2$,
+equation~\eqref{eq:lb-after-delta-bound} becomes
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2 w}.
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 T}{nm\kappa^2 w}.
 \end{equation}
@@
 We can trivially expand the domain of impulse responses to which the lower
-bound applies to include $\alpha$-Holder continuous functions. These are
-functions which satisfy
+bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
+continuous functions. These are functions which satisfy
 \begin{equation}
-	\abs{g(u) - g(v)} \leq \kappa \norm{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
+	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
 \end{equation}
-for some constant $\kappa$, and for $\alpha > 0$.
+for some constant $\kappa$, and for $\alpha > 0$. Using this property,
+equation~\eqref{eq:delta-bound} reads
+\begin{equation} \label{eq:holder-delta-bound}
+	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{T} + 1\bigg).
+\end{equation}
+Hence, we choose $\delta = (\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
+w})^{1/2\alpha}$, to procure an asymptotic lower bound
+\begin{equation}
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
+w}\bigg)^{1/\alpha}.
+\end{equation}
 
@@
 
-\textcolor{red}{Needs rewrite.}
+The lower bound given by Theorem~\ref{thm:main-lb} goes to zero as the number
+of sensors, $m$, goes to infinity, \emph{even if} the total number of trials
+$n$ is kept \emph{fixed}. This would mean that a high sensor density can
+overcome the effect of noise in a single trial. The reason this happens is that
+we assume sensors are affected by i.i.d. noise, no matter what sampling density
+we use. This is an increasingly poor assumption as sensor density increases,
+however; we expect noise to become correlated if sensors are extremely close
+(due to inductive/capacitive coupling, for example). A more realistic lower
+bound will show the benefit of increasing sensor density up to a point only,
+beyond which it will have to scale alongside the number of trials.
 
-The reason that the local Fano method gives a poorer bound than Le Cam's method
-is that we're using the local Fano method on a bounded domain, making $V$ as a
-function of the packing size $\delta$.  It is evident even from examining
-equations \eqref{eq:fano-lb} and \eqref{eq:mutual-info-kl-reln} that taking
-just two hypotheses with a suitable separation will yield tighter bounds, since
-the cardinality of the packing set $V$ will no longer be dependent on $\delta$.
-This will allow us to make use of the expression in equation
-\eqref{kl-vi-vj-final} to choose $\delta$, which will yield the rate we saw in
-Le Cam's method. It is to be seen whether using the global Fano
-method~\cite{Duchi2015Information} will improve the rate, or at least, the
-constants that we attained with Le Cam's technique. A more rigorous treatment,
-which finds an upper bound for the sum, rather than using integrals, so as to
-give bounds for even moderate numbers of sensors is also delegated to future
-work.
+The lower bounding \emph{technique} gives certain inisights on the issue of
+sensor placement. Suppose we wanted to achieve a higher resolution in a
+restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
+\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
+to place sensors \emph{not} precisely over the region, but rather in the region
+corresponding to the \emph{largest change} in the impulse response. Indeed, it
+is possible to derive an  approximate lower bound using Taylor's approximation,
+which shows that the KL-divergence between distributions is maximized (and
+hence error minimized) at regions where the slope of $x(t;\theta)$ is largest.
+
+Another point on sensor placement bears repeating: the bounds derived in this
+paper apply to only a specific sensor configuration, i.e., the uniform one.
+This would intuitively seem to be an appropriate choice in the minimax setting,
+however, since any non-uniform placement will have one or more points which is
+far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
+select such a point, where the value of the impulse response so produced at the
+sensors is smallest, so that SNR is minimized.
+
+For the application of EEG source localization, it might be possible to find
+algorithms which achieve similar scalings as the lower bounds presented here.
+It is also hoped that the techniques presented here will help us derive
+analytical bounds in the more difficult setting.
+
+\section*{Acknowledgements}
+
+Praveen Venkatesh is partially supported by the Dowd Fellowship from the
+College of Engineering at Carnegie Mellon University. The authors would like to
+thank Philip and Marsha Dowd for their support and encouragement.
 

### 2017-01-18 paper.tex
Replace `t` by `s` in text.

@@
 
-We assume that the point source is located on a circle of circumference $T$ (a
+We assume that the point source is located on a circle of circumference $S$ (a
 circular domain enables us to use symmetry arguments to simplify the proof). We
-can view this domain as a line, on which signals are periodic with period $T$.
+can view this domain as a line, on which signals are periodic with period $S$.
 The point source is therefore located somewhere within one period. We denote
-the set of possible locations by $\Theta = [0, T)$. Due to the periodic nature
+the set of possible locations by $\Theta = [0, S)$. Due to the periodic nature
 of the domain, a source located at position $\theta \in \Theta$ implies the
-presence of sources at $t = \theta + kT$,~$\forall \, k \in \mathbb Z$.
+presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.
 
@@
 Sensors are assumed to be uniformly distributed over the domain, i.e., if there
-are $m$ sensors, they are placed at locations $t = 0$, $T/m$, $2T/m$,~\dots,
-$(m{-}1)T/m$ (the offset of the first sensor is arbitrary, so without loss of
+are $m$ sensors, they are placed at locations $s = 0$, $S/m$, $2S/m$,~\dots,
+$(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
 generality we take it to be 0). The periodicity of the space ensures that we
-automatically also have sensors at $T$, $T{+}T/m$,~\dots\@ The lower bounds we
+automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
 provide, therefore, are for \emph{this specific sensor configuration}. For a
@@
 $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
-represented by the impulse signal, $f(t;\theta) = \delta(t - \theta)$, where
+represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
 $\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
@@
 correspond to low-pass filtering). Let this impulse response be given by
-$g(t)$. Then, the noiseless, continuous-space signal (post-filtering and
-pre-sampling) is given by the convolution, $x(t; \theta) = (g*f)(t) = g(t -
-\theta)$. Here, we further make the simplifying assumption that $g(t)$ has a
+$g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
+pre-sampling) is given by the convolution, $x(s; \theta) = (g*f)(s) = g(s -
+\theta)$. Here, we further make the simplifying assumption that $g(s)$ has a
 sufficiently restricted support, so that aliasing effects are avoided, and
-$x(t; \theta)$ is always well-defined. To be precise, $g(t) = 0$ when $\abs{t}
-> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < T / 2$
+$x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$ when $\abs{s}
+> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
 (the reason for the factor of $1/2$ will become clear in a later section).
@@
 The sensors sample this continuous-space shifted impulse response, with some
-additive noise. We denote the noiseless sampled version of $x(t; \theta)$ by
+additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
 the $m$-length vector $\v x(\theta)$:
 \begin{equation} \label{eq:sampled-signal}
-	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kT}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)T}{m}; \theta\Big)\bigg]^T
+	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)S}{m}; \theta\Big)\bigg]^T
 \end{equation}
@@
 	\begin{equation} \label{eq:main-lower-bound}
-		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{128} \frac{\sigma^2 T}{nm\kappa^2w}
+		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}
 	\end{equation}
@@
 		total size of the support of the difference signal is $w+2\delta$,
-		hence at most $\floor*{\frac{(w + 2\delta)m}{T}}$ samples of
+		hence at most $\floor*{\frac{(w + 2\delta)m}{S}}$ samples of
 		$\Delta(k)$ are non-zero.}
@@
 	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
-	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kT}{m}; \theta_0\Big) - x\Big(\frac{kT}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
-	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
+	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
+	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
 \end{align}
-where $x(t;\theta_i)$ is the continuous-space filtered signal described in
+where $x(s;\theta_i)$ is the continuous-space filtered signal described in
 section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
@@
 \begin{equation}
-	\abs[\Big]{g\Big(\frac{kT}{m} - \theta_0\Big) - g\Big(\frac{kT}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
+	\abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)} \leq \kappa \abs{\theta_0 - \theta_1} = \kappa \cdot 2\delta
 \end{equation}
@@
 equal to the number of sensors in the total region covered by the signals
-$x(t;\theta_0)$ and $x(t;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
+$x(s;\theta_0)$ and $x(s;\theta_1)$ (see Figs.~\ref{fig:overlap-middle} and
 \ref{fig:delta-sampled}). Therefore, $\norm{\v\Delta}_0 = \floor[\big]{\frac{(w
-+ 2\delta)m}{T} + 1}$, since at most a fraction $(w + 2\delta) / T$ of the $m$
++ 2\delta)m}{S} + 1}$, since at most a fraction $(w + 2\delta) / S$ of the $m$
 sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
@@
 \begin{equation} \label{eq:delta-bound}
-	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{T} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{T} + 1\Big).
+	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{S} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{S} + 1\Big).
 \end{equation}
 Since sensors are uniformly distributed, and since the domain is periodic, this
-holds even if $\theta_0$ lies at the edge of the domain (close to $t=0$, for
-example). \textcolor{blue}{In such a case, one part of the signal $x(t;\theta_0)$ will appear at
+holds even if $\theta_0$ lies at the edge of the domain (close to $s=0$, for
+example). \textcolor{blue}{In such a case, one part of the signal $x(s;\theta_0)$ will appear at
 the left edge of the domain, and the remaining part will appear as the
-repetition from the period $[T, 2T)$, at the right edge of the domain.} Also
-note that the two signals $x(t;\theta_0)$ and $x(t;\theta_1)$ overlap at most
-once, since $w < T/2$, as stated in section~\ref{sec:signal-model}.
+repetition from the period $[S, 2S)$, at the right edge of the domain.} Also
+note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
+once, since $w < S/2$, as stated in section~\ref{sec:signal-model}.
 
@@
 \begin{align}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \\
-	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{T} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \\
+	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
 \end{align}
@@
 tighten the bound by choosing $\delta$ as a function of the remaining variables
-in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 T}} =
-\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2T}{8nm\kappa^2
-w}}$, so that for $\Phi(\delta) = \delta^2$,
+in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 S}} =
+\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2
+S}{8nm\kappa^2 w}}$, so that for $\Phi(\delta) = \delta^2$,
 equation~\eqref{eq:lb-after-delta-bound} becomes
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 T}{nm\kappa^2 w}.
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 S}{nm\kappa^2 w}.
 \end{equation}
@@
 \emph{all} parts of the impulse response should get \emph{sensed} uniformly.
-So, if $\theta$ were restricted to the region $[0, T)$ (now on a linear,
+So, if $\theta$ were restricted to the region $[0, S)$ (now on a linear,
 non-periodic domain), and if sensors were available to sense the signal from
-$[-w/2, T{+}w/2)$ (for an impulse response with restricted support as described
+$[-w/2, S{+}w/2)$ (for an impulse response with restricted support as described
 in section~\ref{sec:signal-model}), then the proof for sensor noise would still
@@
 \begin{equation} \label{eq:holder-delta-bound}
-	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{T} + 1\bigg).
+	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
 \end{equation}
-Hence, we choose $\delta = (\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
+Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
 w})^{1/2\alpha}$, to procure an asymptotic lower bound
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 T}{2^{2\alpha + 1} nm \kappa^2
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
 w}\bigg)^{1/\alpha}.
@@
 Another simple extension takes our problem from a one-dimensional setting to a
-$d$-dimensional setting. Here, we would have $\v\theta \in [0, T)^d$, and the
+$d$-dimensional setting. Here, we would have $\v\theta \in [0, S)^d$, and the
 $\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
@@
 which shows that the KL-divergence between distributions is maximized (and
-hence error minimized) at regions where the slope of $x(t;\theta)$ is largest.
+hence error minimized) at regions where the slope of $x(s;\theta)$ is largest.
 

### 2017-01-21 q-function-test/q_fn_test.py
Add Q-fn script for bd with new sensor model.

@@ -1,0 +1,67 @@
+#!/usr/bin/env python3
+
+from __future__ import print_function, division
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+import scipy.special as spl
+
+def compute_bound(M):
+    S = 1
+    w = 0.1
+    sigma2 = 1
+    n = np.logspace(2, 5, 4)[:, np.newaxis]
+
+    #M = 10
+    delta = np.linspace(0, 0.25, 1000)
+
+    # Define the space
+    num_s = 1000
+    s = np.linspace(0, S, M, endpoint=False)
+    #s = np.linspace(0, S, num_s, endpoint=False)
+
+    # Assume theta0 = 0, so that theta1 = 2*delta
+    theta0 = 0  # But this is implicit, moving forward
+    theta1 = 2 * delta[:, np.newaxis]
+
+    # Define the sampled impulse response
+    x0 = np.zeros(M)
+    i = np.abs(s) <= w/2
+    x0[i] = w/2 - s[i]
+    i = np.abs(S - s) <= w/2
+    x0[i] = w/2 - (S - s[i])
+
+    x1 = np.zeros((delta.size, M))
+    i = np.abs(s - theta1) <= w/2
+    x1[i] = w/2 - np.abs(s - theta1)[i]
+    i = np.abs(S - (s - theta1)) <= w/2
+    x1[i] = w/2 - np.abs(S - (s - theta1)[i])
+
+    #print(x0.shape)
+    #print(x1.shape)
+    #plt.plot(x1[100] - x0)
+    #plt.show()
+
+    dmin_by_2 = np.sqrt(np.sum((x1 - x0) ** 2, axis=-1)) / 2
+    Pe = 0.5 - 0.5 * spl.erf(dmin_by_2 / np.sqrt(2 * M * sigma2 / n))
+
+    bound = delta**2 * Pe
+    return np.max(bound, axis=-1)
+
+    #plt.plot(bound.T)
+    #plt.show()
+
+if __name__ == '__main__':
+    Ms = np.arange(2, 50)
+    bound = []
+    for M in Ms:
+        bound.append(compute_bound(M))
+    plt.semilogy(np.vstack(bound))
+    plt.title('Lower bound vs. number of sensors', fontsize=20)
+    plt.xlabel('$m$', fontsize=20)
+    plt.ylabel('$\mathcal{M} = \delta^2 P_e$', fontsize=20)
[…]

### 2017-01-22 q-function-test/q_fn_test.py
Fix the integration issue.
- Making the sensors integrators gives the correct bound which shows
  larger error at smaller numbers of sensors

@@ -17,26 +17,39 @@ def compute_bound(M):
     delta = np.linspace(0, 0.25, 1000)
 
     # Define the space
-    num_s = 1000
-    s = np.linspace(0, S, M, endpoint=False)
-    #s = np.linspace(0, S, num_s, endpoint=False)
+    num_s = 10000
+    s = np.linspace(0, S, num_s, endpoint=False)
 
     # Assume theta0 = 0, so that theta1 = 2*delta
     theta0 = 0  # But this is implicit, moving forward
     theta1 = 2 * delta[:, np.newaxis]
 
-    # Define the sampled impulse response
-    x0 = np.zeros(M)
+    # Define the continuous impulse response
+    x0_c = np.zeros(s.size)
     i = np.abs(s) <= w/2
-    x0[i] = w/2 - s[i]
+    x0_c[i] = w/2 - s[i]
     i = np.abs(S - s) <= w/2
-    x0[i] = w/2 - (S - s[i])
+    x0_c[i] = w/2 - (S - s[i])
 
-    x1 = np.zeros((delta.size, M))
+    x1_c = np.zeros((delta.size, s.size))
     i = np.abs(s - theta1) <= w/2
-    x1[i] = w/2 - np.abs(s - theta1)[i]
+    x1_c[i] = w/2 - np.abs(s - theta1)[i]
     i = np.abs(S - (s - theta1)) <= w/2
-    x1[i] = w/2 - np.abs(S - (s - theta1)[i])
+    x1_c[i] = w/2 - np.abs(S - (s - theta1)[i])
+
+    # Compute mean sensor values by integrating the continuous impulse response
+    x0 = np.zeros(M)
+    x1 = np.zeros((delta.size, M))
+    ds = S / num_s
+    # j=0 is a special case
+    i = (s >= (M - 0.5) * S / M) + (s < 0.5 * S / M)
+    x0[0] = np.sum(x0_c[i]) * ds
+    x1[:, 0] = np.sum(x1_c[:, i], axis=1) * ds
+    for j in range(1, M):
+        # Compute the expected value of the j'th sensor for all deltas
+        i = (s >= (j - 0.5) * S / M) * (s < (j + 0.5) * S / M)
+        x0[j] = np.sum(x0_c[i]) * ds
+        x1[:, j] = np.sum(x1_c[:, i], axis=1) * ds
 
[…]

### 2017-01-22 paper.tex
Add new section on numerical bounds.

@@
 \subsection{Lower bounds using Le Cam's method}
+\label{sec:lecam-lb}
 
@@
 
+\subsection{Towards a more realistic sensor model}
+
+The bound in Theorem~\ref{thm:main-lb} indicates that the error in source
+localization goes to zero, as the number of sensors goes to infinity. This
+observation is distinct from the lower bound given
+in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
+the lower bound is strictly greater than zero. This indicates that the bound
+in section~\ref{sec:lecam-lb} is loose for large numbers of sensors.
+
+The looseness lies in a poor sensor model: we assume that an arbitrarily large
+number of sensors can be squeezed into a finite amount of space, and that these
+sensors \emph{still} give us i.i.d.\ observations, with the same noise
+variance. This is an impractical expectation. In reality, sensors have a
+certain width, and the signal measured by them is the integral of the
+continuous-space signal within that width (this is similar to a sample-and-hold
+circuit, which integrates a continuous-\emph{time} signal over a short period).
+If the width of a sensor is decreased, then effectively, its signal-to-noise
+ratio reduces \textcolor{red}{<Need to add reference or explanation>} (this is
+intuitively evident in the sample-and-hold analogy: to compute the signal
+value, the integral must be divided by the time interval over which the
+integration is performed; this division amplifies noise as the time interval
+gets smaller).
+
+We performed a preliminary study to understand the effect of viewing sensors
+as integrators. The bounding technique used in section~\ref{sec:lecam-lb} no
+longer easily admits a solution which gives a bound for all values of $m$. We
+can compute the bound numerically, however, using exact expressions for error
+probability in a binary hypothesis test. For gaussian distributions of equal
+variance, the expression is a Q-function in the distance between their means:
+\begin{equation}
+	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_1 - \v\mu_2}}{2\sigma}\bigg)
+\end{equation}
+\textcolor{red}{Is this definitely correct? i.e.\ the best test is a linear
+separator? I think this is coming from Neyman-Pearson. Should I cite?}
+The minimax estimation risk is lower bounded by the risk in hypothesis testing,
+so
+\begin{equation}
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma}\bigg).
+\end{equation}
+This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
+separated by a distance of $2\delta$. As the $\delta$ increases, it becomes
+easier to distinguish between the two hypotheses, so $P_e$ falls. When
+numerically evaluating the bound, therefore, we have to \emph{manually}
+trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
+comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
+hypotheses to distinguish between. To make the simulation easier, we can relax
+the process of finding the least discernable hypothesis pair by fixing
+$\theta_0$. Then, we need only optimize over $\delta$, making the process more
+tractable. This comes at the cost of loosening the lower bound.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=3.2in]{lb-vs-numsensors-int}
+	\caption{A numerically generated plot of the lower bound on minimax risk of
+	source localization, against the number of uniformly distributed sensors
+used to estimate the location. The different curves are for different numbers
+of ``trials'' (i.i.d.\ sensor observations). The bound saturates for large $m$,
+indicating that for a fixed number of trials (or equivalently, for a fixed
+SNR), there is reduced benefit in increasing the number of sensors beyond a
+point. However, with more trials, the bound saturates at increasingly larger
+numbers of sensors. Thus, there is benefit to increasing the number of sensors,
+provided SNR can be increased by leveraging larger numbers of trials.}
+	\label{fig:numerical}
+\end{figure}
+
+Plotting this numerically computed bound for different numbers of trials (see
+Fig.~\ref{fig:numerical}) reveals some interesting trends. First, the bound
+saturates as $m$ grows large, matching the behaviour presented
+in~\cite{Grover2016Fundamental}. Second, the lower bound on error is larger for
+smaller numbers of sensors, as we expect. With fewer sensors, it is harder to
+estimate the location of the point source. Third and most importantly, the
+point at which the bound begins to saturate appears to increase when we use
+more trials. Recall that the number of ``trials'' is the number of i.i.d.\
+sensor observations we receive. Intuitively, estimation is eased with more
+trials, as we could perform more averaging, and increase SNR. \emph{With higher
+SNR, there is greater benefit in using a larger number of sensors.} This
+matches the intuition given in~\cite{Grover2016Information}, where it is
+propounded that using more sensors allows us to sample a greater number of
+high-frequency components of the source signal, and hence get a better estimate
+of its location.
+
 \section{Extensions}

### 2017-01-22 paper.tex
Remove section on Holder continuity.

@@
 
-\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}
+%\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}
 
-We can trivially expand the domain of impulse responses to which the lower
-bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
-continuous functions. These are functions which satisfy
-\begin{equation}
-	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
-\end{equation}
-for some constant $\kappa$, and for $\alpha > 0$. Using this property,
-equation~\eqref{eq:delta-bound} reads
-\begin{equation} \label{eq:holder-delta-bound}
-	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
-\end{equation}
-Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
-w})^{1/2\alpha}$, to procure an asymptotic lower bound
-\begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
-w}\bigg)^{1/\alpha}.
-\end{equation}
+%We can trivially expand the domain of impulse responses to which the lower
+%bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
+%continuous functions. These are functions which satisfy
+%\begin{equation}
+%    \abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
+%\end{equation}
+%for some constant $\kappa$, and for $\alpha > 0$. Using this property,
+%equation~\eqref{eq:delta-bound} reads
+%\begin{equation} \label{eq:holder-delta-bound}
+%    \norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
+%\end{equation}
+%Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
+%w})^{1/2\alpha}$, to procure an asymptotic lower bound
+%\begin{equation}
+%    \mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
+%w}\bigg)^{1/\alpha}.
+%\end{equation}
 

### 2017-01-22 paper.tex
Edit abstract.

@@
 
-\title{Minimax lower bounds for source localization}
+\title{Lower Bounds on the Minimax Risk for the \\ Source Localization Problem}
 
@@
 
-The ``source localization'' problem is one that arises in several fields. For
-instance, in neuroscience, one might wish to use electroencephalography (EEG)
-measurements to locate the source of brain activity.
-\textcolor{red}{<Briefly mention other applications>}.
+The ``source localization'' problem is one in which we wish to estimate the
+location of a point source observed through a diffusive medium using an array
+of sensors. The diffusive medium is modeled as a low-pass filter, and the noise
+is taken to be additive, white and gaussian.
 
-The common underlying factor in each of these problems is the presence of a
-point source, whose signal passes through a diffusive medium and is sensed by
-an array of sensors. We then wish to recover the location of the source using
-noisy sensed values. The diffusive medium is modeled as acting like a low-pass
-filter. The noise is taken to be additive gaussian noise \textcolor{red}{which
-may have a non-diagonal covariance matrix}.
+We give lower bounds on the minimax risk (mean squared-error in location) in
+estimating the location of the source, which applies to all estimators, for
+\textcolor{red}{compactly supported (am I using this correctly?)} Lipschitz-continuous impulse responses of
+the low-pass filter, when using a unformly distributed sensor array. We show
+that the minimax error decays to zero inversely in the number of sensors. We
+also perform a preliminary numerical analysis for a more physical model that
+views sensors as integrators, wherein the bound saturates before going to zero
+for large sensor numbers. The benefit of increased sensor density is seen only
+when the signal-to-noise ratio is high. Our bounds are the first to give a
+scaling in terms of the number of sensors used.
 
-\textcolor{red}{Rephrase this para.}
-We give minimax lower bounds on the squared error in estimating the location of
-the source, which applies to all estimators, when using unformly distributed
-sensors and for certain classes of impulse response of the low-pass filter. Our
-bounds are the first to give a scaling in terms of sensor density.
+While our results are shown for sources located on a one-dimensional circular
+domain, they can be easily extended to sources on one-dimensional line segments
+and d-dimensional boxes. The technique for deriving these minimax bounds also
+sheds light on the sensor placement problem: increased resolution in a narrow
+region can be obtained by placing sensors \emph{around} the region of interest.
 

### 2017-01-22 paper.tex
Edit intro and discussion; fix numerical section.

@@
 estimating the location of the source, which applies to all estimators, for
-\textcolor{red}{compactly supported (am I using this correctly?)} Lipschitz-continuous impulse responses of
-the low-pass filter, when using a unformly distributed sensor array. We show
-that the minimax error decays to zero inversely in the number of sensors. We
-also perform a preliminary numerical analysis for a more physical model that
-views sensors as integrators, wherein the bound saturates before going to zero
-for large sensor numbers. The benefit of increased sensor density is seen only
-when the signal-to-noise ratio is high. Our bounds are the first to give a
-scaling in terms of the number of sensors used.
+\textcolor{red}{compactly supported (am I using this correctly?)}
+Lipschitz-continuous impulse responses of the low-pass filter, when using a
+unformly distributed sensor array. We show that the minimax error decays to
+zero inversely in the number of sensors. We also perform a preliminary
+numerical analysis for a more physical model that views sensors as integrators,
+wherein the bound saturates before going to zero for large sensor numbers. The
+benefit of increased sensor density is seen only when the signal-to-noise ratio
+is high. Our bounds are the first to give a scaling in terms of the number of
+sensors used.
 
@@
 
-The source localization problem is one that appears in many fields where it is
-of interest to find the position of a source using an array of sensors.
-
-Our principal motivation comes from an application in brain activity
-measurement, where one wishes to use modalities such as electroencephalography
-(EEG) and magnetoencephalography (MEG) to record activity inside the
-brain~\cite{Baillet2001Electromagnetic}.  For example, current EEG systems use
-anywhere between 10 and 250 sensors (electrodes) placed on the scalp, to sense
-electric potentials produced by neuronal activity within the
-brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
-produce this activity are frequently modeled as current dipoles. For a single
-activated dipole within the brain (which is modeled as being localized to a
-point), the electrodes effectively sense a diffuse (blurred-out) representation
-of the point source, as a result of the spatial low-pass filtering effect of
-the different layers between the brain surface and scalp surface (cerebrospinal
-fluid, skull and skin).
+The source localization problem is one that arises in many fields in different
+forms. Our principal motivation comes from Electroencephalography (EEG), a
+non-invasive brain measurement modality which uses sensors (electrodes) placed
+on the scalp to sense electric potentials produced by neuronal activity within
+the brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
+produce this activity are frequently modeled as current dipoles, and it is
+often of clinical or neuroscientific interest to estimate their
+locations~\cite{Baillet2001Electromagnetic}. For a single activated dipole
+within the brain (which is modeled as being localized to a point), the
+electrodes effectively sample a diffuse (blurred) representation of the point
+source, as a result of the spatial low-pass filtering effect of the different
+layers between the brain surface and scalp surface (cerebrospinal fluid, skull
+and skin).
 
@@
 conclusion is based primarily on a Nyquist rate analysis, and on an
-information-theoretic bound (which are possibly very loose) on the accuracy of
-source localization algorithms. In deriving this bound, however, the scalp
-potential was never sampled; equivalently, it was assumed that an
-\emph{infinite} number of sensors was available to sample the EEG signal at
-every point on the scalp. Hence, the dependence of the bound on the number of
-sensors is lost.
+information-theoretic bound (first derived in~\cite{Grover2016Fundamental}) on
+the accuracy of source localization algorithms. This information-theoretic
+bound, however, was derived for the unsampled, continuous-space potential on
+the scalp. In other words, it was a result asymptotic in the number of sensors.
+The claim in~\cite{Grover2016Information} is therefore not fully substantiated
+by this analysis, since it does not provide a lower bound showing improvement
+with increasing sensor density.
 
-Earlier work by Mosher et al.~\cite{Mosher1993Error}, which seeks to address
-this issue by deriving Cramer-Rao lower bounds, is also not completely
-satisfactory because these bounds do not apply to biased estimators. Commonly
-used source localization algorithms (such as the Minimum Norm
+Earlier work by Mosher et al.~\cite{Mosher1993Error} also sought to derive
+lower bounds on source localization accuracy by deriving Cramer-Rao lower
+bounds. They also have some preliminary numerical results showing improvement
+with increased numbers of sensors. However, this result is also not completely
+satisfactory because Cramer-Rao bounds do not apply to biased estimators.
+Commonly used source localization algorithms (such as the Minimum Norm
 Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
@@
 This paper seeks to address the shortcomings of earlier methods by deriving
-minimax lower bounds for the source localization problem, which apply to
-\emph{all} estimators (biased \emph{and} unbiased), and which can give a
-scaling in terms of the number of sensors used (for a fixed sensor placement
+lower bounds on the minimax risk for the source localization problem, which
+apply to \emph{all} estimators (biased \emph{and} unbiased), and which can give
+a scaling in terms of the number of sensors used (for a fixed sensor placement
 configuration). Computing the lower bound for the ``real brain model'' (where
@@
 difficult since analytical solutions for the EEG signal, given the brain
-activity, do not exist. ``Spherical head
-models''~\cite{Nunez2006Electric,Grover2016Information} \emph{do} have
-analytical solutions, but are still not easily amenable to analytical lower
-bounds because the spherical surface does not permit uniform
+activity, do not exist. Previous lower bounds are based on ``spherical head
+models''~\cite{Nunez2006Electric,Grover2016Information} which \emph{have}
+analytical solutions. But these are still not easily amenable to analytical
+lower bounds because the spherical surface does not permit uniform
 sampling~\cite{Heath1956Thirteen}, and because the solution is expressed in
@@
 Section~\ref{sec:source-localization}, the minimax techniques and our main
-result in Section~\ref{sec:minimax-lower-bounds} and a few straightforward
-extensions in Section~\ref{sec:extensions}. Finally, we conclude with a
-discussion on implications for sensor placement and future work in
-Section~\ref{sec:discussion}.
+results in Section~\ref{sec:minimax-lower-bounds}. Finally, we conclude in
+Section~\ref{sec:discussion} with a discussion on how our results can be
+extended to other simple settings, and on implications for sensor placement.
 
@@
 We start by giving a detailed description of the one-dimensional setting of the
-source localization problem. Recall that, in this problem, we're trying to
-determine the location of a point source by observing it through a diffusive
-medium using a sensor array.
+source localization problem.
 
@@
 
-\subsection{Towards a more realistic sensor model}
+\subsection{Towards a more \textcolor{blue}{physical} sensor model}
 
@@
 localization goes to zero, as the number of sensors goes to infinity. This
-observation is distinct from the lower bound given
-in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
-the lower bound is strictly greater than zero. This indicates that the bound
-in section~\ref{sec:lecam-lb} is loose for large numbers of sensors.
+observation is significantly different from the information-theoretic lower
+bound given in~\cite{Grover2016Fundamental}, where even with an infinite number
+of sensors, the lower bound is strictly greater than zero. This indicates that
+the bound in section~\ref{sec:lecam-lb} is loose for large numbers of sensors.
 
@@
 If the width of a sensor is decreased, then effectively, its signal-to-noise
-ratio reduces \textcolor{red}{<Need to add reference or explanation>} (this is
-intuitively evident in the sample-and-hold analogy: to compute the signal
-value, the integral must be divided by the time interval over which the
-integration is performed; this division amplifies noise as the time interval
-gets smaller).
+ratio reduces (this is intuitively evident in the sample-and-hold analogy: to
+compute the signal value, the integral must be divided by the time interval
+over which the integration is performed; this division amplifies noise as the
+time interval gets smaller).
 
 We performed a preliminary study to understand the effect of viewing sensors
-as integrators. The bounding technique used in section~\ref{sec:lecam-lb} no
-longer easily admits a solution which gives a bound for all values of $m$. We
-can compute the bound numerically, however, using exact expressions for error
-probability in a binary hypothesis test. For gaussian distributions of equal
-variance, the expression is a Q-function in the distance between their means:
+as integrators. In the new sensor model, sensors have a finite width, which
+decreases as the number of sensors increases, in order to allow their number to
+grow unbounded. Concretely, the $k$-th sensor which is located at $s = kS/m$
+extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$. The signal
+sensed by this sensor is the $k$-th element of $\v x(\theta)$, given by
 \begin{equation}
-	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_1 - \v\mu_2}}{2\sigma}\bigg)
+	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
+\end{equation}
+\textcolor{red}{Also need to talk about noise here - sensor obs. are still iid
+because we assume wss noise, and integrating over distinct regions of this
+process retains iid nature}
+The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
+admits a solution which gives a bound for all values of $m$. We can compute the
+bound numerically, however, using exact expressions for error probability in a
+binary hypothesis test. For gaussian distributions of equal variance, the best
+possible error probability (over all tests) is a Q-function in the distance
+between their means:
+\begin{equation}
+	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma}\bigg)
 \end{equation}
@@
 The minimax estimation risk is lower bounded by the risk in hypothesis testing,
-so
+hence
 \begin{equation}
@@
 
-\section{Extensions}
-\label{sec:extensions}
+%\section{Extensions}
+%\label{sec:extensions}
 
-\subsection{From a circular (periodic) domain to a linear (aperiodic) domain}
+%\subsection{From a circular (periodic) domain to a linear (aperiodic) domain}
 
-So far, we've relied on the presence of a circular domain for to make the
-arguments in the proof. However, the most important requirement was that
-\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
-So, if $\theta$ were restricted to the region $[0, S)$ (now on a linear,
-non-periodic domain), and if sensors were available to sense the signal from
-$[-w/2, S{+}w/2)$ (for an impulse response with restricted support as described
-in section~\ref{sec:signal-model}), then the proof for sensor noise would still
-fall through, albeit with slightly different constants.
+%So far, we've relied on the presence of a circular domain for to make the
+%arguments in the proof. However, the most important requirement was that
+%\emph{all} parts of the impulse response should get \emph{sensed} uniformly.
+%So, if $\theta$ were restricted to the region $[0, S)$ (now on a linear,
+%non-periodic domain), and if sensors were available to sense the signal from
+%$[-w/2, S{+}w/2)$ (for an impulse response with restricted support as described
+%in section~\ref{sec:signal-model}), then the proof for sensor noise would still
+%fall through, albeit with slightly different constants.
 
@@
 
-\subsection{From a one-dimensional domain to a $d$-dimensional domain}
+%\subsection{From a one-dimensional domain to a $d$-dimensional domain}
 
-Another simple extension takes our problem from a one-dimensional setting to a
-$d$-dimensional setting. Here, we would have $\v\theta \in [0, S)^d$, and the
-$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
-\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
-the manner described in~\cite{Duchi2015Information}, we can split the minimax
-risk along each of the $d$ dimensions, and bound each separately using Le Cam's
-method.
+%Another simple extension takes our problem from a one-dimensional setting to a
+%$d$-dimensional setting. Here, we would have $\v\theta \in [0, S)^d$, and the
+%$\ell_2$ loss function, $\Phiorho(\v\theta, \vhat\theta) = \norm{\v\theta -
+%\vhat\theta}^2$. Then, using Assouad's lemma~\cite{Tsybakov2009Introduction} in
+%the manner described in~\cite{Duchi2015Information}, we can split the minimax
+%risk along each of the $d$ dimensions, and bound each separately using Le Cam's
+%method.
 
@@
 
-The lower bound given by Theorem~\ref{thm:main-lb} goes to zero as the number
-of sensors, $m$, goes to infinity, \emph{even if} the total number of trials
-$n$ is kept \emph{fixed}. This would mean that a high sensor density can
-overcome the effect of noise in a single trial. The reason this happens is that
-we assume sensors are affected by i.i.d. noise, no matter what sampling density
-we use. This is an increasingly poor assumption as sensor density increases,
-however; we expect noise to become correlated if sensors are extremely close
-(due to inductive/capacitive coupling, for example). A more realistic lower
-bound will show the benefit of increasing sensor density up to a point only,
-beyond which it will have to scale alongside the number of trials.
+While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
+for a large number of sensors, it still gives some important insights. For
+instance, if we assume that sensors have a constant width $c$, then even if we
+view sensors as integrators, the bound tells us something about the scaling of
+error with number of sensors, up to $m = \floor*{\frac{S}{c}}$. Beyond this
+point, averaging noise by increasing the number of trials may help one get to a
+target mean squared error in location. An analytical derivation of the
+trade-off between $m$ and $n$ in achieving a certain target MSE is relegated to
+future work.
 
-The lower bounding \emph{technique} gives certain inisights on the issue of
-sensor placement. Suppose we wanted to achieve a higher resolution in a
+While the bounds in section~\ref{sec:lecam-lb} were derived for a
+one-dimensional circular domain, extensions to a one-dimensional linear domain
+(of fixed length) and to a $d$-dimensional domain (circular or linear) are
+fairly straightforward, under certain conditions. For a 1D linear domain, we
+require that sensors capture the entirety of the impulse response even at the
+edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
+S{+}w/2]$. For extending to $d$-dimensions, it suffices to apply Assouad's
+Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
+independent 1D problems.
+
+The lower bounding \emph{technique} itself gives certain inisights on the issue
+of sensor placement. Suppose we wanted to achieve a higher resolution in a
 restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
 \Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
-to place sensors \emph{not} precisely over the region, but rather in the region
-corresponding to the \emph{largest change} in the impulse response. Indeed, it
-is possible to derive an  approximate lower bound using Taylor's approximation,
-which shows that the KL-divergence between distributions is maximized (and
-hence error minimized) at regions where the slope of $x(s;\theta)$ is largest.
+to place sensors \emph{not} precisely over $[a, b]$, but rather in the region
+\emph{surrounding} $[a, b]$, corresponding to the \emph{largest change} in the
+impulse response. Indeed, it is possible to derive an approximate lower bound
+using Taylor's approximation, which shows that the KL-divergence between
+distributions is maximized (and hence error minimized) at regions where the
+slope of $x(s;\theta)$ is largest.
 
@@
 far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
-select such a point, where the value of the impulse response so produced at the
-sensors is smallest, so that SNR is minimized.
+select a $\theta$ for which the value of the impulse response at the sensors is
+smallest, so that SNR is minimized.
 

### 2017-01-22 paper.tex
Make several miscellaneous fixes.

@@
 Earlier work by Mosher et al.~\cite{Mosher1993Error} also sought to derive
-lower bounds on source localization accuracy by deriving Cramer-Rao lower
-bounds. They also have some preliminary numerical results showing improvement
-with increased numbers of sensors. However, this result is also not completely
+lower bounds on source localization error by deriving Cramer-Rao lower bounds.
+They also give some preliminary numerical results showing improvement with
+increased numbers of sensors. However, this result is also not completely
 satisfactory because Cramer-Rao bounds do not apply to biased estimators.
@@
 The one-dimensional toy problem is an effective tool for understanding bounds
-on source localization accuracy in other settings as well, such as
-\textcolor{red}{<insert other applications>}. A vast literature on linear
-inverse problems (see~\cite{Bal2012Introduction} for an introduction to this
-field) and deconvolution algorithms exists, and has addressed the reduced
-one-dimensional problem in broad settings
+on source localization accuracy in other settings as well, such as auditory
+localization of a sound using a microphone array (although typically, very
+different approaches are employed there, when compared to EEG source
+localization). A vast literature on linear inverse problems
+(see~\cite{Bal2012Introduction} for an introduction to this field) and
+deconvolution algorithms exists, and has addressed the reduced one-dimensional
+problem in broad settings
 (see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
@@
 of the domain, a source located at position $\theta \in \Theta$ implies the
-presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.
+presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$ (using
+`$s$' for the spatial variable).
 
@@
 automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
-provide, therefore, are for \emph{this specific sensor configuration}. For a
-discussion on why this configuration might be an appropriate choice in the
-minimax setting, and on non-uniform sensor placement, see
-section~\ref{sec:discussion}.
+provide are for \emph{this specific sensor configuration}. For a discussion on
+why this configuration might be an appropriate choice in the minimax setting,
+and on non-uniform sensor placement, see section~\ref{sec:discussion}.
 
@@
 I$, i.e. the sensors are afflicted by i.i.d.\ noise. The second is called the
-``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms.
-\textcolor{red}{Insert description of source noise.}
+``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms. \textcolor{blue}{We
+restrict our attention to the sensor noise setting in this paper.}
 
@@
 \hat\theta) = \abs{\theta - \hat\theta}$). For this metric, we can define the
-minimax risk over all possible estimators $\hat\theta(Y^n)$ and all possible
+minimax risk over all possible estimators $\hat\theta(Y^n)$ and all parameters
 $\theta \in \Theta$:
@@
 \end{equation}
-where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$) and
-$Y^n$ is the random vector corresponding to a noisy realization of sensor
-values.
+where $\Phi$ is any non-decreasing function (e.g.\ $\Phi(\rho) = \rho^2$).
 
@@
 	\end{equation}
-	where $V$ is the unknown, true hypothesis, and $\psi$ is our estimate of
-	the hypothesis.
+	where $V$ is the unknown true hypothesis which takes values uniformly from
+	$\mathcal{V}$, and $\psi$ is our estimate of the hypothesis.
 \end{theorem}
@@
 difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
-of error is high (where $\theta_j$ has been selected to be suitably close).
+of error is high.
 
@@
 problem. The simplest way to do this is to consider a binary hypothesis test
-($\abs{\mathcal{V}} = 2$) and use what is known as Le Cam's method:
+and use what is known as Le Cam's method:
 \begin{theorem} \label{thm:le-cam}
-	For a binary hypothesis test, i.e., when $\mathcal{V} = \{0, 1\}$,
+	For a binary hypothesis test, i.e., $\mathcal{V} = \{0, 1\}$,
 	\begin{equation}
@@
 in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:le-cam} states
-that the minimum probability of error that any estimator must make in a binary
-hypothesis testing problem is related to the distance between the distributions
-corresponding to the two hypotheses. The closer the two distributions, the
-higher the chance of making an error in distinguishing between them.
+that the minimum achievable error probability in a binary hypothesis testing
+problem is related to the distance between the distributions corresponding to
+the two hypotheses.
 
@@
 	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
-	location of a point source is lower bounded by:
+	location of a point source is lower bounded by
 	\begin{equation} \label{eq:main-lower-bound}
-		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}
+		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}.
 	\end{equation}
 \end{theorem}
-
-\begin{IEEEproof}
-Starting from equation~\eqref{eq:le-cam-bound} and working on the setting
-described in Section~\ref{sec:source-localization}, we proceed to derive the
-total variation distance for the distributions of interest. Using Pinsker's
-inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
-KL-divergence~\cite{Duchi2015Information}, we see that:
-\begin{equation} \label{eq:pinsker-tensorization}
-	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
-\end{equation}
-For multivariate normal distributions with the same covariance, the
-KL-divergence is given by
-\begin{equation} \label{eq:kl-div-normal}
-	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
-\end{equation}
-where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
-respectively~\cite{DuchiDerivation}.
 
@@
 		total size of the support of the difference signal is $w+2\delta$,
-		hence at most $\floor*{\frac{(w + 2\delta)m}{S}}$ samples of
+		hence at most $\floor*{\frac{(w + 2\delta)m}{S} + 1}$ samples of
 		$\Delta(k)$ are non-zero.}
@@
 
-For the case of sensor noise, $P_i = \mathcal{N}(\v x(\theta_i), \sigma^2 \m
-I)$, as described in section~\ref{sec:channel-model}. Hence, combining
+\begin{IEEEproof}
+Starting from equation~\eqref{eq:le-cam-bound}, we proceed to derive the total
+variation distance for the distributions of interest. Using Pinsker's
+inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
+KL-divergence~\cite{Duchi2015Information}, we see that:
+\begin{equation} \label{eq:pinsker-tensorization}
+	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
+\end{equation}
+For multivariate normal distributions with the same covariance, the
+KL-divergence is given by
+\begin{equation} \label{eq:kl-div-normal}
+	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
+\end{equation}
+where $\v \mu_0$ and $\v \mu_1$ are the means of $P_0$ and $P_1$
+respectively~\cite{DuchiDerivation}. For the case of sensor noise, $P_i =
+\mathcal{N}(\v x(\theta_i), \sigma^2 \m I)$, as described in
+section~\ref{sec:channel-model}. Hence, combining
 equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
@@
 $\mathbb I_A(k)$ denote the indicator function of $k$ belonging to the set $A$
-(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and is $0$ otherwise). Then, we have
+(i.e., $\mathbb I_A(k) = 1$ if $k \in A$, and $0$ otherwise). Then, we have
 \begin{align}
-	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
-	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) \\
-	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k)
+	&\norm{\v\Delta}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 = \sum_{k=0}^{m-1} \abs{\Delta(k)}^2 \, \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) \\
+	&= \sum_{k=0}^{m-1} \abs[\Big]{x\Big(\frac{kS}{m}; \theta_0\Big) - x\Big(\frac{kS}{m}; \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) \\
+	&= \sum_{k=0}^{m-1} \abs[\Big]{g\Big(\frac{kS}{m} - \theta_0\Big) - g\Big(\frac{kS}{m} - \theta_1\Big)}^2 \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k)
 \end{align}
@@
 \begin{equation}
-	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} > 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
+	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \sum_{k=0}^{m-1} \mathbb I_{\{\ell: \abs{\Delta(\ell)} \neq 0\}}(k) = 4 \kappa^2 \delta^2 \norm{\v\Delta}_0.
 \end{equation}
@@
 
-\subsection{Towards a more \textcolor{blue}{physical} sensor model}
+\subsection{Towards a more physical sensor model}
 
@@
 certain width, and the signal measured by them is the integral of the
-continuous-space signal within that width (this is similar to a sample-and-hold
+continuous-space signal within that width (analogous to a sample-and-hold
 circuit, which integrates a continuous-\emph{time} signal over a short period).
@@
 extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$. The signal
-sensed by this sensor is the $k$-th element of $\v x(\theta)$, given by
+sensed by this sensor is the $k$-th element of $\v x(\theta)$, now given by
 \begin{equation}
@@
 \end{equation}
-\textcolor{red}{Also need to talk about noise here - sensor obs. are still iid
-because we assume wss noise, and integrating over distinct regions of this
-process retains iid nature}
+The noise vector $\v \epsilon$ is also generated similarly, by integrating over
+small sections of a wide-sense-stationary white noise process, which is assumed
+to additively corrupt the signal. This leads to i.i.d.\ noise values at sensors
+(since they do not overlap), with variance inversely proportional to $m$, i.e.,
+$\sigma(m) \propto 1/\sqrt{m}$.
+
 The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
@@
 \begin{equation}
-	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma}\bigg)
+	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg)
 \end{equation}
@@
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma}\bigg).
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
 \end{equation}

### 2017-01-23 paper.tex
WIP: Incorporate edits from comments.

@@
 
-The ``source localization'' problem is one in which we wish to estimate the
-location of a point source observed through a diffusive medium using an array
-of sensors. The diffusive medium is modeled as a low-pass filter, and the noise
-is taken to be additive, white and gaussian.
+The ``source localization'' problem is one in which we estimate the location of
+a point source observed through a diffusive medium using an array of sensors.
 
 We give lower bounds on the minimax risk (mean squared-error in location) in
-estimating the location of the source, which applies to all estimators, for
-\textcolor{red}{compactly supported (am I using this correctly?)}
-Lipschitz-continuous impulse responses of the low-pass filter, when using a
-unformly distributed sensor array. We show that the minimax error decays to
-zero inversely in the number of sensors. We also perform a preliminary
-numerical analysis for a more physical model that views sensors as integrators,
-wherein the bound saturates before going to zero for large sensor numbers. The
-benefit of increased sensor density is seen only when the signal-to-noise ratio
-is high. Our bounds are the first to give a scaling in terms of the number of
-sensors used.
+estimating the location of the source, which apply to all estimators, for
+\textcolor{blue}{certain classes} of impulse responses of the low-pass filter,
+when using a unformly distributed sensor array. We show that
+\textcolor{blue}{for sensors of a fixed size}, the lower bound decays with
+increasing numbers of sensors. We also perform a preliminary numerical analysis
+to understand the effect of increasing the number of sensors to infinity by
+shrinking their size, wherein the bound saturates for large sensor numbers.
+\textcolor{blue}{In the second scenario, it is seen that there is greater
+benefit to increasing the number of sensors} as the signal-to-noise increases.
+Our bounds are the first to give a scaling for the minimax risk in terms of the
+number of sensors used.
 
-While our results are shown for sources located on a one-dimensional circular
-domain, they can be easily extended to sources on one-dimensional line segments
-and d-dimensional boxes. The technique for deriving these minimax bounds also
-sheds light on the sensor placement problem: increased resolution in a narrow
-region can be obtained by placing sensors \emph{around} the region of interest.
+%While our results are derived for sources located on a one-dimensional circular
+%domain, they can be easily extended to sources on one-dimensional line segments
+%and d-dimensional boxes. The technique for deriving these minimax bounds also
+%sheds light on the sensor placement problem: increased resolution in a narrow
+%region can be obtained by placing sensors \emph{around} the region of interest.
 
@@
 
-The source localization problem is one that arises in many fields in different
-forms. Our principal motivation comes from Electroencephalography (EEG), a
-non-invasive brain measurement modality which uses sensors (electrodes) placed
-on the scalp to sense electric potentials produced by neuronal activity within
-the brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
-produce this activity are frequently modeled as current dipoles, and it is
-often of clinical or neuroscientific interest to estimate their
+The source localization problem arises in many fields in different forms. Our
+principal motivation comes from Electroencephalography (EEG), a non-invasive
+brain measurement modality which uses electrodes placed on the scalp to sense
+electric potentials produced by neuronal activity within the
+brain~\cite{Nunez2006Electric}. The neurons (or groups of neurons) which
+produce this activity are usually modeled as current dipoles, and it is often
+of clinical or neuroscientific interest to estimate their
 locations~\cite{Baillet2001Electromagnetic}. For a single activated dipole
-within the brain (which is modeled as being localized to a point), the
-electrodes effectively sample a diffuse (blurred) representation of the point
-source, as a result of the spatial low-pass filtering effect of the different
-layers between the brain surface and scalp surface (cerebrospinal fluid, skull
-and skin).
+within the brain (which is modeled as a point source), the electrodes
+effectively sample a diffuse (blurred) representation of the dipole, as a
+result of the spatial low-pass filtering effect of the different layers between
+the brain surface and scalp surface (cerebrospinal fluid, skull and skin).
 
@@
 conclusion is based primarily on a Nyquist rate analysis, and on an
-information-theoretic bound (first derived in~\cite{Grover2016Fundamental}) on
-the accuracy of source localization algorithms. This information-theoretic
-bound, however, was derived for the unsampled, continuous-space potential on
-the scalp. In other words, it was a result asymptotic in the number of sensors.
-The claim in~\cite{Grover2016Information} is therefore not fully substantiated
-by this analysis, since it does not provide a lower bound showing improvement
-with increasing sensor density.
+information-theoretic bound~\cite{Grover2016Fundamental} on the accuracy of
+source localization algorithms. This information-theoretic bound, however, was
+derived for the unsampled, continuous-space potential on the scalp, or
+equivalently, in the limit of the number of sensors going to infinity. The
+claim that source localization can benefit from increased sensor density is,
+therefore, not fully substantiated by the information-theoretic bound, since
+the latter does not provide a lower bound showing improvement with increasing
+sensor density.
 
-Earlier work by Mosher et al.~\cite{Mosher1993Error} also sought to derive
-lower bounds on source localization error by deriving Cramer-Rao lower bounds.
-They also give some preliminary numerical results showing improvement with
-increased numbers of sensors. However, this result is also not completely
-satisfactory because Cramer-Rao bounds do not apply to biased estimators.
-Commonly used source localization algorithms (such as the Minimum Norm
-Estimate~\cite{Hamalainen1994Interpreting}) on the other hand, are \emph{known}
-to be biased~\cite{Lin2006Assessing}.
+Earlier work by Mosher et al.~\cite{Mosher1993Error} also gave numerical lower
+bounds on source localization error. However, the Cramer-Rao lower bounds
+derived by them do not apply to biased estimators, including several commonly
+used source localization
+algorithms~\cite{Hamalainen1994Interpreting,Lin2006Assessing}.
 
@@
 lower bounds on the minimax risk for the source localization problem, which
-apply to \emph{all} estimators (biased \emph{and} unbiased), and which can give
-a scaling in terms of the number of sensors used (for a fixed sensor placement
-configuration). Computing the lower bound for the ``real brain model'' (where
-the complete geometry of the brain surface is accounted for) is rendered very
-difficult since analytical solutions for the EEG signal, given the brain
-activity, do not exist. Previous lower bounds are based on ``spherical head
-models''~\cite{Nunez2006Electric,Grover2016Information} which \emph{have}
-analytical solutions. But these are still not easily amenable to analytical
-lower bounds because the spherical surface does not permit uniform
-sampling~\cite{Heath1956Thirteen}, and because the solution is expressed in
-terms of special functions. We therefore restrict our analysis to a source
-localization problem on a one-dimensional domain (to be described in detail in
-Section~\ref{sec:source-localization}).
+apply to \emph{all} estimators (biased \emph{and} unbiased), and which captures
+how the bound scales with increasing numbers of sensors. Previous lower bounds
+are based on ``spherical head
+models''~\cite{Nunez2006Electric,Grover2016Information}, which admit analytical
+solutions for the potential of a single dipole. But spherical models are not
+easily amenable to analytical lower bounds which seek to capture scaling in the
+number of sensors, because the spherical surface does not permit uniform
+sampling~\cite{Heath1956Thirteen}. We therefore restrict our analysis to a
+source localization problem on a one-dimensional ``circular'' domain (to be
+described in detail in Section~\ref{sec:source-localization}).
 
 The one-dimensional toy problem is an effective tool for understanding bounds
-on source localization accuracy in other settings as well, such as auditory
-localization of a sound using a microphone array (although typically, very
-different approaches are employed there, when compared to EEG source
-localization). A vast literature on linear inverse problems
-(see~\cite{Bal2012Introduction} for an introduction to this field) and
-deconvolution algorithms exists, and has addressed the reduced one-dimensional
-problem in broad settings
+on source localization accuracy in other settings as well, \textcolor{red}{such
+	as auditory localization of a sound using a microphone array (although
+	typically, very different approaches are employed there, when compared to
+EEG source localization) <shall I remove this?>}. A vast literature on linear
+inverse problems and deconvolution algorithms exists
+(see~\cite{Bal2012Introduction} for an introduction to this field), and has
+addressed the reduced one-dimensional problem in broad settings
 (see~\cite{Cavalier2002Sharp,Efromovich1997Robust,Ibragimov1981Statistical} and
@@
 unique, since most prior work focuses on recovering a whole function (given
-certain smoothness constraints), rather than locating a point source. Work that
-does address point sources, to our knowledge, does not address scaling in the
-number of sensors, since problem settings and applications differ greatly.
+certain smoothness constraints), rather than locating a point
+source~\cite{Cavalier2002Sharp}. \textcolor{blue}{The error metric used when
+recovering the whole function is the mean-squared error in the space of
+square-integrable functions, rather than the distance between the true and
+estimated locations}. Work that \emph{does} address point sources and
+location-based error metrics~\cite{Ibragimov1981Statistical} does not, to our
+knowledge, address scaling in the number of sensors.
 
@@
 through a diffusive medium (treated as a low-pass filter), and corrupted by
-additive Gaussian noise. We describe the problem setting in detail in
-Section~\ref{sec:source-localization}, the minimax techniques and our main
-results in Section~\ref{sec:minimax-lower-bounds}. Finally, we conclude in
+additive white Gaussian noise. We describe the problem setting in detail in
+Section~\ref{sec:source-localization} and the minimax techniques and our main
+results in Section~\ref{sec:minimax-lower-bounds}. We conclude in
 Section~\ref{sec:discussion} with a discussion on how our results can be
-extended to other simple settings, and on implications for sensor placement.
+extended to other simple settings.
 
-%\textcolor{red}{Introduction needs to be re-written.}
-
-%Electroencephalograhy (EEG) is a system used to record the electrical activity
-%of the brain. It is a non-invasive system, which may use anywhere from around
-%10 to 250 electrodes placed on the scalp, to sense electric potentials. These
-%potentials are generated by neuronal activity within the
-%brain~\cite{Buzsaki2012Origin}. These sources of neural activity -- neurons or
-%groups of neurons -- are usually modeled as current
-%dipoles~\cite{Nunez2006Electric}.
-
-%Often, it is of clinical or scientific interest to reconstruct brain activity
-%patterns from EEG sensor measurements. This process is what is broadly referred
-%to when we speak of the term ``source localization''. In this paper, I restrict
-%the discussion to that of localizing a \emph{single} dipole, and refer to this
-%process as ``dipole source localization''. Several algorithms for source
-%localization have been proposed over the years
-%(see~\cite{Baillet2001Electromagnetic} for an excellent review). However, until
-%recently, there has been only one work that has theoretically examined the
-%fundamental limits of source localization accuracy.
-
-%Mosher et.\ al.~\cite{Mosher1993Error} first propounded Cramer-Rao lower bounds
-%for unbiased source localization algorithms. Their work also forms the basis
-%for setting up the source localization problem and deriving more universally
-%applicable bounds in this paper. The Cramer-Rao lower bound is not in itself a
-%completely satisfactory answer to the question of fundamental limits for source
-%localization accuracy. This is because Cramer-Rao bounds only apply to unbiased
-%estimators (or to estimators of \emph{known} bias). In practice, however, many
-%popular source localization algorithms have been shown to be biased, e.g.\
-%the Minimum Norm Estimate (MNE)~\cite{Hamalainen1994Interpreting} is known to
-%bias the solution towards the surface of the head~\cite{Lin2006Assessing}. It
-%is also known that unbiased estimators can have worse mean-squared-error
-%performance than biased estimators. So Cramer-Rao bounds are useful only to a
-%degree, and there may be benefit in deriving bounds that hold for all
-%estimators.
-
-%To this end, Grover~\cite{Grover2016Fundamental} recently proposed a new lower
-%bound for the error in localizing a single dipole. This bound used techniques
-%from information theory, for bounding the source localization error by
-%expressing it in terms of the mutual information across some channel, and then
-%bounding the mutual information by the capacity of the channel. In deriving
-%this bound, however, the scalp potential was never sampled; equivalently, it
-%was assumed that an \emph{infinite} number of sensors was available to sample
-%the EEG signal at every point on the scalp. Clearly, this is a poor assumption
-%and could result in a very loose bound, because it allows for more information
-%to be available at the receiver than otherwise possible. The lower bound also
-%relies on certain relaxations that allow the dipole to distribute its power in
-%non-physical ways in frequency domain. This once again makes the bound loose by
-%assigning the channel a higher capacity than what it could otherwise have.
-
-%To address the shortcomings of the Cramer-Rao and information theoretic lower
-%bounds, I apply two minimax methods to the problem of computing a lower bound
-%for localization error in the idealized EEG dipole source localization problem.
-%I briefly review two minimax methods -- Le Cam's, and Fano's local
-%method~\cite{Duchi2015Information} -- and describe my approach in deriving the
-%minimax lower bound using each of these for spherical and one-dimensional head
-%models.
+For the application of EEG source localization, it might be possible to find
+algorithms which achieve similar scalings as the lower bounds presented here.
+It is also hoped that the techniques presented here will help us derive bounds
+in more difficult settings, such as spherical and realistic brain models.
 
@@
 
-We assume that the point source is located on a circle of circumference $S$ (a
-circular domain enables us to use symmetry arguments to simplify the proof). We
-can view this domain as a line, on which signals are periodic with period $S$.
-The point source is therefore located somewhere within one period. We denote
-the set of possible locations by $\Theta = [0, S)$. Due to the periodic nature
-of the domain, a source located at position $\theta \in \Theta$ implies the
-presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$ (using
-`$s$' for the spatial variable).
+We assume that the point source is located on a circle of circumference $S$. We
+use the variable `$s$' to represent a general point on this domain. We can also
+view this domain as a line, on which signals are periodic with period $S$.  The
+point source is therefore located somewhere within one period. We denote the
+set of possible locations by $\Theta = [0, S)$. Due to the periodic nature of
+the domain, a source located at position $\theta \in \Theta$ implies the
+presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.
 
@@
 why this configuration might be an appropriate choice in the minimax setting,
-and on non-uniform sensor placement, see section~\ref{sec:discussion}.
+see section~\ref{sec:discussion}.
 
@@
 More concretely, we assume that the medium is linear and shift-invariant, so
-that it can be represented by a spatial impulse response (blurring would then
-correspond to low-pass filtering). Let this impulse response be given by
+that it can be represented by a spatial impulse response. Then, blurring would
+correspond to low-pass filtering.  Let this impulse response be given by
 $g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
@@
 > w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
-(the reason for the factor of $1/2$ will become clear in a later section).
+(the reason for the factor of $1/2$ will become clear in a later section). For
+the proof, $g(s)$ is also assumed to be Lipschitz continuous with parameter
+$\kappa$. This implies that $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \;
+\forall \;\; u, v \in \Theta$.
 
-The sensors sample this continuous-space shifted impulse response, with some
+The sensors sample the continuous-space shifted impulse response, with some
 additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
@@
 \end{equation}
+In the source localization problem, we receive $n$ trials\footnote{The word
+``trials'' comes from neuroscience literature, where several trials of an
+experiment are run with a single participant. The participant is given the same
+stimulus in each trial, evoking the same response in the brain (usually with
+some trial-to-trial variability). For our purposes, we assume that trials are
+effectively i.i.d. realizations of sensor noise, with no trial-to-trial
+variability.} (i.e., $n$ realizations) of $\v y$ according to
+equation~\eqref{eq:sensor-obs}, for the same point source $\theta$, using which
+we need to estimate the location of the source.
+
 The complete signal model described in this section is summarized in
@@
 
-The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is
-the only source of uncertainty in the problem. For our purposes, we assume that
-$\v \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
-\Sigma)$. Two kinds of covariance matrices are of particular interest. The
-first is dubbed the ``sensor noise'' setting, wherein $\m\Sigma = \sigma^2 \m
-I$, i.e. the sensors are afflicted by i.i.d.\ noise. The second is called the
-``source noise'' setting, wherein $\m\Sigma$ has off-diagonal terms. \textcolor{blue}{We
-restrict our attention to the sensor noise setting in this paper.}
+The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is the
+only source of uncertainty in the problem. For our purposes, we assume that $\v
+\epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
+\Sigma)$. We restrict our analysis to the ``sensor noise'' setting, wherein
+$\m\Sigma = \sigma^2 \m I$, i.e. the sensors are afflicted by i.i.d.\ noise.
 
 With the addition of Gaussian noise, each possible source location $\theta$
-gives rise to a different distribution at the sensors, denoted by
-\begin{equation} \label{eq:p-theta}
-	P(\theta) = \mathcal{N}(\v x(\theta), \m \Sigma).
-\end{equation}
-$\v y$ is therefore one sample from $P(\theta)$. The space of distributions
-produced by all possible source locations is $\mathcal{P} = \{P(\theta) :
-\theta \in \Theta \}$. We are interested in computing lower bounds for the loss
-function $\Phi(\rho(\theta, \hat\theta)) = \abs{\theta - \hat\theta}^2$, where
-$\hat\theta$ is some estimate of the location based on $n$ trials (i.e. $n$
-realizations) of the noisy sensor observations $\v y$.
+gives rise to a different distribution at the sensors, denoted by $P(\theta) =
+\mathcal{N}(\v x(\theta), \m \Sigma)$. $\v y$ is therefore one sample from the
+distribution $P(\theta)$. The space of distributions produced by all possible
+source locations is $\mathcal{P} = \{P(\theta) : \theta \in \Theta \}$.
+
+The noise is also assumed to be i.i.d.\ across trials, i.e., the $n$
+realizations of $\v y$ are independently drawn from $P(\theta)$, for the
+same location parameter $\theta$.
 
@@
 
-\textcolor{blue}{
 Several techniques for deriving lower bounds on the minimax risk are described
-in~\cite{Tsybakov2009Introduction}. We follow the excellent tutorial written by
-John Duchi~\cite{Duchi2015Information} to briefly outline the steps involved in
-deriving these bounds.
-}
+in~\cite{Tsybakov2009Introduction}. We follow the excellent tutorial of John
+Duchi~\cite{Duchi2015Information} to outline the steps involved.
 
@@
 \label{sec:lecam-lb}
+
+Recall that we are interested in computing lower bounds on the minimax risk for
+the source localization problem defined in
+Section~\ref{sec:source-localization}. We measure \emph{risk} in terms of the
+squared-distance between the true location and the estimated location. Hence,
+our loss function is $\Phi(\rho(\theta, \hat\theta)) = \abs{\theta -
+\hat\theta}^2$, where $\hat\theta$ is some estimate of the location based on
+$n$ trials of the noisy sensor observations $\v y$.
 
@@
 
-The upper bound in~\eqref{eq:delta-bound} translates into a lower
-bound for~\eqref{eq:lb-after-pinsker}:
-\begin{align}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) &\geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{n \cdot 4 \kappa^2 \delta^2}{2\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \\
-	&= \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2} \bigg( \frac{(w + 2\delta) m}{S} + 1\bigg)} \Bigg] \label{eq:lb-after-delta-bound}
-\end{align}
+Combining equations~\eqref{eq:lb-after-pinsker} and~\eqref{eq:delta-bound},
+\begin{equation} \label{eq:lb-after-delta-bound}
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2}\bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg)} \Bigg].
+\end{equation}
 Asymptotically, we choose smaller values of $\delta$ as the number of sensors
@@
 
-The lower bounding \emph{technique} itself gives certain inisights on the issue
-of sensor placement. Suppose we wanted to achieve a higher resolution in a
-restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
-\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
-to place sensors \emph{not} precisely over $[a, b]$, but rather in the region
-\emph{surrounding} $[a, b]$, corresponding to the \emph{largest change} in the
-impulse response. Indeed, it is possible to derive an approximate lower bound
-using Taylor's approximation, which shows that the KL-divergence between
-distributions is maximized (and hence error minimized) at regions where the
-slope of $x(s;\theta)$ is largest.
+%The lower bounding \emph{technique} itself gives certain inisights on the issue
+%of sensor placement. Suppose we wanted to achieve a higher resolution in a
+%restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
+%\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
+%to place sensors \emph{not} precisely over $[a, b]$, but rather in the region
+%\emph{surrounding} $[a, b]$, corresponding to the \emph{largest change} in the
+%impulse response. Indeed, it is possible to derive an approximate lower bound
+%using Taylor's approximation, which shows that the KL-divergence between
+%distributions is maximized (and hence error minimized) at regions where the
+%slope of $x(s;\theta)$ is largest.
 
@@
 
-For the application of EEG source localization, it might be possible to find
-algorithms which achieve similar scalings as the lower bounds presented here.
-It is also hoped that the techniques presented here will help us derive
-analytical bounds in the more difficult setting.
-
-\section*{Acknowledgements}
-
-Praveen Venkatesh is partially supported by the Dowd Fellowship from the
-College of Engineering at Carnegie Mellon University. The authors would like to
-thank Philip and Marsha Dowd for their support and encouragement.
-
 %\IEEEtriggeratref{8}

### 2017-01-24 paper.tex
Complete incorporating all edits.

@@
 \begin{abstract}
+
+To be considered for the 2017 IEEE Jack Keil Wolf ISIT Student Paper Award.
 
@@
 additive noise is given by $\v \epsilon$ (to be described shortly), and the
-noisy samples are represented by $\v y$:
+noisy samples are represented by
 \begin{equation} \label{eq:sensor-obs}
-	\v y = \v x(\theta) + \v \epsilon
+	\v y = \v x(\theta) + \v \epsilon.
 \end{equation}
@@
 \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
-\Sigma)$. We restrict our analysis to the ``sensor noise'' setting, wherein
-$\m\Sigma = \sigma^2 \m I$, i.e. the sensors are afflicted by i.i.d.\ noise.
+\Sigma)$. We restrict our analysis to a ``sensor noise'' setting, wherein
+$\m\Sigma = \sigma^2 \m I$, i.e., noise is i.i.d.\ across sensors.
+
+The noise is also assumed to be i.i.d.\ across trials, i.e., the $n$
+realizations of $\v y$ are independently drawn from $P(\theta)$, for the
+same location parameter $\theta$.
 
@@
 source locations is $\mathcal{P} = \{P(\theta) : \theta \in \Theta \}$.
-
-The noise is also assumed to be i.i.d.\ across trials, i.e., the $n$
-realizations of $\v y$ are independently drawn from $P(\theta)$, for the
-same location parameter $\theta$.
 
@@
 
-We start by lower bounding the minimax risk of the estimation problem with the
-risk incurred in a multiple hypothesis testing problem. For this, we first need
+\textcolor{blue}{We start by lower bounding the maximum risk of the estimation problem with the
+average risk of a multiple hypothesis testing problem.} For this, we first need
 to define a $2\delta$-packing:%
@@
 in~\cite{Duchi2015Information}.  Intuitively, Theorem~\ref{thm:est-to-testing}
-says that the error in estimating $\theta_i$ is likely to be more if it is
+says that the error in estimating $\theta_i$ is likely to be large if it is
 difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
@@
 
-Recall that we are interested in computing lower bounds on the minimax risk for
-the source localization problem defined in
-Section~\ref{sec:source-localization}. We measure \emph{risk} in terms of the
+For the source localization problem, we measure \emph{risk} in terms of the
 squared-distance between the true location and the estimated location. Hence,
@@
 
-We now state the main result of this paper.
-\begin{theorem} \label{thm:main-lb}
-	For a source localization problem as defined in
-	section~\ref{sec:source-localization} with sensor noise and a spatial
-	impulse response that is $\kappa$-Lipschitz continuous and has restricted
-	support of width $w$, the \textcolor{blue}{asymptotic} minimax risk in estimating the
-	location of a point source is lower bounded by
-	\begin{equation} \label{eq:main-lower-bound}
-		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}.
-	\end{equation}
-\end{theorem}
-
 \begin{figure}[t]
 	\centering
-	\includegraphics[width=2.8in]{overlap-middle-pics}
+	\includegraphics[width=2.6in]{overlap-middle-pics}
 	\caption{Depiction of the continuous-space signals produced by two
@@
 \end{figure}
-
 \begin{figure}[t]
 	\centering
-	\includegraphics[width=2.8in]{delta-sampled-pics}
+	\includegraphics[width=2.6in]{delta-sampled-pics}
 	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
@@
 
+We now state the main result of this paper.
+\begin{theorem} \label{thm:main-lb}
+	For a source localization problem as defined in
+	section~\ref{sec:source-localization}, the minimax risk in estimating the
+	location of a point source is lower bounded by
+	\begin{equation}
+		\mathfrak{M}_n(\mathcal{P}, \Phi\circ\rho) \geq \sup_{0 < \delta < S/4} \frac{\delta^2}{2} \Bigg[1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2}\bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg)} \Bigg]
+	\end{equation}
+	For sufficiently large $m$, the bound can be approximated by
+	\begin{equation} \label{eq:main-lower-bound}
+		\mathfrak{M}_n(\mathcal{P}, \Phiorho) \gtrsim \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2w}.
+	\end{equation}
+\end{theorem}%
 \begin{IEEEproof}
@@
 + 2\delta)m}{S} + 1}$, since at most a fraction $(w + 2\delta) / S$ of the $m$
-sensors \textcolor{blue}{(plus 1, to account for edge-effects)} can lie in the region covered by
+sensors (plus 1, to account for edge-effects) can lie in the region covered by
 the two impulse responses. The final upper bound on $\norm{\v\Delta}^2$ is
@@
 holds even if $\theta_0$ lies at the edge of the domain (close to $s=0$, for
-example). \textcolor{blue}{In such a case, one part of the signal $x(s;\theta_0)$ will appear at
+example). In such a case, one part of the signal $x(s;\theta_0)$ will appear at
 the left edge of the domain, and the remaining part will appear as the
-repetition from the period $[S, 2S)$, at the right edge of the domain.} Also
+repetition from the period $[S, 2S)$, at the right edge of the domain. Also
 note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
@@
 \end{equation}
-Asymptotically, we choose smaller values of $\delta$ as the number of sensors
-grows large. Hence, \textcolor{blue}{neglecting edge effects} and terms of order $\delta^3$, we
-tighten the bound by choosing $\delta$ as a function of the remaining variables
-in order to have $\sqrt{\frac{2nm\kappa^2\delta^2 w}{\sigma^2 S}} =
-\frac{1}{2}$. This is achieved for $\delta = \sqrt{\frac{\sigma^2
-S}{8nm\kappa^2 w}}$, so that for $\Phi(\delta) = \delta^2$,
-equation~\eqref{eq:lb-after-delta-bound} becomes
+This bound holds for any feasible $2\delta$-packing. We can derive the tightest
+possible bound by maximizing the above quantity over all feasible $\delta$.
+Since the maximum attainable separation between two hypotheses on the periodic
+domain is $S/2$, we maximize $\delta$ over $(0, S/4)$. This yields the theorem.
+
+To derive the approximation, we observe that for sufficiently large numbers of
+sensors, the optimal value of $\delta$ starts becoming small, as hypotheses
+must chosen to be closer in order to make the error probability large. Hence,
+neglecting edge effects and terms of order $\delta^3$, we can give an
+approximate bound for large $m$ using a heuristic: tighten the bound by
+choosing $\sqrt{\frac{2n\kappa^2\delta^2wm}{\sigma^2 S}} = \frac{1}{2}$. This
+is achieved for $\delta = \sqrt{\frac{\sigma^2 S}{8nm\kappa^2 w}}$, so that for
+$\Phi(\delta) = \delta^2$, equation~\eqref{eq:lb-after-delta-bound} becomes
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \textcolor{blue}{\frac{1}{32}} \frac{\sigma^2 S}{nm\kappa^2 w}.
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2 w}.
 \end{equation}
@@
 
-The bound in Theorem~\ref{thm:main-lb} indicates that the error in source
-localization goes to zero, as the number of sensors goes to infinity. This
-observation is significantly different from the information-theoretic lower
-bound given in~\cite{Grover2016Fundamental}, where even with an infinite number
-of sensors, the lower bound is strictly greater than zero. This indicates that
-the bound in section~\ref{sec:lecam-lb} is loose for large numbers of sensors.
+The bound in Theorem~\ref{thm:main-lb} may mislead one to think that the error
+in source localization goes to zero, as the number of sensors goes to infinity.
+This observation is qualitatively different from the information-theoretic
+lower bound given in~\cite{Grover2016Fundamental}, where even with an infinite
+number of sensors, the lower bound is strictly greater than zero. This
+indicates that the bound in section~\ref{sec:lecam-lb} is failing to capture
+some effect which leads to saturation of error, as the number of sensors
+increases.
 
-The looseness lies in a poor sensor model: we assume that an arbitrarily large
-number of sensors can be squeezed into a finite amount of space, and that these
-sensors \emph{still} give us i.i.d.\ observations, with the same noise
-variance. This is an impractical expectation. In reality, sensors have a
-certain width, and the signal measured by them is the integral of the
-continuous-space signal within that width (analogous to a sample-and-hold
-circuit, which integrates a continuous-\emph{time} signal over a short period).
-If the width of a sensor is decreased, then effectively, its signal-to-noise
-ratio reduces (this is intuitively evident in the sample-and-hold analogy: to
-compute the signal value, the integral must be divided by the time interval
-over which the integration is performed; this division amplifies noise as the
-time interval gets smaller).
+Indeed, the bound in Theorem~\ref{thm:main-lb} assumes that an arbitrarily
+large number of sensors can be squeezed into a finite amount of space, and that
+these sensors \emph{still} give us i.i.d.\ observations, with the same noise
+variance. This is aphysical, since in reality, sensors have a certain width,
+and the signal measured by them is the integral of the continuous-space signal
+within that width (analogous to a sample-and-hold circuit, which integrates a
+continuous-\emph{time} signal over a short period).  If the width of a sensor
+is decreased, then effectively, its signal-to-noise ratio reduces. This is
+intuitively evident in the sample-and-hold analogy: to compute the signal
+value, the integral must be divided by the time interval over which the
+integration is performed; this division amplifies noise as the time interval
+gets smaller.
 
@@
 bound numerically, however, using exact expressions for error probability in a
-binary hypothesis test. For gaussian distributions of equal variance, the best
-possible error probability (over all tests) is a Q-function in the distance
-between their means:
+binary hypothesis test. For gaussian distributions of equal variance and a
+uniform prior on the hypotheses, the best possible error probability (over all
+tests) is a Q-function~\cite{Qfunction} in the distance between their
+means~\cite{NPLemmaOrSimilar},
 \begin{equation}
-	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg)
+	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_0 - \v\mu_1}}{2\sigma(m)}\bigg).
 \end{equation}
-\textcolor{red}{Is this definitely correct? i.e.\ the best test is a linear
-separator? I think this is coming from Neyman-Pearson. Should I cite?}
 The minimax estimation risk is lower bounded by the risk in hypothesis testing,
@@
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma(m)}\bigg).
 \end{equation}
@@
 	\caption{A numerically generated plot of the lower bound on minimax risk of
-	source localization, against the number of uniformly distributed sensors
-used to estimate the location. The different curves are for different numbers
-of ``trials'' (i.i.d.\ sensor observations). The bound saturates for large $m$,
-indicating that for a fixed number of trials (or equivalently, for a fixed
-SNR), there is reduced benefit in increasing the number of sensors beyond a
-point. However, with more trials, the bound saturates at increasingly larger
-numbers of sensors. Thus, there is benefit to increasing the number of sensors,
-provided SNR can be increased by leveraging larger numbers of trials.}
+		source localization, against the number of uniformly distributed
+		sensors, $m$, used to estimate the location. The different curves are
+		for different numbers of ``trials'' $n$ (i.i.d.\ sensor observations).
+		The bound saturates for large $m$, indicating that for a fixed number
+		of trials (or equivalently, for a fixed SNR), there is reduced benefit
+		in increasing the number of sensors beyond a point. However, with more
+		trials, the bound saturates at increasingly larger numbers of sensors.
+	Thus, there is benefit to increasing the number of sensors, provided SNR
+can be increased by leveraging larger numbers of trials.}
 	\label{fig:numerical}
@@
 estimate the location of the point source. Third and most importantly, the
-point at which the bound begins to saturate appears to increase when we use
+point at which the bound begins to saturate increases when we use
 more trials. Recall that the number of ``trials'' is the number of i.i.d.\

### 2017-01-24 paper.tex
Revise the physical sensor model section.

@@
 \usepackage{mathtools}
+\usepackage{nicefrac}
 \usepackage{array}
@@
 	\IEEEauthorblockN{
-		Praveen Venkatesh\IEEEauthorrefmark{1}
-		and Pulkit Grover\IEEEauthorrefmark{2}
+		\textcolor{blue}{Praveen Venkatesh %\IEEEauthorrefmark{1}
+		and Pulkit Grover} %\IEEEauthorrefmark{2}
 	}
-	\IEEEauthorblockA{
-		Electrical \& Computer Engineering,
-		and the Center for the Neural Basis of Cognition,
-		Carnegie Mellon University \\
-		\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
-		\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
-	}
+	%\IEEEauthorblockA{
+	%    Electrical \& Computer Engineering,
+	%    and the Center for the Neural Basis of Cognition,
+	%    Carnegie Mellon University
+	%    \\
+	%    \IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
+	%    \IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
+	%}
 }
@@
 To be considered for the 2017 IEEE Jack Keil Wolf ISIT Student Paper Award.
-
 The ``source localization'' problem is one in which we estimate the location of
@@
 
-\section{Minimax lower bounds for the one-dimensional model}
+\section{Lower bounds on the minimax risk for the one-dimensional model}
 \label{sec:minimax-lower-bounds}
@@
 \begin{equation}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2 w}.
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \gtrsim \frac{1}{32} \frac{\sigma^2 S}{nm\kappa^2 w}.
 \end{equation}
@@
 in source localization goes to zero, as the number of sensors goes to infinity.
+\textcolor{blue}{
 This observation is qualitatively different from the information-theoretic
@@
 increases.
+}
 
@@
 these sensors \emph{still} give us i.i.d.\ observations, with the same noise
-variance. This is aphysical, since in reality, sensors have a certain width,
-and the signal measured by them is the integral of the continuous-space signal
+variance. This is aphysical, since in reality, each sensor has a certain width,
+and the value measured by it is the integral of the continuous-space signal
 within that width (analogous to a sample-and-hold circuit, which integrates a
@@
 
-We performed a preliminary study to understand the effect of viewing sensors
-as integrators. In the new sensor model, sensors have a finite width, which
-decreases as the number of sensors increases, in order to allow their number to
-grow unbounded. Concretely, the $k$-th sensor which is located at $s = kS/m$
-extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$. The signal
-sensed by this sensor is the $k$-th element of $\v x(\theta)$, now given by
+We performed a preliminary study to understand the effect of viewing sensors as
+integrators. In the new sensor model, sensors have a width which decreases as
+their number grows to infinity. Concretely, the $k$-th sensor which is located
+at $s = kS/m$ extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$.
+The signal sensed by this sensor is the $k$-th element of $\v x(\theta)$, now
+given by
 \begin{equation}
@@
 \end{equation}
+\textcolor{blue}{
 The noise vector $\v \epsilon$ is also generated similarly, by integrating over
 small sections of a wide-sense-stationary white noise process, which is assumed
-to additively corrupt the signal. This leads to i.i.d.\ noise values at sensors
-(since they do not overlap), with variance inversely proportional to $m$, i.e.,
-$\sigma(m) \propto 1/\sqrt{m}$.
+to additively corrupt the continuous-space signal $x(s;\theta)$ prior to
+sampling. This leads to i.i.d.\ noise values at sensors (since they do not
+overlap), with variance inversely proportional to $m$, i.e., $\sigma(m) \propto
+1/\sqrt{m}$.
+}
 
 The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
-admits a solution which gives a bound for all values of $m$. We can compute the
-bound numerically, however, using exact expressions for error probability in a
+admits a solution which gives a bound for all values of $m$. We instead compute
+the bound numerically, using exact expressions for error probability in a
 binary hypothesis test. For gaussian distributions of equal variance and a
-uniform prior on the hypotheses, the best possible error probability (over all
-tests) is a Q-function~\cite{Qfunction} in the distance between their
+uniform prior on the hypotheses, the minimum possible error probability (over
+all tests) is a Q-function in the distance between their
 means~\cite{NPLemmaOrSimilar},
@@
 \end{equation}
-The minimax estimation risk is lower bounded by the risk in hypothesis testing,
-hence
+where $Q(x) = \int_x^\infty \frac{1}{\sqrt{2\pi u}} e^{-u^2/2} du$. Hence, from
+Theorem~\ref{thm:est-to-testing},
 \begin{equation}
@@
 \end{equation}
-This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
-separated by a distance of $2\delta$. As the $\delta$ increases, it becomes
-easier to distinguish between the two hypotheses, so $P_e$ falls. When
-numerically evaluating the bound, therefore, we have to \emph{manually}
-trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
-comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
-hypotheses to distinguish between. To make the simulation easier, we can relax
-the process of finding the least discernable hypothesis pair by fixing
-$\theta_0$. Then, we need only optimize over $\delta$, making the process more
-tractable. This comes at the cost of loosening the lower bound.
+This bound is valid for any $\{\theta_0, \theta_1\}$ constituting a
+$2\delta$-packing of $\Theta$. To numerically optimize over all possible
+packings, we relax the process by fixing $\theta_0 = 0$ and optimizing over
+$\theta_1 = 2\delta$.  We compute sensor values by performing numerical
+integration, and find the best possible $\delta$ by grid search.
+
+%This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
+%separated by a distance of $2\delta$.
+%As $\delta$ increases, it becomes
+%easier to distinguish between the two hypotheses, so $P_e$ falls. When
+%numerically evaluating the bound, therefore, we have to \emph{manually}
+%trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
+%comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
+%hypotheses to distinguish between. To make the simulation easier, we can relax
+%the process of finding the least discernable hypothesis pair by fixing
+%$\theta_0$. Then, we need only optimize over $\delta$, making the process more
+%tractable. This comes at the cost of loosening the lower bound.
 
@@
 in~\cite{Grover2016Fundamental}. Second, the lower bound on error is larger for
-smaller numbers of sensors, as we expect. With fewer sensors, it is harder to
-estimate the location of the point source. Third and most importantly, the
-point at which the bound begins to saturate increases when we use
-more trials. Recall that the number of ``trials'' is the number of i.i.d.\
-sensor observations we receive. Intuitively, estimation is eased with more
-trials, as we could perform more averaging, and increase SNR. \emph{With higher
-SNR, there is greater benefit in using a larger number of sensors.} This
-matches the intuition given in~\cite{Grover2016Information}, where it is
-propounded that using more sensors allows us to sample a greater number of
-high-frequency components of the source signal, and hence get a better estimate
-of its location.
+smaller numbers of sensors, as we expect. Third and most importantly, as the
+number of trials increases, bound begins to saturate only for larger numbers of
+sensors. In other words, there is increased benefit in using larger numbers of
+sensors, when we also have more trials\footnote{Recall that the number of
+``trials'' is the number of i.i.d.\ sensor observations we receive, per
+equation~\ref{eq:sensor-obs}.}. This substantiates the intuition given
+in~\cite{Grover2016Information}, which addresses this issue using a
+Nyquist-rate perspective. A larger number of sensors will sample a larger
+number of high-frequency components of the source signal (and hence allow us to
+locate it better), but only if the noise floor is sufficiently low. Noise
+variance, in turn, can be reduced by averaging over multiple trials.
 
@@
 edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
-S{+}w/2]$. For extending to $d$-dimensions, it suffices to apply Assouad's
+S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
 Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
-independent 1D problems.
+independent one-dimensional problems.
+
+Another point on sensor placement bears repeating: the bounds derived in this
+paper apply to only a specific sensor configuration, i.e., the uniform one.
+Intuitively, this is the correct choice in the minimax setting, since any
+non-uniform placement will have one or more points which is far from all
+sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
+$\theta$ for which the value of the impulse response at the sensors is
+smallest, so that the ratio of mean-sensor-value to noise variance (a form of
+``SNR'') is minimized.
 
@@
 
-Another point on sensor placement bears repeating: the bounds derived in this
-paper apply to only a specific sensor configuration, i.e., the uniform one.
-This would intuitively seem to be an appropriate choice in the minimax setting,
-however, since any non-uniform placement will have one or more points which is
-far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
-select a $\theta$ for which the value of the impulse response at the sensors is
-smallest, so that SNR is minimized.
-
 %\IEEEtriggeratref{8}

### 2017-01-25 q-function-test/q_fn_test.py
Fix and check q_fn_test.py.

@@ -11,13 +11,13 @@ def compute_bound(M):
     S = 1
     w = 0.1
     sigma2 = 1
-    n = np.logspace(2, 5, 4)[:, np.newaxis]
+    n = np.logspace(4, 7, 4)[:, np.newaxis]
 
     #M = 10
-    delta = np.linspace(0, 0.25, 1000)
+    delta = np.linspace(0, 0.25, 1000, endpoint=False)
 
     # Define the space
-    num_s = 10000
+    num_s = 50000
     s = np.linspace(0, S, num_s, endpoint=False)
 
     # Assume theta0 = 0, so that theta1 = 2*delta
@@ -57,30 +57,35 @@ def compute_bound(M):
     #plt.show()
 
     dmin_by_2 = np.sqrt(np.sum((x1 - x0) ** 2, axis=-1)) / 2
-    Pe = 0.5 - 0.5 * spl.erf(dmin_by_2 / np.sqrt(2 * sigma2 / M / n))
+    Pe = 0.5 - 0.5 * spl.erf(dmin_by_2 / np.sqrt(sigma2 / M / n))
 
     bound = delta**2 * Pe
+    plt.figure()
+    plt.semilogy(bound.T)
+    plt.savefig('opt-%d.png' % M)
+    plt.close()
+
     return np.max(bound, axis=-1)
 
     #plt.plot(bound.T)
     #plt.show()
 
 if __name__ == '__main__':
-    Ms = np.arange(2, 50, 2)
+    Ms = np.r_[2:60:2]
     bound = []
     for M in Ms:
         print(M)
         bound.append(compute_bound(M))
-    plt.plot(Ms, np.vstack(bound), linewidth=2)
+    plt.semilogy(Ms, np.vstack(bound), linewidth=2)
     plt.title('Lower bound vs. number of sensors', fontsize=20)
     plt.xlabel('$m$', fontsize=20)
     plt.ylabel('$\mathfrak{M} = \delta^2 P_e$', fontsize=20)
-    ax = plt.gca()
-    box = ax.get_position()
-    ax.set_position([box.x0, box.y0, box.width * 0.8, box.height])
-    ax.legend(('$\sigma_0^2/n = 10^{-2}$', '$\sigma_0^2/n = 10^{-3}$',
-               '$\sigma_0^2/n = 10^{-4}$', '$\sigma_0^2/n = 10^{-5}$'),
[…]

### 2017-01-25 paper.tex
Make miscellaneous minor edits.

@@
 estimating the location of the source, which apply to all estimators, for
-\textcolor{blue}{certain classes} of impulse responses of the low-pass filter,
-when using a unformly distributed sensor array. We show that
+\textcolor{blue}{certain classes of diffusive media represented by low-pass
+filters}, when using a unformly distributed sensor array. We show that
 \textcolor{blue}{for sensors of a fixed size}, the lower bound decays with
@@
 Section~\ref{sec:source-localization} and the minimax techniques and our main
-results in Section~\ref{sec:minimax-lower-bounds}. We conclude in
-Section~\ref{sec:discussion} with a discussion on how our results can be
-extended to other simple settings.
+results \textcolor{blue}{(for a naive and then for a more physical sensor
+model)} in Section~\ref{sec:minimax-lower-bounds}. We conclude in
+Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
+and on how our results can be extended to other simple settings.
 
-For the application of EEG source localization, it might be possible to find
-algorithms which achieve similar scalings as the lower bounds presented here.
-It is also hoped that the techniques presented here will help us derive bounds
-in more difficult settings, such as spherical and realistic brain models.
+\textcolor{blue}{
+For EEG source localization, we hope to find algorithms that achieve scalings
+close to the bounds we present.  We also expect to build upon the techniques
+presented in this paper to derive bounds for spherical and realistic brain
+models.
+}
 
@@
 
-All signals on the aforementioned circular domain are of the form
-$f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
-represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
+%All ``continuous-space'' signals (analogous to continuous- and
+	%discrete-\emph{time} signals) on the aforementioned circular domain are
+All signals of the form $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$
+is represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
 $\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
@@
 the proof, $g(s)$ is also assumed to be Lipschitz continuous with parameter
-$\kappa$. This implies that $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \;
-\forall \;\; u, v \in \Theta$.
+$\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \; \forall \;\; u, v
+\in \Theta$.
 
-The sensors sample the continuous-space shifted impulse response, with some
+The sensors sample the shifted continuous-space impulse response, with some
 additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
@@
 we need to estimate the location of the source.
-
 The complete signal model described in this section is summarized in
@@
 average risk of a multiple hypothesis testing problem.} For this, we first need
-to define a $2\delta$-packing:%
+to define a $2\delta$-packing.%
 \begin{definition}
@@
 
+\textcolor{blue}{
 Another point on sensor placement bears repeating: the bounds derived in this
@@
 ``SNR'') is minimized.
+}
 

### 2017-01-25 q-function-test/q_fn_test.py
Add annotated figure.

@@ -67,8 +67,6 @@ def compute_bound(M):
 
     return np.max(bound, axis=-1)
 
-    #plt.plot(bound.T)
-    #plt.show()
 
 if __name__ == '__main__':
     Ms = np.r_[2:60:2]
@@ -77,16 +75,15 @@ if __name__ == '__main__':
         print(M)
         bound.append(compute_bound(M))
     plt.semilogy(Ms, np.vstack(bound), linewidth=2)
-    plt.title('Lower bound vs. number of sensors', fontsize=20)
-    plt.xlabel('$m$', fontsize=20)
-    plt.ylabel('$\mathfrak{M} = \delta^2 P_e$', fontsize=20)
-    #ax = plt.gca()
-    #box = ax.get_position()
-    #ax.set_position([box.x0, box.y0, box.width * 0.8, box.height])
-    #ax.legend(('$\sigma_0^2/n = 10^{-2}$', '$\sigma_0^2/n = 10^{-3}$',
-    #           '$\sigma_0^2/n = 10^{-4}$', '$\sigma_0^2/n = 10^{-5}$'),
-    #          loc='center left', bbox_to_anchor=(1, 0.5))
-    #plt.legend(('$\sigma_0^2/n = 10^{-2}$', '$\sigma_0^2/n = 10^{-3}$',
-    #            '$\sigma_0^2/n = 10^{-4}$', '$\sigma_0^2/n = 10^{-5}$'),
-    #           loc='upper right')
+    plt.title('Numerically computed lower bound vs.\nnumber of sensors',
+              fontsize=20)
+    plt.xlabel('Number of sensors, $m$', fontsize=20)
+    plt.ylabel('Lower bound, $\sup_{0<\delta<S/4} \delta^2 P_e$', fontsize=20)
+    ax = plt.gca()
+    ax.tick_params(axis='both', which='major', labelsize=12)
+    plt.text(40, 4e-3, '$n = 1$', fontsize=18)
+    plt.text(40, 3e-4, '$n = 10$', fontsize=18)
+    plt.text(40, 2e-6, '$n = 100$', fontsize=18)
+    plt.text(40, 2e-7, '$n = 1000$', fontsize=18)
+    plt.tight_layout()
     plt.show()

### 2017-01-25 paper.tex
Add annotated figure.
Make one submittable version.

@@
 	\IEEEauthorblockN{
-		\textcolor{blue}{Praveen Venkatesh %\IEEEauthorrefmark{1}
-		and Pulkit Grover} %\IEEEauthorrefmark{2}
+		Praveen Venkatesh (\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
+		and Pulkit Grover (\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
 	}
@@
 estimating the location of the source, which apply to all estimators, for
-\textcolor{blue}{certain classes of diffusive media represented by low-pass
-filters}, when using a unformly distributed sensor array. We show that
-\textcolor{blue}{for sensors of a fixed size}, the lower bound decays with
+certain classes of diffusive media represented by low-pass
+filters, when using a uniformly distributed sensor array. We show that
+for sensors of a fixed size, the lower bound decays with
 increasing numbers of sensors. We also perform a preliminary numerical analysis
@@
 shrinking their size, wherein the bound saturates for large sensor numbers.
-\textcolor{blue}{In the second scenario, it is seen that there is greater
-benefit to increasing the number of sensors} as the signal-to-noise increases.
+In the second scenario, it is seen that there is greater
+benefit to increasing the number of sensors as the signal-to-noise increases.
 Our bounds are the first to give a scaling for the minimax risk in terms of the
@@
 \section{Introduction}
-
-%- The source localization problem is one that occurs in several fields
-%  - Brain activity measurement, in the form of localizing brain activity
-%    - Possible applications are epilepsy focus localization
-%    - Neuroscientific experiments - locating the source of activity at certain
-%      points in time, for understanding brain function
-%  - Need to read Vetterli's papers on acoustic source localization-type things
-%  - Need to read up linear inverse problems literature
-
-%- Previous work
-%  - In the brain activity localization side of things, lots of algorithms, but
-%    not much understanding of bounds (Mosher, Grover).
-%    - These have their own issues: CRLB does not apply to all estimators, info
-%      theoretic bound does not give scaling with sensors
-%  - Other work on minimax bounds and estimators for linear inverse problems
-%    concentrate on function estimation (with smoothness constraints on the
-%    function being estimated)
-%    - e.g. Tsybakov, Efromovich, Ibragimov \& Has'minskii, and references
-%      therein
-%    - Obviously, bounds for function estimation will look radically different
-%      from bounds for a location parameter
-%    - Location-parameter based work appears to exist in Ibragimov-Has'minskii,
-%      but they treat it as an exercise, without seriously considering
-%      extensions, and looking at scaling with number of sensors
-
-%- Cite Fisher's book on circular domain signals somewhere (statistical analysis
-%  of circular data)
 
@@
 The one-dimensional toy problem is an effective tool for understanding bounds
-on source localization accuracy in other settings as well, \textcolor{red}{such
-	as auditory localization of a sound using a microphone array (although
-	typically, very different approaches are employed there, when compared to
-EEG source localization) <shall I remove this?>}. A vast literature on linear
-inverse problems and deconvolution algorithms exists
+on source localization accuracy in other settings as well. A vast literature on
+linear inverse problems and deconvolution algorithms exists
 (see~\cite{Bal2012Introduction} for an introduction to this field), and has
@@
 certain smoothness constraints), rather than locating a point
-source~\cite{Cavalier2002Sharp}. \textcolor{blue}{The error metric used when
-recovering the whole function is the mean-squared error in the space of
-square-integrable functions, rather than the distance between the true and
-estimated locations}. Work that \emph{does} address point sources and
-location-based error metrics~\cite{Ibragimov1981Statistical} does not, to our
-knowledge, address scaling in the number of sensors.
+source~\cite{Cavalier2002Sharp}. Work that \emph{does} address point sources
+and location-based error metrics~\cite{Ibragimov1981Statistical} does not, to
+our knowledge, address scaling in the number of sensors.
 
@@
 Section~\ref{sec:source-localization} and the minimax techniques and our main
-results \textcolor{blue}{(for a naive and then for a more physical sensor
-model)} in Section~\ref{sec:minimax-lower-bounds}. We conclude in
+results (for a naive and then for a more physical sensor model) in
+Section~\ref{sec:minimax-lower-bounds}. We conclude in
 Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
@@
 
-\textcolor{blue}{
 For EEG source localization, we hope to find algorithms that achieve scalings
@@
 models.
-}
 
@@
 some trial-to-trial variability). For our purposes, we assume that trials are
-effectively i.i.d. realizations of sensor noise, with no trial-to-trial
+effectively i.i.d.\ realizations of sensor noise, with no trial-to-trial
 variability.} (i.e., $n$ realizations) of $\v y$ according to
@@
 	\includegraphics[width=3.5in]{block-diagram}
-	\caption{A diagramatic representation of the signal model described in
+	\caption{A diagrammatic representation of the signal model described in
 	section~\ref{sec:signal-model}.}
@@
 
-\textcolor{blue}{We start by lower bounding the maximum risk of the estimation problem with the
-average risk of a multiple hypothesis testing problem.} For this, we first need
+We start by lower bounding the maximum risk of the estimation problem with the
+average risk of a multiple hypothesis testing problem. For this, we first need
 to define a $2\delta$-packing.%
@@
 The superscripts ``$n$'' remind us that these are $n$-fold product
-distributions, since we have $n$ i.i.d. trials used in the estimate.  The
+distributions, since we have $n$ i.i.d.\ trials used in the estimate.  The
 difficulty in Le Cam's method lies in selecting the two hypotheses to trade-off
@@
 in source localization goes to zero, as the number of sensors goes to infinity.
-\textcolor{blue}{
-This observation is qualitatively different from the information-theoretic
-lower bound given in~\cite{Grover2016Fundamental}, where even with an infinite
-number of sensors, the lower bound is strictly greater than zero. This
-indicates that the bound in section~\ref{sec:lecam-lb} is failing to capture
-some effect which leads to saturation of error, as the number of sensors
-increases.
-}
+This observation is contradicts the information-theoretic lower bound given
+in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
+the lower bound is strictly greater than zero. This indicates that the bound in
+section~\ref{sec:lecam-lb} is failing to capture some effect which leads to
+saturation of error as the number of sensors increases.
 
@@
 large number of sensors can be squeezed into a finite amount of space, and that
-these sensors \emph{still} give us i.i.d.\ observations, with the same noise
-variance. This is aphysical, since in reality, each sensor has a certain width,
-and the value measured by it is the integral of the continuous-space signal
-within that width (analogous to a sample-and-hold circuit, which integrates a
-continuous-\emph{time} signal over a short period).  If the width of a sensor
-is decreased, then effectively, its signal-to-noise ratio reduces.  This is
-intuitively evident in the sample-and-hold analogy: to compute the signal
-value, the integral must be divided by the time interval over which the
-integration is performed; this division amplifies noise as the time interval
-gets smaller.
+these sensors \emph{still} have the same SNR.  This is aphysical, since in
+reality, each sensor has a certain width, and the value measured by it is the
+integral of the continuous-space signal within that width (analogous to a
+sample-and-hold circuit, which integrates a continuous-\emph{time} signal over
+a short period).  If the width of a sensor is decreased, then effectively, its
+SNR reduces.  This is intuitively evident in the sample-and-hold analogy: to
+compute the signal value, the integral must be divided by the time interval
+over which the integration is performed; this division amplifies noise as the
+time interval gets smaller.
 
@@
 \end{equation}
-\textcolor{blue}{
 The noise vector $\v \epsilon$ is also generated similarly, by integrating over
-small sections of a wide-sense-stationary white noise process, which is assumed
-to additively corrupt the continuous-space signal $x(s;\theta)$ prior to
-sampling. This leads to i.i.d.\ noise values at sensors (since they do not
-overlap), with variance inversely proportional to $m$, i.e., $\sigma(m) \propto
-1/\sqrt{m}$.
-}
+small sections of a white noise process, which is assumed to additively corrupt
+the continuous-space signal $x(s;\theta)$ prior to sampling. This leads to
+i.i.d.\ noise values at sensors (since they do not overlap), with variance
+inversely proportional to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$.
 
 The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
-admits a solution which gives a bound for all values of $m$. We instead compute
-the bound numerically, using exact expressions for error probability in a
-binary hypothesis test. For gaussian distributions of equal variance and a
-uniform prior on the hypotheses, the minimum possible error probability (over
-all tests) is a Q-function in the distance between their
+admits a closed-form solution which gives a bound for all values of $m$. We
+instead compute the bound numerically, using exact expressions for error
+probability in a binary hypothesis test. For Gaussian distributions of equal
+variance and a uniform prior on the hypotheses, the minimum possible error
+probability (over all tests) is a $Q$-function in the distance between their
 means~\cite{NPLemmaOrSimilar},
@@
 \end{equation}
-where $Q(x) = \int_x^\infty \frac{1}{\sqrt{2\pi u}} e^{-u^2/2} du$. Hence, from
+where $Q(x) = \int_x^\infty \frac{1}{\sqrt{2\pi}} e^{-u^2/2} du$. Hence, from
 Theorem~\ref{thm:est-to-testing},
@@
 	\centering
-	\includegraphics[width=3.2in]{lb-vs-numsensors-int}
+	\includegraphics[width=2.8in]{lb-vs-m-annotated}
 	\caption{A numerically generated plot of the lower bound on minimax risk of
@@
 
-\textcolor{blue}{
 Another point on sensor placement bears repeating: the bounds derived in this
@@
 smallest, so that the ratio of mean-sensor-value to noise variance (a form of
-``SNR'') is minimized.
-}
+SNR) is minimized.
 

### 2017-01-25 q-function-test/q_fn_test.py

@@ -85,5 +85,6 @@ if __name__ == '__main__':
     plt.text(40, 3e-4, '$n = 10$', fontsize=18)
     plt.text(40, 2e-6, '$n = 100$', fontsize=18)
     plt.text(40, 2e-7, '$n = 1000$', fontsize=18)
+    plt.text(1, 1e-7, '$\sigma^2 = 10^{-4}$', fontsize=18)
     plt.tight_layout()
     plt.show()

### 2017-01-25 paper.tex
Add paragraph about compressive sensing.

@@
 large number of sensors can be squeezed into a finite amount of space, and that
-these sensors \emph{still} have the same SNR.  This is aphysical, since in
+these sensors \emph{still} have the same SNR.  This is non-physical, since in
 reality, each sensor has a certain width, and the value measured by it is the
@@
 
-%This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
-%separated by a distance of $2\delta$.
-%As $\delta$ increases, it becomes
-%easier to distinguish between the two hypotheses, so $P_e$ falls. When
-%numerically evaluating the bound, therefore, we have to \emph{manually}
-%trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
-%comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
-%hypotheses to distinguish between. To make the simulation easier, we can relax
-%the process of finding the least discernable hypothesis pair by fixing
-%$\theta_0$. Then, we need only optimize over $\delta$, making the process more
-%tractable. This comes at the cost of loosening the lower bound.
-
 \begin{figure}[t]
@@
 variance, in turn, can be reduced by averaging over multiple trials.
+
+\section{Discussion}
+\label{sec:discussion}
+
+While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
+for a large number of sensors, it still gives some important insights. For
+instance, if we assume that sensors have a constant width $c$, then even if we
+view sensors as integrators, the bound tells us something about the scaling of
+error with number of sensors, up to $m = \floor*{\frac{S}{c}}$. Beyond this
+point, averaging noise by increasing the number of trials may help one get to a
+target mean squared error in location. An analytical derivation of the
+trade-off between $m$ and $n$ in achieving a certain target MSE is relegated to
+future work.
+
+We also note that the minimax bounds from compressive sensing
+literature~\cite{AriasCastro2013Fundamental} do not apply in our setting,
+because those consider the problem of recovering the whole source signal,
+$x(s;\theta)$. The loss function used there is hence the energy of the
+difference signal $\int \abs{x(s) - \hat x(s)}^2 ds$. We, on the other hand,
+are interested in bounding the minimax error in \emph{location}, i.e.,
+$\abs{\theta - \hat\theta}^2$.
+
+While the bounds in section~\ref{sec:lecam-lb} were derived for a
+one-dimensional circular domain, extensions to a one-dimensional linear domain
+(of fixed length) and to a $d$-dimensional domain (circular or linear) are
+fairly straightforward, under certain conditions. For a 1D linear domain, we
+require that sensors capture the entirety of the impulse response even at the
+edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
+S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
+Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
+independent one-dimensional problems. Such extensions substantially broaden the
+number of settings in which this bound applies.
+
+Another point on sensor placement bears repeating: the bounds derived in this
+paper apply to only a specific sensor configuration, i.e., the uniform one.
+Intuitively, this is the correct choice in the minimax setting, since any
+non-uniform placement will have one or more points which is far from all
+sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
+$\theta$ for which the value of the impulse response at the sensors is
+smallest, so that the ratio of mean-sensor-value to noise variance (a form of
+SNR) is minimized.
+
+%The lower bounding \emph{technique} itself gives certain inisights on the issue
+%of sensor placement. Suppose we wanted to achieve a higher resolution in a
+%restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
+%\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
+%to place sensors \emph{not} precisely over $[a, b]$, but rather in the region
+%\emph{surrounding} $[a, b]$, corresponding to the \emph{largest change} in the
+%impulse response. Indeed, it is possible to derive an approximate lower bound
+%using Taylor's approximation, which shows that the KL-divergence between
+%distributions is maximized (and hence error minimized) at regions where the
+%slope of $x(s;\theta)$ is largest.
 
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
-for a large number of sensors, it still gives some important insights. For
-instance, if we assume that sensors have a constant width $c$, then even if we
-view sensors as integrators, the bound tells us something about the scaling of
-error with number of sensors, up to $m = \floor*{\frac{S}{c}}$. Beyond this
-point, averaging noise by increasing the number of trials may help one get to a
-target mean squared error in location. An analytical derivation of the
-trade-off between $m$ and $n$ in achieving a certain target MSE is relegated to
-future work.
-
-While the bounds in section~\ref{sec:lecam-lb} were derived for a
-one-dimensional circular domain, extensions to a one-dimensional linear domain
-(of fixed length) and to a $d$-dimensional domain (circular or linear) are
-fairly straightforward, under certain conditions. For a 1D linear domain, we
-require that sensors capture the entirety of the impulse response even at the
-edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
-S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
-Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
-independent one-dimensional problems.
-
-Another point on sensor placement bears repeating: the bounds derived in this
-paper apply to only a specific sensor configuration, i.e., the uniform one.
-Intuitively, this is the correct choice in the minimax setting, since any
-non-uniform placement will have one or more points which is far from all
-sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
-$\theta$ for which the value of the impulse response at the sensors is
-smallest, so that the ratio of mean-sensor-value to noise variance (a form of
-SNR) is minimized.
-
-%The lower bounding \emph{technique} itself gives certain inisights on the issue
-%of sensor placement. Suppose we wanted to achieve a higher resolution in a
-%restricted interval of the parameter space, i.e.\ $\theta \in [a, b] \subset
-%\Theta$, such that $\abs{b - a} \ll w$. Then, it might be of greatest benefit
-%to place sensors \emph{not} precisely over $[a, b]$, but rather in the region
-%\emph{surrounding} $[a, b]$, corresponding to the \emph{largest change} in the
-%impulse response. Indeed, it is possible to derive an approximate lower bound
-%using Taylor's approximation, which shows that the KL-divergence between
-%distributions is maximized (and hence error minimized) at regions where the
-%slope of $x(s;\theta)$ is largest.
-
 %\IEEEtriggeratref{8}

### 2017-01-25 paper.tex
Make major edits to foreshadow sensor size issue.

@@
 \newtheorem{definition}{Definition}
+
+\setlength{\textfloatsep}{10pt}
 
@@
 source~\cite{Cavalier2002Sharp}. Work that \emph{does} address point sources
-and location-based error metrics~\cite{Ibragimov1981Statistical} does not, to
-our knowledge, address scaling in the number of sensors.
+and location-based error metrics~\cite[Ch.~7, Sec.~2]{Ibragimov1981Statistical}
+does not, to our knowledge, address scaling in the number of sensors.
 
@@
 through a diffusive medium (treated as a low-pass filter), and corrupted by
-additive white Gaussian noise. We describe the problem setting in detail in
+additive white Gaussian noise. We are also the first to analyze the
+implications physical sensor models on such lower bounds. A simplistic
+theoretical model might assume that the number of sensors can increase
+unbounded, while maintaining a fixed SNR at each sensor. We show that this is
+not physically possible in our setting, and derive numerical bounds which have
+radically different asymptotic behaviour.
+
+We describe the problem setting in detail in
 Section~\ref{sec:source-localization} and the minimax techniques and our main
-results (for a naive and then for a more physical sensor model) in
+results (for a na\"ive and then for a more physical sensor model) in
 Section~\ref{sec:minimax-lower-bounds}. We conclude in
@@
 
-The sensors sample the shifted continuous-space impulse response, with some
-additive noise. We denote the noiseless sampled version of $x(s; \theta)$ by
-the $m$-length vector $\v x(\theta)$:
+\subsection{Sensor and noise models}
+\label{sec:sensor-model}
+
+We consider two sensor models: a simplistic ``point sensor'' model and an
+``integrator sensor'' model, to be used in sections~\ref{sec:lecam-lb}
+and~\ref{sec:physical-model} respectively.
+
+In the ``point sensor model'', sensors \emph{sample} the shifted
+continuous-space impulse response, with some additive noise. We denote the
+noiseless sampled version of $x(s; \theta)$ by the $m$-length vector $\v
+x(\theta)$,
 \begin{equation} \label{eq:sampled-signal}
-	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m-1)S}{m}; \theta\Big)\bigg]^T
+	\v x(\theta) = \bigg[x(0; \theta), \ldots, x\Big(\frac{kS}{m}; \theta\Big), \ldots, x\Big(\frac{(m{-}1)S}{m}; \theta\Big)\bigg]^T
 \end{equation}
-where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. The
-additive noise is given by $\v \epsilon$ (to be described shortly), and the
-noisy samples are represented by
+where $m$ is the number of sensors and $k \in \{0, 1, \ldots, m-1\}$. Additive
+noise $\v \epsilon$ corrupts $\v x(\theta)$ to produce the noisy sensor values
 \begin{equation} \label{eq:sensor-obs}
@@
 \end{equation}
-In the source localization problem, we receive $n$ trials\footnote{The word
-``trials'' comes from neuroscience literature, where several trials of an
-experiment are run with a single participant. The participant is given the same
-stimulus in each trial, evoking the same response in the brain (usually with
-some trial-to-trial variability). For our purposes, we assume that trials are
-effectively i.i.d.\ realizations of sensor noise, with no trial-to-trial
-variability.} (i.e., $n$ realizations) of $\v y$ according to
-equation~\eqref{eq:sensor-obs}, for the same point source $\theta$, using which
-we need to estimate the location of the source.
-The complete signal model described in this section is summarized in
-Fig.~\ref{fig:signal-model}.
+The noise $\v \epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim
+\mathcal{N}(\v 0, \m \Sigma)$. We restrict our analysis to a ``sensor noise''
+setting, wherein $\m\Sigma = \sigma^2 \m I$, i.e., noise is i.i.d.\ across
+sensors.
 
-\subsection{Channel model}
-\label{sec:channel-model}
+In the ``integrator sensor'' model, sensors have a \emph{width} which decreases
+as their number grows to infinity. Concretely, the $k$-th sensor which is
+located at $s = kS/m$ \emph{occupies} the space $((k{-}\frac{1}{2})S/m,
+(k{+}\frac{1}{2})S/m)$.  The signal sensed by this sensor is given by the
+$k$-th element of $\v x(\theta)$,
+\begin{equation}
+	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds.
+\end{equation}
+In this model, the noise vector $\v \epsilon$ is also generated similarly, by
+integrating over small sections of a white noise process, which is assumed to
+additively corrupt the continuous-space signal $x(s;\theta)$ \emph{prior} to
+sampling (see Fig.~\ref{fig:signal-model}). This leads to i.i.d.\ noise values
+at sensors (since sensors have no overlap), with variance inversely
+proportional to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$.
 
-The noise $\v \epsilon$, introduced in equation~\eqref{eq:sensor-obs}, is the
-only source of uncertainty in the problem. For our purposes, we assume that $\v
-\epsilon$ is zero-mean and Gaussian, $\v \epsilon \sim \mathcal{N}(\v 0, \m
-\Sigma)$. We restrict our analysis to a ``sensor noise'' setting, wherein
-$\m\Sigma = \sigma^2 \m I$, i.e., noise is i.i.d.\ across sensors.
-
-The noise is also assumed to be i.i.d.\ across trials, i.e., the $n$
-realizations of $\v y$ are independently drawn from $P(\theta)$, for the
-same location parameter $\theta$.
+In the source localization problem, we receive $n$ ``trials''\footnote{The word
+	``trials'' comes from neuroscience literature, where multiple trials of an
+	experiment are run, with the same stimulus being given to the participant
+	in each trial, evoking the same response in the brain (with some
+trial-to-trial variability, which we ignore). For our purposes, we assume that
+trials are effectively i.i.d.\ realizations of sensor noise.} (i.e., $n$
+realizations) of $\v y$ according to equation~\eqref{eq:sensor-obs}, for the
+\emph{same} point source $\theta$, using which we need to estimate the location
+of the source.  The noise is also assumed to be i.i.d.\ across trials, i.e.,
+the $n$ realizations of $\v y$ are independently drawn from $P(\theta)$, for
+the same location parameter $\theta$.
 
@@
 
-Thus, the final lower bound can be written as:
+Thus, the final lower bound can be written as
 \begin{equation} \label{eq:le-cam-bound}
-	\mathfrak{M}_n(\mathcal P, \Phiorho) \geq \frac{\Phi(\delta)}{2} \big(1 - \norm{P_1^n - P_0^n}_{TV}\big)
+	\mathfrak{M}_n(\mathcal P, \Phiorho) \geq \frac{\Phi(\delta)}{2} \big(1 - \norm{P_1^n - P_0^n}_{TV}\big).
 \end{equation}
@@
 \label{sec:lecam-lb}
-
-For the source localization problem, we measure \emph{risk} in terms of the
-squared-distance between the true location and the estimated location. Hence,
-our loss function is $\Phi(\rho(\theta, \hat\theta)) = \abs{\theta -
-\hat\theta}^2$, where $\hat\theta$ is some estimate of the location based on
-$n$ trials of the noisy sensor observations $\v y$.
 
@@
 
-We now state the main result of this paper.
+For the source localization problem, we measure \emph{risk} in terms of the
+squared-distance between the true location and the estimated location. Hence,
+our loss function is $\Phi(\rho(\theta, \hat\theta)) = \abs{\theta -
+\hat\theta}^2$, where $\hat\theta$ is some estimate of the location based on
+$n$ trials of the noisy sensor observations $\v y$. We now state the main
+result of this paper.
 \begin{theorem} \label{thm:main-lb}
@@
 	location of a point source is lower bounded by
-	\begin{equation}
+	\begin{equation*}
 		\mathfrak{M}_n(\mathcal{P}, \Phi\circ\rho) \geq \sup_{0 < \delta < S/4} \frac{\delta^2}{2} \Bigg[1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2}\bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg)} \Bigg]
-	\end{equation}
+	\end{equation*}
 	For sufficiently large $m$, the bound can be approximated by
@@
 \mathcal{N}(\v x(\theta_i), \sigma^2 \m I)$, as described in
-section~\ref{sec:channel-model}. Hence, combining
+section~\ref{sec:sensor-model}. Hence, combining
 equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
@@
 \begin{equation} \label{eq:delta-bound}
-	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor*{\frac{(w + 2\delta)m}{S} + 1} \leq 4 \kappa^2 \delta^2 \Big(\frac{(w + 2\delta) m}{S} + 1\Big).
+	\norm{\v\Delta}^2 \leq 4 \kappa^2 \delta^2 \floor[\Big]{\!\frac{(w{+}2\delta)m}{S} + 1\!} \leq 4 \kappa^2 \delta^2 \bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg).
 \end{equation}
@@
 \subsection{Towards a more physical sensor model}
+\label{sec:physical-model}
 
@@
 in source localization goes to zero, as the number of sensors goes to infinity.
-This observation is contradicts the information-theoretic lower bound given
+This observation contradicts the information-theoretic lower bound given
 in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
@@
 a short period). If the width of a sensor is decreased, then effectively, its
-SNR reduces.  This is intuitively evident in the sample-and-hold analogy: to
-compute the signal value, the integral must be divided by the time interval
-over which the integration is performed; this division amplifies noise as the
-time interval gets smaller.
+SNR reduces (this is explained in Appendix~\ref{app:integrator-snr} in the
+full version of this paper~\cite{FullVersion}).
 
-We performed a preliminary study to understand the effect of viewing sensors as
-integrators. In the new sensor model, sensors have a width which decreases as
-their number grows to infinity. Concretely, the $k$-th sensor which is located
-at $s = kS/m$ extends from $(k{-}\frac{1}{2})S/m$ to $(k{+}\frac{1}{2})S/m$.
-The signal sensed by this sensor is the $k$-th element of $\v x(\theta)$, now
-given by
-\begin{equation}
-	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds
-\end{equation}
-The noise vector $\v \epsilon$ is also generated similarly, by integrating over
-small sections of a white noise process, which is assumed to additively corrupt
-the continuous-space signal $x(s;\theta)$ prior to sampling. This leads to
-i.i.d.\ noise values at sensors (since they do not overlap), with variance
-inversely proportional to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$.
+%This is intuitively evident in the sample-and-hold analogy: to compute the
+%signal value, the integral must be divided by the time interval over which the
+%integration is performed; this division amplifies noise as the time interval
+%gets smaller.
 
-The bounding technique used in section~\ref{sec:lecam-lb} no longer easily
-admits a closed-form solution which gives a bound for all values of $m$. We
-instead compute the bound numerically, using exact expressions for error
-probability in a binary hypothesis test. For Gaussian distributions of equal
-variance and a uniform prior on the hypotheses, the minimum possible error
-probability (over all tests) is a $Q$-function in the distance between their
-means~\cite{NPLemmaOrSimilar},
+We performed a preliminary study to understand the effect of using the
+``integrator sensor'' model defined in section~\ref{sec:sensor-model}.  The
+bounding technique used in section~\ref{sec:lecam-lb} no longer easily admits a
+closed-form solution which gives a bound for all values of $m$. We instead
+compute the bound numerically, using exact expressions for error probability in
+a binary hypothesis test. For Gaussian distributions of equal variance and a
+uniform prior on the hypotheses, the minimum possible error probability (over
+all tests) is a $Q$-function in the distance between their
+means~\cite[Ch.~7]{Scharf1991Statistical},
 \begin{equation}
@@
 packings, we relax the process by fixing $\theta_0 = 0$ and optimizing over
-$\theta_1 = 2\delta$.  We compute sensor values by performing numerical
-integration, and find the best possible $\delta$ by grid search.
+$\theta_1 = 2\delta$.  We compute sensor values for a triangular impulse
+response, by performing numerical integration, and find the best possible
+$\delta$ by grid search.
 
@@
 		sensors, $m$, used to estimate the location. The different curves are
-		for different numbers of ``trials'' $n$ (i.i.d.\ sensor observations).
-		The bound saturates for large $m$, indicating that for a fixed number
-		of trials (or equivalently, for a fixed SNR), there is reduced benefit
-		in increasing the number of sensors beyond a point. However, with more
-		trials, the bound saturates at increasingly larger numbers of sensors.
-	Thus, there is benefit to increasing the number of sensors, provided SNR
-can be increased by leveraging larger numbers of trials.}
+		for different numbers of ``trials'', $n$ (number of i.i.d.\ sensor
+		observations). The bound saturates for large $m$, indicating that for
+		a \emph{fixed} number of trials, there is decreasing benefit to using
+		more sensors.  However, with more trials, the bound saturates at
+		increasingly larger numbers of sensors. Thus, there may be benefit to
+	increasing the number of sensors when you have more trials.}
 	\label{fig:numerical}
@@
 sensors. In other words, there is increased benefit in using larger numbers of
-sensors, when we also have more trials\footnote{Recall that the number of
-``trials'' is the number of i.i.d.\ sensor observations we receive, per
-equation~\ref{eq:sensor-obs}.}. This substantiates the intuition given
+sensors, when we also have more trials. This substantiates the intuition given
 in~\cite{Grover2016Information}, which addresses this issue using a
@@
 While the bounds in section~\ref{sec:lecam-lb} were derived for a
-one-dimensional circular domain, extensions to a one-dimensional linear domain
-(of fixed length) and to a $d$-dimensional domain (circular or linear) are
-fairly straightforward, under certain conditions. For a 1D linear domain, we
-require that sensors capture the entirety of the impulse response even at the
-edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
-S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
+one-dimensional circular domain, extensions to a 1D linear domain (of fixed
+length) and to a $d$-dimensional domain (circular or linear) are fairly
+straightforward, under certain conditions. For a 1D linear domain, we require
+that sensors capture the entirety of the impulse response even at the edges of
+the domain. Hence, sensors must be placed uniformly in $[-w/2, S{+}w/2]$. For
+extending to $d$ dimensions, it suffices to apply Assouad's
 Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
-independent one-dimensional problems. Such extensions substantially broaden the
-number of settings in which this bound applies.
+independent 1D problems. Such extensions substantially broaden the number of
+settings in which this bound applies.
 
-Another point on sensor placement bears repeating: the bounds derived in this
-paper apply to only a specific sensor configuration, i.e., the uniform one.
-Intuitively, this is the correct choice in the minimax setting, since any
-non-uniform placement will have one or more points which is far from all
-sensors. The ``maximization'' over $\theta \in \Theta$ would then select a
-$\theta$ for which the value of the impulse response at the sensors is
-smallest, so that the ratio of mean-sensor-value to noise variance (a form of
-SNR) is minimized.
+Also note, the bounds derived in this paper apply only when sensors are
+uniformly distributed.  Intuitively, this is the correct choice in the minimax
+setting, since any non-uniform placement will have one or more points which is
+far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
+select a $\theta$ for which the value of the impulse response at the sensors is
+smallest, so that SNR is minimized.
 
@@
 
+\newpage
+
+\appendices
+
+\section{SNR in the integrator model}
+\label{app:integrator-snr}
+
 \end{document}

### 2017-01-26 paper.tex
Make most final edits.

@@
 estimating the location of the source, which apply to all estimators, for
-certain classes of diffusive media represented by low-pass
-filters, when using a uniformly distributed sensor array. We show that
-for sensors of a fixed size, the lower bound decays with
+certain classes of diffusive media, when using a uniformly distributed sensor
+array. We show that for sensors of a fixed size, the lower bound decays with
 increasing numbers of sensors. We also perform a preliminary numerical analysis
 to understand the effect of increasing the number of sensors to infinity by
-shrinking their size, wherein the bound saturates for large sensor numbers.
-In the second scenario, it is seen that there is greater
-benefit to increasing the number of sensors as the signal-to-noise increases.
-Our bounds are the first to give a scaling for the minimax risk in terms of the
-number of sensors used.
+shrinking their size, wherein the bound saturates for large sensor numbers.  In
+the second scenario, it is seen that there is greater benefit to increasing the
+number of sensors as the signal-to-noise ratio increases.  Our bounds are the
+first to give a scaling for the minimax risk in terms of the number of sensors
+used.
 
@@
 locations~\cite{Baillet2001Electromagnetic}. For a single activated dipole
-within the brain (which is modeled as a point source), the electrodes
-effectively sample a diffuse (blurred) representation of the dipole, as a
-result of the spatial low-pass filtering effect of the different layers between
-the brain surface and scalp surface (cerebrospinal fluid, skull and skin).
+within the brain (which is modeled as a point source), the electrodes sample a
+diffuse (blurred) representation of the dipole, as a result of the spatial
+low-pass filtering effect of the different layers of the skull, between the
+brain and scalp.
 
@@
 
-Hence, we believe that this paper is the first to give lower bounds on source
-localization error (measured in an $\ell_2$-distance sense) in estimating the
-location of a one-dimensional point source, which is observed by sensors
-through a diffusive medium (treated as a low-pass filter), and corrupted by
-additive white Gaussian noise. We are also the first to analyze the
-implications physical sensor models on such lower bounds. A simplistic
-theoretical model might assume that the number of sensors can increase
-unbounded, while maintaining a fixed SNR at each sensor. We show that this is
-not physically possible in our setting, and derive numerical bounds which have
-radically different asymptotic behaviour.
+Hence, we believe that this paper is the first to give lower bounds on the
+minimax error in estimating the location of a point source, which is observed
+by sensors through a diffusive medium, and corrupted by additive white Gaussian
+noise. We are also the first to analyze the implications physical sensor models
+on such lower bounds. A simplistic theoretical model might assume that the
+number of sensors can increase unbounded, while maintaining a fixed SNR at each
+sensor. We show that this is not physically possible in our setting, and derive
+numerical bounds which have radically different asymptotic behaviour.
 
-We describe the problem setting in detail in
-Section~\ref{sec:source-localization} and the minimax techniques and our main
-results (for a na\"ive and then for a more physical sensor model) in
-Section~\ref{sec:minimax-lower-bounds}. We conclude in
-Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
-and on how our results can be extended to other simple settings.
+We describe the problem setting in Section~\ref{sec:source-localization} and
+the minimax techniques and our main results (for a na\"ive and then for a more
+physical sensor model) in Section~\ref{sec:minimax-lower-bounds}. We conclude
+in Section~\ref{sec:discussion} with a discussion on the goodness of our
+bounds, and on how our results can be extended to other settings.
 
@@
 
-In the ``point sensor model'', sensors \emph{sample} the shifted
+In the ``point sensor'' model, sensors \emph{sample} the shifted
 continuous-space impulse response, with some additive noise. We denote the
@@
 In the ``integrator sensor'' model, sensors have a \emph{width} which decreases
-as their number grows to infinity. Concretely, the $k$-th sensor which is
-located at $s = kS/m$ \emph{occupies} the space $((k{-}\frac{1}{2})S/m,
+as their number grows to infinity. Concretely, the \mbox{$k$-th} sensor which
+is located at $s = kS/m$ \emph{occupies} the space $((k{-}\frac{1}{2})S/m,
 (k{+}\frac{1}{2})S/m)$.  The signal sensed by this sensor is given by the
@@
 \end{equation}
-In this model, the noise vector $\v \epsilon$ is also generated similarly, by
-integrating over small sections of a white noise process, which is assumed to
-additively corrupt the continuous-space signal $x(s;\theta)$ \emph{prior} to
-sampling (see Fig.~\ref{fig:signal-model}). This leads to i.i.d.\ noise values
-at sensors (since sensors have no overlap), with variance inversely
-proportional to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$.
-
-In the source localization problem, we receive $n$ ``trials''\footnote{The word
-	``trials'' comes from neuroscience literature, where multiple trials of an
-	experiment are run, with the same stimulus being given to the participant
-	in each trial, evoking the same response in the brain (with some
-trial-to-trial variability, which we ignore). For our purposes, we assume that
-trials are effectively i.i.d.\ realizations of sensor noise.} (i.e., $n$
-realizations) of $\v y$ according to equation~\eqref{eq:sensor-obs}, for the
-\emph{same} point source $\theta$, using which we need to estimate the location
-of the source.  The noise is also assumed to be i.i.d.\ across trials, i.e.,
-the $n$ realizations of $\v y$ are independently drawn from $P(\theta)$, for
-the same location parameter $\theta$.
+Here, a white noise process $\epsilon(s)$ additively corrupts the
+continuous-space signal $x(s;\theta)$ prior to sampling (see
+Fig.~\ref{fig:signal-model}). $\v \epsilon$ is generated by integrating
+$\epsilon(s)$ over a sensor width. This leads to i.i.d.\ noise values at
+sensors (since sensors have no overlap), with variance inversely proportional
+to $m$, i.e., $\sigma(m) \propto 1/\sqrt{m}$ (refer
+Appendix~\ref{app:integrator-snr} in the full version of this
+paper~\cite{FullVersion} for an explanation).
 
@@
 
+In the source localization problem, we receive $n$ ``trials''\footnote{The word
+	``trials'' comes from neuroscience literature, where multiple trials of an
+	experiment are run, with the same stimulus being given to the participant
+	in each trial, evoking the same response in the brain (with some
+trial-to-trial variability, which we ignore). For our purposes, we assume that
+trials are i.i.d.\ realizations of sensor noise.} of $\v y$ according to
+equation~\eqref{eq:sensor-obs}, for the \emph{same} point source $\theta$,
+using which we need to estimate the location of the source. Note that noise is
+assumed to be i.i.d.\ across trials, i.e., the $n$ realizations of $\v y$ are
+independently drawn from $P(\theta)$, for the same location parameter $\theta$.
+
 \begin{figure}[tp] %  figure placement: here, top, bottom, or page
 	\centering
-	\includegraphics[width=3.5in]{block-diagram}
-	\caption{A diagrammatic representation of the signal model described in
+	\includegraphics[width=3.2in]{block-diagram}
+	\caption{A block diagram of the two sensor models described in
 	section~\ref{sec:signal-model}.}
@@
 
-We performed a preliminary study to understand the effect of using the
-``integrator sensor'' model defined in section~\ref{sec:sensor-model}.  The
-bounding technique used in section~\ref{sec:lecam-lb} no longer easily admits a
-closed-form solution which gives a bound for all values of $m$. We instead
-compute the bound numerically, using exact expressions for error probability in
-a binary hypothesis test. For Gaussian distributions of equal variance and a
-uniform prior on the hypotheses, the minimum possible error probability (over
-all tests) is a $Q$-function in the distance between their
-means~\cite[Ch.~7]{Scharf1991Statistical},
+This observation motivates the ``integrator sensor'' model defined in
+section~\ref{sec:sensor-model}. With this model, the bounding technique used in
+section~\ref{sec:lecam-lb} no longer easily admits a closed-form solution which
+gives a bound for all values of $m$. We instead compute the bound numerically,
+using exact expressions for error probability in a binary hypothesis test. For
+Gaussian distributions of equal variance and a uniform prior on the hypotheses,
+the minimum possible error probability (over all tests) is a $Q$-function in
+the distance between their means~\cite[Ch.~7]{Scharf1991Statistical},
 \begin{equation}
@@
 		source localization, against the number of uniformly distributed
-		sensors, $m$, used to estimate the location. The different curves are
-		for different numbers of ``trials'', $n$ (number of i.i.d.\ sensor
-		observations). The bound saturates for large $m$, indicating that for
-		a \emph{fixed} number of trials, there is decreasing benefit to using
-		more sensors.  However, with more trials, the bound saturates at
-		increasingly larger numbers of sensors. Thus, there may be benefit to
-	increasing the number of sensors when you have more trials.}
+		sensors, $m$, used to estimate the location (code available
+		online~\cite{Code}). The different curves are for different numbers of
+		``trials'', $n$ (number of i.i.d.\ sensor observations). The bound
+		saturates for large $m$, indicating that for a \emph{fixed} number of
+		trials, there is decreasing benefit to using more sensors.  However,
+	with more trials, the bound saturates at increasingly larger numbers of
+sensors. Thus, there may be benefit to increasing the number of sensors when
+you have more trials.}
 	\label{fig:numerical}
@@
 
-Plotting this numerically computed bound for different numbers of trials (see
-Fig.~\ref{fig:numerical}) reveals some interesting trends. First, the bound
-saturates as $m$ grows large, matching the behaviour presented
-in~\cite{Grover2016Fundamental}. Second, the lower bound on error is larger for
+Plotting this numerically-computed bound for different numbers of trials
+reveals some interesting trends (see Fig.~\ref{fig:numerical}). First, the
+bound saturates as $m$ grows large, matching the behaviour of the
+information-theoretic bound. Second, the lower bound on error is larger for
 smaller numbers of sensors, as we expect. Third and most importantly, as the
-number of trials increases, bound begins to saturate only for larger numbers of
-sensors. In other words, there is increased benefit in using larger numbers of
-sensors, when we also have more trials. This substantiates the intuition given
-in~\cite{Grover2016Information}, which addresses this issue using a
-Nyquist-rate perspective. A larger number of sensors will sample a larger
-number of high-frequency components of the source signal (and hence allow us to
-locate it better), but only if the noise floor is sufficiently low. Noise
-variance, in turn, can be reduced by averaging over multiple trials.
+number of trials increases, the bound begins to saturate only at a larger
+number of sensors. In other words, there is \emph{increased} benefit in using
+larger numbers of sensors, when we \emph{also} have more trials. This
+substantiates the intuition given in~\cite{Grover2016Information}, which makes
+this point using a Nyquist-rate argument: a larger number of sensors will
+sample a larger number of high-frequency components of the source signal (and
+hence allow us to locate it better), but only if the noise floor is
+sufficiently low. Noise variance, in turn, can be reduced by averaging over
+multiple trials.
 
@@
 We also note that the minimax bounds from compressive sensing
-literature~\cite{AriasCastro2013Fundamental} do not apply in our setting,
-because those consider the problem of recovering the whole source signal,
-$x(s;\theta)$. The loss function used there is hence the energy of the
-difference signal $\int \abs{x(s) - \hat x(s)}^2 ds$. We, on the other hand,
-are interested in bounding the minimax error in \emph{location}, i.e.,
+literature~\cite{AriasCastro2013Fundamental} \emph{do not} apply in our
+setting, because those consider the problem of recovering the \emph{whole}
+source signal, $x(s;\theta)$. The loss function used there is hence the energy
+of the difference signal, $\int \abs{x(s) - \hat x(s)}^2 ds$. We, on the other
+hand, are interested in bounding the minimax error in \emph{location}, i.e.,
 $\abs{\theta - \hat\theta}^2$.
@@
 Also note, the bounds derived in this paper apply only when sensors are
-uniformly distributed.  Intuitively, this is the correct choice in the minimax
-setting, since any non-uniform placement will have one or more points which is
-far from all sensors. The ``maximization'' over $\theta \in \Theta$ would then
-select a $\theta$ for which the value of the impulse response at the sensors is
-smallest, so that SNR is minimized.
+uniformly distributed.  Intuitively, this is the \emph{correct} choice in the
+minimax setting, since any non-uniform placement will have one or more points
+which is far from all sensors. The ``maximization'' over $\theta \in \Theta$
+would then select a $\theta$ for which the value of the impulse response at the
+sensors is smallest, so that SNR is minimized.
 

### 2017-01-26 q-function-test/q_fn_test.py

@@ -51,14 +51,11 @@ def compute_bound(M):
         x0[j] = np.sum(x0_c[i]) * ds
         x1[:, j] = np.sum(x1_c[:, i], axis=1) * ds
 
-    #print(x0.shape)
-    #print(x1.shape)
-    #plt.plot(x1[100] - x0)
-    #plt.show()
-
+    # Compute min. distance and error probability
     dmin_by_2 = np.sqrt(np.sum((x1 - x0) ** 2, axis=-1)) / 2
     Pe = 0.5 - 0.5 * spl.erf(dmin_by_2 / np.sqrt(sigma2 / M / n))
 
+    # Plot bound before optimization to check proper maximiza available
     bound = delta**2 * Pe
     plt.figure()
     plt.semilogy(bound.T)

### 2017-02-05 paper.tex
Final version of the paper, without appendix.

@@
 array. We show that for sensors of a fixed size, the lower bound decays with
-increasing numbers of sensors. We also perform a preliminary numerical analysis
-to understand the effect of increasing the number of sensors to infinity by
-shrinking their size, wherein the bound saturates for large sensor numbers.  In
-the second scenario, it is seen that there is greater benefit to increasing the
+increasing numbers of sensors. We also analyze a more physical sensor model to
+understand the effect of shrinking the size of sensors as their number
+increases to infinity, wherein the bound saturates for large sensor numbers.
+In this scenario, it is seen that there is greater benefit to increasing the
 number of sensors as the signal-to-noise ratio increases.  Our bounds are the
@@
 noise. We are also the first to analyze the implications physical sensor models
-on such lower bounds. A simplistic theoretical model might assume that the
+have on such lower bounds. A simplistic theoretical model might assume that the
 number of sensors can increase unbounded, while maintaining a fixed SNR at each
@@
 $k$-th element of $\v x(\theta)$,
-\begin{equation}
+\begin{equation} \label{eq:samples-int-model}
 	x_k(\theta) = \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds.
@@
 Fig.~\ref{fig:signal-model}). $\v \epsilon$ is generated by integrating
-$\epsilon(s)$ over a sensor width. This leads to i.i.d.\ noise values at
+$\epsilon(s)$ over each sensor's width. This leads to i.i.d.\ noise values at
 sensors (since sensors have no overlap), with variance inversely proportional
@@
 	For a source localization problem as defined in
-	section~\ref{sec:source-localization}, the minimax risk in estimating the
-	location of a point source is lower bounded by
+	section~\ref{sec:source-localization} under the point sensor model, the
+	minimax risk in estimating the location of a point source is lower bounded
+	by
 	\begin{equation*}
@@
 		trials, there is decreasing benefit to using more sensors.  However,
-	with more trials, the bound saturates at increasingly larger numbers of
-sensors. Thus, there may be benefit to increasing the number of sensors when
-you have more trials.}
+		the plot suggests that with more trials, the bound saturates at
+		increasingly larger numbers of sensors. Thus, there may be benefit to
+		increasing the number of sensors when you have more trials.}
 	\label{fig:numerical}
@@
 number of sensors. In other words, there is \emph{increased} benefit in using
-larger numbers of sensors, when we \emph{also} have more trials. This
-substantiates the intuition given in~\cite{Grover2016Information}, which makes
-this point using a Nyquist-rate argument: a larger number of sensors will
-sample a larger number of high-frequency components of the source signal (and
-hence allow us to locate it better), but only if the noise floor is
-sufficiently low. Noise variance, in turn, can be reduced by averaging over
-multiple trials.
+more sensors, when we \emph{also} have more trials. This substantiates the
+intuition given in~\cite{Grover2016Information}, which makes this point using a
+Nyquist-rate argument: a larger number of sensors will sample a larger number
+of high-frequency components of the source signal (and hence allow us to locate
+it better), but only if the noise floor is sufficiently low. Noise variance, in
+turn, can be reduced by averaging over multiple trials.
 
@@
 setting, because those consider the problem of recovering the \emph{whole}
-source signal, $x(s;\theta)$. The loss function used there is hence the energy
-of the difference signal, $\int \abs{x(s) - \hat x(s)}^2 ds$. We, on the other
+source signal, $f(s;\theta)$. The loss function used there is hence the energy
+of the difference signal, $\int \abs{f(s) - \hat f(s)}^2 ds$. We, on the other
 hand, are interested in bounding the minimax error in \emph{location}, i.e.,

### 2017-02-05 paper.tex
WIP: Add appendix.

@@
 
+In the integrator model of sensors, recall that the samples are given by
+equation~\eqref{eq:samples-int-model}. We compute the SNR approximately at the
+$k$-th sensor as follows. The power of the signal is given by
+\begin{align}
+	\abs{x_k(\theta)}^2 &= \abs*{\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds.}^2 \\
+	&\approx \abs*{\frac{S}{m} x\Big(\frac{kS}{m}; \theta\Big)}^2 \\
+	&= \frac{S^2}{m^2} \abs*{x\Big(\frac{kS}{m}; \theta\Big)}^2
+\end{align}
+where in the approximation, we have assumed that the signal is roughly constant
+in a small interval, taking the value of the signal at $s = kS/m$. The constant
+itself is not relevant; it suffices to note at this point that the signal power
+diminishes as $1/m^2$ since the sensor size \emph{must} diminish as $1/m$, if
+the number of sensors has to increase to infinity.
+
+The noise variance at the $k$-th sensor is computed similarly:
+\begin{align}
+	\mathbb E[\epsilon_k^2] &= \mathbb E \Bigg[ \bigg(\int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s)\bigg)^2 \Bigg] \\
+	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s) ds \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s') ds' \Bigg] \\
+	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s) \epsilon(s') ds ds' \Bigg] \\
+	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \mathbb E[\epsilon(s) \epsilon(s')] ds ds' \\
+	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} R_\epsilon(s, s') ds ds' \\
+	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \delta(s - s') ds ds' \\
+	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} ds \\
+	&= \frac{S}{m}
+\end{align}
+where $R_\epsilon(s, s') = \delta(s - s')$ is the autocorrelation function of
+the white noise process.
+
 \end{document}

### 2017-02-06 paper.tex
Add acknowledgements and complete appendix.

--- 2017-02-05 paper.tex
@@
 
+\section*{Acknowledgements}
+
+This work was supported in part by Systems on Nanoscale Information fabriCs
+(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
+Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
+College of Engineering at Carnegie Mellon University. The authors would like to
+thank Philip and Marsha Dowd for their financial support and encouragement.
+
 \appendices
@@
 
+In the integrator model of sensors, recall that the samples are given by
+equation~\eqref{eq:samples-int-model}. We compute the SNR approximately at the
+$k$-th sensor as follows. The power of the signal is given by
+\begin{align}
+	\abs{x_k(\theta)}^2 &= \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds\bigg)^2 \\
+	&\approx \bigg(\frac{S}{m} \; x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 = \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \label{eq:signal-power-k},
+\end{align}
+where in the approximation, we have assumed that the signal is roughly constant
+in a small interval, taking the value of the signal at $s = kS/m$. The constant
+itself is not relevant; it suffices to note at this point that the signal power
+diminishes as $1/m^2$ since the sensor size \emph{must} diminish as $1/m$, if
+the number of sensors has to increase to infinity.
+
+The noise variance at the $k$-th sensor is computed similarly:
+\begin{align}
+	\mathbb E[\epsilon_k^2] &= \mathbb E \Bigg[ \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s)\bigg)^2 \Bigg] \\
+	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s) ds \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s') ds' \Bigg] \\
+	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s) \epsilon(s') ds ds' \Bigg] \\
+	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \mathbb E[\epsilon(s) \epsilon(s')] ds ds' \\
+	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} R_\epsilon(s, s') ds ds' \\
+	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \sigma^2 \delta(s - s') ds ds' \\
+	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \sigma^2 ds \\
+	&= \sigma^2 \frac{S}{m}, \label{eq:noise-var-k}
+\end{align}
+where $R_\epsilon(s, s') = \sigma^2 \delta(s - s')$ is the autocorrelation
+function of the white noise process, and $\sigma^2$ is the amplitude of the
+white noise power spectral density.
+
+We can understand how the SNR at the $k$-th sensor scales with $m$, therefore,
+by taking the ratio of~\eqref{eq:signal-power-k} and~\eqref{eq:noise-var-k}
+\begin{align}
+	\text{SNR}(k) &= \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \cdot \frac{m}{S\sigma^2} \\
+	&= \frac{S}{m\sigma^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \propto 1/m.
+\end{align}
+Hence, as the number of sensors $m$ grows to infinity, their sizes must
+necessarily reduce inversely with $m$, and as a result, their SNR also falls
+inversely with $m$, when we view these sensors as integrators.
+
 \end{document}

### 2017-02-06 q-function-test/q_fn_test.py
Increase y-axis tick label fontsize in figure.

@@ -77,7 +77,8 @@ if __name__ == '__main__':
     plt.xlabel('Number of sensors, $m$', fontsize=20)
     plt.ylabel('Lower bound, $\sup_{0<\delta<S/4} \delta^2 P_e$', fontsize=20)
     ax = plt.gca()
-    ax.tick_params(axis='both', which='major', labelsize=12)
+    ax.tick_params(axis='x', which='major', labelsize=12)
+    ax.tick_params(axis='y', which='major', labelsize=14)
     plt.text(40, 4e-3, '$n = 1$', fontsize=18)
     plt.text(40, 3e-4, '$n = 10$', fontsize=18)
     plt.text(40, 2e-6, '$n = 100$', fontsize=18)

### 2017-05-07 paper.tex
WIP: Incorporate comments from reviews.

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,letterpaper]{IEEEtran}
 
@@
 \usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
+
+\usepackage[normalem]{ulem}
 
@@
 	}
-	%\IEEEauthorblockA{
-	%    Electrical \& Computer Engineering,
-	%    and the Center for the Neural Basis of Cognition,
-	%    Carnegie Mellon University
-	%    \\
-	%    \IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
-	%    \IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
-	%}
+	\IEEEauthorblockA{
+		\textcolor{red}{Electrical \& Computer Engineering,
+		and the Center for the Neural Basis of Cognition,
+		Carnegie Mellon University}
+		%\\
+		%\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
+		%\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
+	}
 }
@@
 
-To be considered for the 2017 IEEE Jack Keil Wolf ISIT Student Paper Award.
 The ``source localization'' problem is one in which we estimate the location of
@@
 diffuse (blurred) representation of the dipole, as a result of the spatial
-low-pass filtering effect of the different layers of the skull, between the
+low-pass-filtering effect of the different layers of the skull, between the
 brain and scalp.
@@
 lower bounds on the minimax risk for the source localization problem, which
-apply to \emph{all} estimators (biased \emph{and} unbiased), and which captures
+apply to \emph{all} estimators (biased \emph{and} unbiased), and which capture
 how the bound scales with increasing numbers of sensors. Previous lower bounds
@@
 described in detail in Section~\ref{sec:source-localization}).
+\textcolor{red}{While this simplified model makes crucial assumptions (such as
+	shift-invariance) that are invalid in more realistic brain models, we hope
+	that the techniques presented here will pave the way for deriving numerical
+	bounds in more complex settings.}
 
@@
 
-\section{The source localization problem}
+\section{\textcolor{red}{The source localization problem} \textcolor{green}{Source Localization in 1D}}
 \label{sec:source-localization}
 
-We start by giving a detailed description of the one-dimensional setting of the
-source localization problem.
+\textcolor{red}{\sout{We start by giving a detailed description of the one-dimensional setting of the
+source localization problem.}}
 
@@
 We assume that the point source is located on a circle of circumference $S$. We
-use the variable `$s$' to represent a general point on this domain. We can also
-view this domain as a line, on which signals are periodic with period $S$.  The
-point source is therefore located somewhere within one period. We denote the
-set of possible locations by $\Theta = [0, S)$. Due to the periodic nature of
-the domain, a source located at position $\theta \in \Theta$ implies the
-presence of sources at $s = \theta + kS$,~$\forall \, k \in \mathbb Z$.
+use the variable `$s$' (for \emph{s}pace) to represent a general point on this
+domain. We can also view this domain as a line, on which signals are periodic
+with period $S$.  The point source is therefore located somewhere within one
+period. We denote the set of possible locations by $\Theta = [0, S)$.
+\textcolor{red}{\sout{Due to
+the periodic nature of the domain, a source located at position $\theta \in
+\Theta$ implies the presence of sources at $s = \theta + kS$,~$\forall \, k \in
+\mathbb Z$.}}
 
@@
 $(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
-generality we take it to be 0). The periodicity of the space ensures that we
-automatically also have sensors at $S$, $S{+}S/m$,~\dots\@ The lower bounds we
+generality we take it to be 0). \textcolor{red}{\sout{The periodicity of the space ensures that we
+automatically also have sensors at $S$, $S{+}S/m$,~\dots\@}} The lower bounds we
 provide are for \emph{this specific sensor configuration}. For a discussion on
@@
 
-%All ``continuous-space'' signals (analogous to continuous- and
-	%discrete-\emph{time} signals) on the aforementioned circular domain are
-All signals of the form $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$
-is represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
+All ``continuous-space'' signals (analogous to continuous- and
+discrete-\emph{time} signals) on the aforementioned circular domain are of the
+form $f:\Theta\mapsto\mathbb{R}$.  The point source located at $\theta$ is
+represented by the impulse signal, $f(s;\theta) = \delta(s - \theta)$, where
 $\delta(\cdot)$ is the Dirac delta function.  The sensors observe this signal
@@
 More concretely, we assume that the medium is linear and shift-invariant, so
-that it can be represented by a spatial impulse response. Then, blurring would
-correspond to low-pass filtering.  Let this impulse response be given by
-$g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
-pre-sampling) is given by the convolution, $x(s; \theta) = (g*f)(s) = g(s -
-\theta)$. Here, we further make the simplifying assumption that $g(s)$ has a
-sufficiently restricted support, so that aliasing effects are avoided, and
-$x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$ when $\abs{s}
-> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
-(the reason for the factor of $1/2$ will become clear in a later section). For
-the proof, $g(s)$ is also assumed to be Lipschitz continuous with parameter
-$\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \; \forall \;\; u, v
-\in \Theta$.
+that it can be \textcolor{red}{characterized} by a spatial impulse response.
+Then, blurring would correspond to low-pass filtering.  Let this impulse
+response be given by $g(s)$. Then, the noiseless, continuous-space signal
+(post-filtering and pre-sampling) is given by the convolution, $x(s; \theta) =
+(g*f)(s) = g(s - \theta)$. Here, we further make the simplifying assumption
+that $g(s)$ has a sufficiently restricted support, so that aliasing effects are
+avoided, and $x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$
+when $\abs{s} > w/2$, where the ``width'' $w$ of the impulse response satisfies
+$w < S / 2$ (the reason for the extra factor of $1/2$ will become clear in a
+later section). For the proof, $g(s)$ is also assumed to be Lipschitz
+continuous with parameter $\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u
+- v} \; \forall \;\; u, v \in \Theta$.
 
@@
 \end{theorem}
-For a proof of this theorem, we refer the reader to Proposition~13.3
-in~\cite{Duchi2015Information}. Intuitively, Theorem~\ref{thm:est-to-testing}
-says that the error in estimating $\theta_i$ is likely to be large if it is
-difficult to distinguish $\theta_i$ from $\theta_j$, i.e.\ if the probability
-of error is high.
+\textcolor{red}{For a proof of this theorem, we refer the reader
+to~\cite[Sec.~2.2]{Tsybakov2009Introduction}, or
+to~\cite[Prop.~13.3]{Duchi2015Information}}. Intuitively,
+Theorem~\ref{thm:est-to-testing} says that the error in estimating $\theta_i$
+is likely to be large if it is difficult to distinguish $\theta_i$ from
+$\theta_j$, i.e.\ if the probability of error is high.
 
@@
 \end{theorem}
-For a proof, we refer the reader to Proposition~2.11
-in~\cite{Duchi2015Information}. Intuitively, Theorem~\ref{thm:le-cam} states
-that the minimum achievable error probability in a binary hypothesis testing
-problem is related to the distance between the distributions corresponding to
-the two hypotheses.
+\textcolor{red}{For a proof, we refer the reader to~\cite[Thm.~2.2]{Tsybakov2009Introduction},
+or to~\cite[Prop.~2.11]{Duchi2015Information} for a more readable account.}
+Intuitively, Theorem~\ref{thm:le-cam} states that the minimum achievable error
+probability in a binary hypothesis testing problem is related to the distance
+between the distributions corresponding to the two hypotheses.
 
@@
 	\begin{equation*}
-		\mathfrak{M}_n(\mathcal{P}, \Phi\circ\rho) \geq \sup_{0 < \delta < S/4} \frac{\delta^2}{2} \Bigg[1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2}\bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg)} \Bigg]
+		\mathfrak{M}_n(\mathcal{P}, \Phi\circ\rho) \geq \sup_{0 < \delta < \frac{S}{4}} \frac{\delta^2}{2} \Bigg[1 - \sqrt{\frac{2n \kappa^2 \delta^2}{\sigma^2}\bigg(\!\frac{(w{+}2\delta) m}{S} + 1\!\bigg)} \Bigg].
 	\end{equation*}
@@
 While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
-for a large number of sensors, it still gives some important insights. For
-instance, if we assume that sensors have a constant width $c$, then even if we
-view sensors as integrators, the bound tells us something about the scaling of
-error with number of sensors, up to $m = \floor*{\frac{S}{c}}$. Beyond this
-point, averaging noise by increasing the number of trials may help one get to a
-target mean squared error in location. An analytical derivation of the
-trade-off between $m$ and $n$ in achieving a certain target MSE is relegated to
-future work.
+for a large number of sensors, it still gives some important insights.
+\textcolor{red}{\sout{For instance, if we assume that sensors have a constant
+		width $c$, then even if we view sensors as integrators, the bound tells
+		us something about the scaling of error with number of sensors, up to
+		$m = \floor*{\frac{S}{c}}$.} The bound tells us how the error scales
+	with the number of sensors up to $m = \floor*{\frac{S}{c}}$, for sensors of
+	a constant width $c$.} \textcolor{red}{\sout{Beyond this point, averaging
+		noise by increasing the number of trials may help one get to a target
+		mean squared error in location.} Averaging noise over a larger number
+	of trials $n$ may help one achieve a target mean squared error in
+	location}. An analytical derivation of the trade-off between $m$ and $n$ in
+achieving a certain target MSE is relegated to future work.
+\textcolor{red}{Further, more sophisticated techniques for deriving lower bounds, such as Fano's method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.}
 
@@
 one-dimensional circular domain, extensions to a 1D linear domain (of fixed
-length) and to a $d$-dimensional domain (circular or linear) are fairly
+length $S$) and to a $d$-dimensional domain (circular or linear) are fairly
 straightforward, under certain conditions. For a 1D linear domain, we require
@@
 extending to $d$ dimensions, it suffices to apply Assouad's
-Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
-independent 1D problems. Such extensions substantially broaden the number of
-settings in which this bound applies.
+Lemma~\cite[Sec.~2.7.2]{Tsybakov2009Introduction} to separate the problem into
+$d$ independent 1D problems. Such extensions substantially broaden the
+\textcolor{red}{\sout{number of settings in which this bound applies.}
+	application domains where this bound could be useful.}
 
@@
 
+\section*{Acknowledgements}
+
+\textcolor{red}{The authors thank Prof.\ Aarti Singh for her useful comments on
+	a preliminary draft of this paper.}
+\textcolor{blue}{
+This work was supported in part by Systems on Nanoscale Information fabriCs
+(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
+Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
+College of Engineering at Carnegie Mellon University. The authors would like to
+thank Philip and Marsha Dowd for their financial support and encouragement.
+}
+
 %\IEEEtriggeratref{8}
@@
 
-\section*{Acknowledgements}
-
-This work was supported in part by Systems on Nanoscale Information fabriCs
-(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
-Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
-College of Engineering at Carnegie Mellon University. The authors would like to
-thank Philip and Marsha Dowd for their financial support and encouragement.
-
 \appendices
@@
 \label{app:integrator-snr}
+
+\textcolor{red}{[This section needs some proofreading. The main issue here is
+	that as the number of sensors $m$ goes to infinity, the number $k$ should
+	also go to infinity. i.e., what is constant is the location of the sensor,
+	not its ``number''. So we should say something along the lines of ``the SNR
+	of the sensor placed at the point $s_0$, with size determined by the number
+	of sensors, is proportional to $1/m$''.]}
 

### 2017-05-07 paper.tex
Make all edits permanent; fix paper length.

@@
 
+\IEEEoverridecommandlockouts
+
 \title{Lower Bounds on the Minimax Risk for the \\ Source Localization Problem}
@@
 	\IEEEauthorblockA{
-		\textcolor{red}{Electrical \& Computer Engineering,
+		Electrical \& Computer Engineering,
 		and the Center for the Neural Basis of Cognition,
-		Carnegie Mellon University}
+		Carnegie Mellon University
 		%\\
@@
 	}
+	\thanks{This work was supported in part by Systems on Nanoscale
+	Information fabriCs (SONIC), one of the six SRC STARnet Centers, sponsored
+	by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by the Dowd
+	Fellowship from the College of Engineering at Carnegie Mellon University.
+	The authors would like to thank Philip and Marsha Dowd for their financial
+	support and encouragement. The authors thank Prof.\ Aarti Singh for her
+	useful comments on a preliminary draft of this paper.
+	}
+	\vspace{-0.25in}
 }
@@
 source localization problem on a one-dimensional ``circular'' domain (to be
-described in detail in Section~\ref{sec:source-localization}).
-\textcolor{red}{While this simplified model makes crucial assumptions (such as
-	shift-invariance) that are invalid in more realistic brain models, we hope
-	that the techniques presented here will pave the way for deriving numerical
-	bounds in more complex settings.}
+described in detail in Section~\ref{sec:source-localization}).  While this
+simplified model makes crucial assumptions (such as shift-invariance) that are
+invalid in more realistic brain models, we hope that the techniques presented
+here will pave the way for deriving numerical bounds in more complex settings.
 
@@
 Hence, we believe that this paper is the first to give lower bounds on the
-minimax error in estimating the location of a point source, which is observed
-by sensors through a diffusive medium, and corrupted by additive white Gaussian
-noise. We are also the first to analyze the implications physical sensor models
-have on such lower bounds. A simplistic theoretical model might assume that the
-number of sensors can increase unbounded, while maintaining a fixed SNR at each
+minimax error in estimating the location of a point source observed by sensors
+through a diffusive medium, and corrupted by additive white Gaussian noise. We
+are also the first to analyze the implications of physical sensor models on
+such lower bounds. A simplistic theoretical model might assume that the number
+of sensors can increase unbounded, while maintaining a fixed SNR at each
 sensor. We show that this is not physically possible in our setting, and derive
-numerical bounds which have radically different asymptotic behaviour.
+numerical bounds which have very different asymptotic behaviour.
 
 We describe the problem setting in Section~\ref{sec:source-localization} and
-the minimax techniques and our main results (for a na\"ive and then for a more
-physical sensor model) in Section~\ref{sec:minimax-lower-bounds}. We conclude
-in Section~\ref{sec:discussion} with a discussion on the goodness of our
-bounds, and on how our results can be extended to other settings.
+the minimax techniques and our main results in
+Section~\ref{sec:minimax-lower-bounds}. We conclude in
+Section~\ref{sec:discussion} with a discussion on the goodness of our bounds,
+and on possible extensions.
 
@@
 
-\section{\textcolor{red}{The source localization problem} \textcolor{green}{Source Localization in 1D}}
+\section{Source Localization in 1D}
 \label{sec:source-localization}
-
-\textcolor{red}{\sout{We start by giving a detailed description of the one-dimensional setting of the
-source localization problem.}}
 
@@
 period. We denote the set of possible locations by $\Theta = [0, S)$.
-\textcolor{red}{\sout{Due to
-the periodic nature of the domain, a source located at position $\theta \in
-\Theta$ implies the presence of sources at $s = \theta + kS$,~$\forall \, k \in
-\mathbb Z$.}}
 
@@
 $(m{-}1)S/m$ (the offset of the first sensor is arbitrary, so without loss of
-generality we take it to be 0). \textcolor{red}{\sout{The periodicity of the space ensures that we
-automatically also have sensors at $S$, $S{+}S/m$,~\dots\@}} The lower bounds we
-provide are for \emph{this specific sensor configuration}. For a discussion on
-why this configuration might be an appropriate choice in the minimax setting,
-see section~\ref{sec:discussion}.
+generality we take it to be 0). The lower bounds we provide are for \emph{this
+	specific sensor configuration}. For a discussion on why this configuration
+might be an appropriate choice in the minimax setting, see
+section~\ref{sec:discussion}.
 
@@
 More concretely, we assume that the medium is linear and shift-invariant, so
-that it can be \textcolor{red}{characterized} by a spatial impulse response.
-Then, blurring would correspond to low-pass filtering.  Let this impulse
-response be given by $g(s)$. Then, the noiseless, continuous-space signal
-(post-filtering and pre-sampling) is given by the convolution, $x(s; \theta) =
-(g*f)(s) = g(s - \theta)$. Here, we further make the simplifying assumption
-that $g(s)$ has a sufficiently restricted support, so that aliasing effects are
-avoided, and $x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$
-when $\abs{s} > w/2$, where the ``width'' $w$ of the impulse response satisfies
-$w < S / 2$ (the reason for the extra factor of $1/2$ will become clear in a
-later section). For the proof, $g(s)$ is also assumed to be Lipschitz
-continuous with parameter $\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u
-- v} \; \forall \;\; u, v \in \Theta$.
+that it can be characterized by a spatial impulse response.  Then, blurring
+would correspond to low-pass filtering.  Let this impulse response be given by
+$g(s)$. Then, the noiseless, continuous-space signal (post-filtering and
+pre-sampling) is given by the convolution, $x(s; \theta) = (g*f)(s) = g(s -
+\theta)$. Here, we further make the simplifying assumption that $g(s)$ has a
+sufficiently restricted support, so that aliasing effects are avoided, and
+$x(s; \theta)$ is always well-defined. To be precise, $g(s) = 0$ when $\abs{s}
+> w/2$, where the ``width'' $w$ of the impulse response satisfies $w < S / 2$
+(the reason for the extra factor of $1/2$ will become clear in a later
+section). For the proof, $g(s)$ is also assumed to be Lipschitz continuous with
+parameter $\kappa$, i.e., $\abs{g(u) - g(v)} \leq \kappa \abs{u - v} \; \forall
+\;\; u, v \in \Theta$.
 
@@
 	\includegraphics[width=3.2in]{block-diagram}
+	\vspace{-3pt}
 	\caption{A block diagram of the two sensor models described in
@@
 \end{theorem}
-\textcolor{red}{For a proof of this theorem, we refer the reader
+For a proof of this theorem, we refer the reader
 to~\cite[Sec.~2.2]{Tsybakov2009Introduction}, or
-to~\cite[Prop.~13.3]{Duchi2015Information}}. Intuitively,
+to~\cite[Prop.~13.3]{Duchi2015Information}. Intuitively,
 Theorem~\ref{thm:est-to-testing} says that the error in estimating $\theta_i$
@@
 \end{theorem}
-\textcolor{red}{For a proof, we refer the reader to~\cite[Thm.~2.2]{Tsybakov2009Introduction},
-or to~\cite[Prop.~2.11]{Duchi2015Information} for a more readable account.}
+For a proof, we refer the reader to~\cite[Thm.~2.2]{Tsybakov2009Introduction},
+or to~\cite[Prop.~2.11]{Duchi2015Information} for a more readable account.
 Intuitively, Theorem~\ref{thm:le-cam} states that the minimum achievable error
@@
 	\includegraphics[width=2.6in]{overlap-middle-pics}
+	\vspace{-3pt}
 	\caption{Depiction of the continuous-space signals produced by two
@@
 	\includegraphics[width=2.6in]{delta-sampled-pics}
+	\vspace{-3pt}
 	\caption{Plot of the samples of the difference signal, $\Delta(k)$. The
@@
 variation distance for the distributions of interest. Using Pinsker's
-inequality~\cite{Kullback1967Lower} and the convenient tensorization of the
-KL-divergence~\cite{Duchi2015Information}, we see that:
+inequality~\cite[Lemma~2.5]{Tsybakov2009Introduction} and the convenient
+tensorization of the KL-divergence~\cite{Duchi2015Information}, we see that:
 \begin{equation} \label{eq:pinsker-tensorization}
@@
 	\includegraphics[width=2.8in]{lb-vs-m-annotated}
+	\vspace{-3pt}
 	\caption{A numerically generated plot of the lower bound on minimax risk of
@@
 While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
-for a large number of sensors, it still gives some important insights.
-\textcolor{red}{\sout{For instance, if we assume that sensors have a constant
-		width $c$, then even if we view sensors as integrators, the bound tells
-		us something about the scaling of error with number of sensors, up to
-		$m = \floor*{\frac{S}{c}}$.} The bound tells us how the error scales
-	with the number of sensors up to $m = \floor*{\frac{S}{c}}$, for sensors of
-	a constant width $c$.} \textcolor{red}{\sout{Beyond this point, averaging
-		noise by increasing the number of trials may help one get to a target
-		mean squared error in location.} Averaging noise over a larger number
-	of trials $n$ may help one achieve a target mean squared error in
-	location}. An analytical derivation of the trade-off between $m$ and $n$ in
-achieving a certain target MSE is relegated to future work.
-\textcolor{red}{Further, more sophisticated techniques for deriving lower bounds, such as Fano's method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.}
+for a large number of sensors, it still gives some important insights.  The
+bound tells us how the error scales with the number of sensors up to $m =
+\floor*{\frac{S}{c}}$, for sensors of a constant width $c$. Averaging noise
+over a larger number of trials $n$ may help one achieve a target mean squared
+error in location. An analytical derivation of the trade-off between $m$ and
+$n$ in achieving a certain target MSE is relegated to future work. Further,
+more sophisticated techniques for deriving lower bounds, such as Fano's
+method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.
 
@@
 $d$ independent 1D problems. Such extensions substantially broaden the
-\textcolor{red}{\sout{number of settings in which this bound applies.}
-	application domains where this bound could be useful.}
+application domains where this bound could be useful.
 
@@
 
-\section*{Acknowledgements}
+%\section*{Acknowledgments}
 
-\textcolor{red}{The authors thank Prof.\ Aarti Singh for her useful comments on
-	a preliminary draft of this paper.}
-\textcolor{blue}{
-This work was supported in part by Systems on Nanoscale Information fabriCs
-(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
-Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
-College of Engineering at Carnegie Mellon University. The authors would like to
-thank Philip and Marsha Dowd for their financial support and encouragement.
-}
+%This work was supported in part by Systems on Nanoscale Information fabriCs
+%(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
+%Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
+%College of Engineering at Carnegie Mellon University.
+%The authors thank Prof.\ Aarti Singh for her useful comments on a preliminary
+%draft of this paper.
+%The authors would like to thank Philip and Marsha Dowd for their financial
+%support and encouragement.
 
@@
 
-\newpage
+%\newpage
 

### 2017-05-08 paper.tex
WIP: Make Pulkit's edits; remove hyperlinks.

@@
 \usepackage{color}
-\usepackage{url}
-\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
+%\usepackage{url}
+%\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}
 
@@
 	\IEEEauthorblockN{
-		Praveen Venkatesh (\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
-		and Pulkit Grover (\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
+		Praveen Venkatesh (\texttt{vpraveen@cmu.edu}) %(\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
+		and Pulkit Grover (\texttt{pulkit@cmu.edu}) %(\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
 	}
@@
 	}
-	\thanks{This work was supported in part by Systems on Nanoscale
-	Information fabriCs (SONIC), one of the six SRC STARnet Centers, sponsored
-	by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by the Dowd
-	Fellowship from the College of Engineering at Carnegie Mellon University.
-	The authors would like to thank Philip and Marsha Dowd for their financial
-	support and encouragement. The authors thank Prof.\ Aarti Singh for her
-	useful comments on a preliminary draft of this paper.
+	\thanks{
+	\textcolor{red}{The full version of this paper is available online~\cite{FullVersion}.}
+
+	This work was supported in part by NSF CNS-1702694 and by Systems on
+	Nanoscale Information fabriCs (SONIC), one of the six SRC STARnet Centers,
+	sponsored by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by
+	the Dowd Fellowship from the College of Engineering at Carnegie Mellon
+	University.  The authors would like to thank Philip and Marsha Dowd for
+	their financial support and encouragement. The authors thank Prof.\ Anand
+	Sarwate and Prof.\ Aarti Singh for their useful comments.
 	}
@@
 a point source observed through a diffusive medium using an array of sensors.
-
-We give lower bounds on the minimax risk (mean squared-error in location) in
+We obtain lower bounds on the minimax risk (mean squared-error in location) in
 estimating the location of the source, which apply to all estimators, for
 certain classes of diffusive media, when using a uniformly distributed sensor
-array. We show that for sensors of a fixed size, the lower bound decays with
-increasing numbers of sensors. We also analyze a more physical sensor model to
-understand the effect of shrinking the size of sensors as their number
+array. We show that for sensors of a fixed size, the lower bound decays to zero
+with increasing numbers of sensors. We also analyze a more physical sensor
+model to understand the effect of shrinking the size of sensors as their number
 increases to infinity, wherein the bound saturates for large sensor numbers.
@@
 diffuse (blurred) representation of the dipole, as a result of the spatial
-low-pass-filtering effect of the different layers of the skull, between the
+low-pass-filtering effect of the different layers of the head, between the
 brain and scalp.
 
-Recent developments~\cite{Grover2016Information} have suggested that source
-localization can benefit greatly from an increase in sensor density. This
-conclusion is based primarily on a Nyquist rate analysis, and on an
+\textcolor{red}{
+\sout{Recent developments} Our recent work~\cite{Grover2016Information}
+\sout{have suggested} suggests that source localization can benefit greatly
+from an increase in sensor density. \sout{This conclusion is based primarily on
+	a Nyquist rate analysis} Revisiting the Nyquist rate arguments presented
+in~\cite{Nunez2006Electric} revealed that the question of how source imaging
+resolution is affected by sensor density has not been addressed. We argued
+intuitively that under appropriate conditions the right algorithms might be
+able to recover the brain signal with much higher fidelity if more sensors were
+used. To follow up on these intuitive arguments, Grover provides an
 information-theoretic bound~\cite{Grover2016Fundamental} on the accuracy of
-source localization algorithms. This information-theoretic bound, however, was
+source localization algorithms.} This information-theoretic bound, however, was
 derived for the unsampled, continuous-space potential on the scalp, or
-equivalently, in the limit of the number of sensors going to infinity. The
+equivalently, in the limit of the number of sensors going to infinity. \textcolor{red}{\sout{The
 claim that source localization can benefit from increased sensor density is,
-therefore, not fully substantiated by the information-theoretic bound, since
-the latter does not provide a lower bound showing improvement with increasing
-sensor density.
+therefore, not fully substantiated by the information-theoretic bound, since it
+does not provide a lower bound that shows improvement with increasing sensor
+density.} Hence, this bound does not substantiate the claim that source
+localization can benefit from increased sensor density.}
 
+%\textcolor{blue}{[NEW VER.1]
+%Our recent work~\cite{Grover2016Information} has suggested that EEG source
+%localization can benefit greatly from an increase in sensor density. Prior
+%work~\cite{Nunez2006Electric} relied on spatial Nyquist rate analyses to
+%understand what sensor density is required to reconstruct the EEG signal on the
+%\emph{surface of the scalp} to within a given mean squared error.  However,
+%that line of research neglected to describe what sensor density is needed to
+%recover the signal on the \emph{surface of the brain}; this second question
+%also requires an understanding of the noise power spectral density of scalp
+%EEG, which has been little-studied. Hence, it is still unknown what the maximum
+%imaging resolution attainable with a given number of sensors is, and lower
+%bounds providing this understanding do not yet exist.
+%}
+
+%\textcolor{green}{[NEW VER.2]
+%Three questions naturally arise in such a setting: (1) What algorithms for
+%source localization are good? (2) What is the best achievable imaging
+%resolution? (3) How does sensor density affect resolution? The first question
+%has been addressed by a vast literature on source localization
+%algorithms~\cite{Baillet2001Electromagnetic}. The second question calls for
+%lower bounds, of which there is as yet very little
+%understanding~\cite{Grover2016Fundamental,Mosher1993Error}. The question of
+%sensor density has received a lot of attention, but according to us, it still
+%remains an open problem. \cite{Nunez2006Electric} uses Nyquist rate arguments
+%to understand the number of sensors required to reconstruct the EEG signal on
+%the \emph{surface of the scalp} to within a certain MSE. However, they fail to
+%address the more relevant question of the number of sensors needed for
+%\emph{source localization}, i.e., the number of sensors needed to recover the
+%signal on the \emph{surface of the brain}. We show
+%in~\cite{Grover2016Information} that this second question begs an understanding
+%of the spatial noise power spectral density of scalp EEG, and that under
+%appropriate conditions the right algorithms might be able to recover the brain
+%signal with much higher fidelity if more sensors were used.
+%\cite{Grover2016Information} does not, however, provide rigorous lower bounds
+%to substantiate these observations.
+%}
+
+%\textcolor{red}{Recent work by Grover~\cite{Grover2016Fundamental} has sought to provide
+%    analytical lower bounds on the accuracy of source localization algorithms using an information-theoretic method.
+%    but did not provide a lower bound showing if and how this accuracy improves
+%    with increasing sensor density.}
 Earlier work by Mosher et al.~\cite{Mosher1993Error} also gave numerical lower
-bounds on source localization error. However, the Cramer-Rao lower bounds
-derived by them do not apply to biased estimators, including several commonly
-used source localization
+bounds on source localization error, with \emph{some} discussion on sensor
+density. However, the Cramer-Rao lower bounds derived by them do not apply to
+biased estimators, including several commonly used source localization
 algorithms~\cite{Hamalainen1994Interpreting,Lin2006Assessing}.
@@
 source localization problem on a one-dimensional ``circular'' domain (to be
-described in detail in Section~\ref{sec:source-localization}).  While this
-simplified model makes crucial assumptions (such as shift-invariance) that are
-invalid in more realistic brain models, we hope that the techniques presented
-here will pave the way for deriving numerical bounds in more complex settings.
+described in detail in Section~\ref{sec:source-localization}). \textcolor{red}{While this
+simplified model makes crucial assumptions (such as shift-invariance) that do
+not hold in realistic brain models, the techniques presented here extend
+naturally for deriving numerical bounds in more complex settings.}
 
@@
 such lower bounds. A simplistic theoretical model might assume that the number
-of sensors can increase unbounded, while maintaining a fixed SNR at each
-sensor. We show that this is not physically possible in our setting, and derive
-numerical bounds which have very different asymptotic behaviour.
+of sensors can increase without bound, while still maintaining a fixed SNR at
+each sensor. We show that this is non-physical in our setting, and derive
+numerical bounds which have radically different asymptotic behaviour.
 
@@
 more sensors, when we \emph{also} have more trials. This substantiates the
-intuition given in~\cite{Grover2016Information}, which makes this point using a
-Nyquist-rate argument: a larger number of sensors will sample a larger number
-of high-frequency components of the source signal (and hence allow us to locate
-it better), but only if the noise floor is sufficiently low. Noise variance, in
-turn, can be reduced by averaging over multiple trials.
+intuition given in~\cite{Grover2016Information}: a larger number of sensors
+will sample a larger number of high-frequency components of the source signal
+(and hence allow us to locate it better), but only if the noise floor is
+sufficiently low. Noise variance, in turn, can be reduced by averaging over
+multiple trials.
 

### 2017-05-08 paper.tex
Fix link for full version.

@@
 		sensors, $m$, used to estimate the location (code available
-		online~\cite{Code}). The different curves are for different numbers of
-		``trials'', $n$ (number of i.i.d.\ sensor observations). The bound
-		saturates for large $m$, indicating that for a \emph{fixed} number of
-		trials, there is decreasing benefit to using more sensors.  However,
-		the plot suggests that with more trials, the bound saturates at
-		increasingly larger numbers of sensors. Thus, there may be benefit to
-		increasing the number of sensors when you have more trials.}
+		online~\cite{FullVersion}). The different curves are for different
+		numbers of ``trials'', $n$ (number of i.i.d.\ sensor observations). The
+		bound saturates for large $m$, indicating that for a \emph{fixed}
+		number of trials, there is decreasing benefit to using more sensors.
+		However, the plot suggests that with more trials, the bound saturates
+		at increasingly larger numbers of sensors. Thus, there may be benefit
+		to increasing the number of sensors when you have more trials.}
 	\label{fig:numerical}

### 2017-05-08 paper.tex
Mark all edits as permanent.

@@
 \usepackage{mathtools}
-\usepackage{nicefrac}
 \usepackage{array}
@@
 
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
 
@@
 	\thanks{
-	\textcolor{red}{The full version of this paper is available online~\cite{FullVersion}.}
+	The full version of this paper is available online~\cite{FullVersion}.
 
@@
 	}
-	\vspace{-0.25in}
+	%\vspace{-0.25in}
 }
@@
 
-\textcolor{red}{
-\sout{Recent developments} Our recent work~\cite{Grover2016Information}
-\sout{have suggested} suggests that source localization can benefit greatly
-from an increase in sensor density. \sout{This conclusion is based primarily on
-	a Nyquist rate analysis} Revisiting the Nyquist rate arguments presented
-in~\cite{Nunez2006Electric} revealed that the question of how source imaging
-resolution is affected by sensor density has not been addressed. We argued
-intuitively that under appropriate conditions the right algorithms might be
-able to recover the brain signal with much higher fidelity if more sensors were
-used. To follow up on these intuitive arguments, Grover provides an
-information-theoretic bound~\cite{Grover2016Fundamental} on the accuracy of
-source localization algorithms.} This information-theoretic bound, however, was
-derived for the unsampled, continuous-space potential on the scalp, or
-equivalently, in the limit of the number of sensors going to infinity. \textcolor{red}{\sout{The
-claim that source localization can benefit from increased sensor density is,
-therefore, not fully substantiated by the information-theoretic bound, since it
-does not provide a lower bound that shows improvement with increasing sensor
-density.} Hence, this bound does not substantiate the claim that source
-localization can benefit from increased sensor density.}
+Our recent work~\cite{Grover2016Information} suggests that source localization
+can benefit greatly from an increase in sensor density. Revisiting the Nyquist
+rate arguments presented in~\cite{Nunez2006Electric} revealed that the question
+of how source imaging resolution is affected by sensor density has not been
+addressed. We argued intuitively that under appropriate conditions, the right
+algorithms might be able to recover the brain signal with much higher fidelity
+if more sensors were used. To follow up on these intuitive arguments, Grover
+provides an information-theoretic bound~\cite{Grover2016Fundamental} on the
+accuracy of source localization algorithms. This information-theoretic bound,
+however, was derived for the unsampled, continuous-space potential on the
+scalp, or equivalently, in the limit of the number of sensors going to
+infinity. Hence, this bound does not substantiate the claim that source
+localization can benefit from increased sensor density.
 
@@
 source localization problem on a one-dimensional ``circular'' domain (to be
-described in detail in Section~\ref{sec:source-localization}). \textcolor{red}{While this
+described in detail in Section~\ref{sec:source-localization}). While this
 simplified model makes crucial assumptions (such as shift-invariance) that do
 not hold in realistic brain models, the techniques presented here extend
-naturally for deriving numerical bounds in more complex settings.}
+naturally for deriving numerical bounds in more complex settings.
 

### 2017-05-10 paper.tex
Make minor edits; make paper size a4.

@@
-\documentclass[conference,letterpaper]{IEEEtran}
+\documentclass[conference,a4paper]{IEEEtran}
 
@@
 
-For EEG source localization, we hope to find algorithms that achieve scalings
+For EEG source localization, we intend to find algorithms that achieve scalings
 close to the bounds we present.  We also expect to build upon the techniques
@@
 might be an appropriate choice in the minimax setting, see
-section~\ref{sec:discussion}.
+Section~\ref{sec:discussion}.
 
@@
 We consider two sensor models: a simplistic ``point sensor'' model and an
-``integrator sensor'' model, to be used in sections~\ref{sec:lecam-lb}
+``integrator sensor'' model, to be used in Sections~\ref{sec:lecam-lb}
 and~\ref{sec:physical-model} respectively.
@@
 	For a source localization problem as defined in
-	section~\ref{sec:source-localization} under the point sensor model, the
+	Section~\ref{sec:source-localization} under the point sensor model, the
 	minimax risk in estimating the location of a point source is lower bounded
@@
 inequality~\cite[Lemma~2.5]{Tsybakov2009Introduction} and the convenient
-tensorization of the KL-divergence~\cite{Duchi2015Information}, we see that:
+tensorization of the KL-divergence~\cite{Duchi2015Information}, we see that
 \begin{equation} \label{eq:pinsker-tensorization}
-	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1)
+	\norm{P_1^n - P_0^n}_{TV}^2 \leq \frac{1}{2} D_{KL}(P_0^n \Vert P_1^n) = \frac{n}{2} D_{KL}(P_0 \Vert P_1).
 \end{equation}
@@
 \begin{equation} \label{eq:kl-div-normal}
-	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1)
+	D_{KL}(P_0 \Vert P_1) = (\v \mu_0 - \v \mu_1)^T \m \Sigma^{-1} (\v \mu_0 - \v \mu_1),
 \end{equation}
@@
 \mathcal{N}(\v x(\theta_i), \sigma^2 \m I)$, as described in
-section~\ref{sec:sensor-model}. Hence, combining
+Section~\ref{sec:sensor-model}. Hence, combining
 equations~\eqref{eq:le-cam-bound}, \eqref{eq:pinsker-tensorization} and
@@
 \begin{equation} \label{eq:lb-after-pinsker}
-	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg]
+	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{\delta^2}{2} \Bigg[ 1 - \sqrt{ \frac{n}{2\sigma^2} \norm*{\v x(\theta_0) - \v x(\theta_1)}^2 } \Bigg].
 \end{equation}
@@
 where $x(s;\theta_i)$ is the continuous-space filtered signal described in
-section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
+Section~\ref{sec:signal-model}. For an impulse response $g$ which is Lipschitz
 continuous with parameter $\kappa$, we can upper bound the term within the
@@
 note that the two signals $x(s;\theta_0)$ and $x(s;\theta_1)$ overlap at most
-once, since $w < S/2$, as stated in section~\ref{sec:signal-model}.
+once, since $w < S/2$, as stated in Section~\ref{sec:signal-model}.
 
@@
 the lower bound is strictly greater than zero. This indicates that the bound in
-section~\ref{sec:lecam-lb} is failing to capture some effect which leads to
+Section~\ref{sec:lecam-lb} is failing to capture some effect which leads to
 saturation of error as the number of sensors increases.
@@
 This observation motivates the ``integrator sensor'' model defined in
-section~\ref{sec:sensor-model}. With this model, the bounding technique used in
-section~\ref{sec:lecam-lb} no longer easily admits a closed-form solution which
+Section~\ref{sec:sensor-model}. With this model, the bounding technique used in
+Section~\ref{sec:lecam-lb} no longer easily admits a closed-form solution which
 gives a bound for all values of $m$. We instead compute the bound numerically,
@@
 $\theta_1 = 2\delta$.  We compute sensor values for a triangular impulse
-response, by performing numerical integration, and find the best possible
+response by performing numerical integration, and find the best possible
 $\delta$ by grid search.
@@
 		source localization, against the number of uniformly distributed
-		sensors, $m$, used to estimate the location (code available
+		sensors, $m$, following the ``integrator sensor'' model (code available
 		online~\cite{FullVersion}). The different curves are for different
@@
 
-While the lower bound presented in section~\ref{sec:lecam-lb} is non-physical
+While the lower bound presented in Section~\ref{sec:lecam-lb} is non-physical
 for a large number of sensors, it still gives some important insights.  The
@@
 
-While the bounds in section~\ref{sec:lecam-lb} were derived for a
+While the bounds in Section~\ref{sec:lecam-lb} were derived for a
 one-dimensional circular domain, extensions to a 1D linear domain (of fixed
@@
 %$[-w/2, S{+}w/2)$ (for an impulse response with restricted support as described
-%in section~\ref{sec:signal-model}), then the proof for sensor noise would still
+%in Section~\ref{sec:signal-model}), then the proof for sensor noise would still
 %fall through, albeit with slightly different constants.

### 2017-05-10 paper.tex
Fix the bug in the appendix.

@@
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
+\DeclarePairedDelimiter\round{\lfloor}{\rceil}
 
@@
 bound tells us how the error scales with the number of sensors up to $m =
-\floor*{\frac{S}{c}}$, for sensors of a constant width $c$. Averaging noise
-over a larger number of trials $n$ may help one achieve a target mean squared
-error in location. An analytical derivation of the trade-off between $m$ and
-$n$ in achieving a certain target MSE is relegated to future work. Further,
-more sophisticated techniques for deriving lower bounds, such as Fano's
-method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be analyzed.
+\floor*{\frac{S}{c}}$, for sensors of a constant width $c$. Beyond this,
+averaging noise over a larger number of trials $n$ may help one achieve a
+target mean squared error in location. An analytical derivation of the
+trade-off between $m$ and $n$ in achieving a certain target MSE is relegated to
+future work. Further, more sophisticated techniques for deriving lower bounds,
+such as Fano's method~\cite[Sec.~2.7.1]{Tsybakov2009Introduction} are yet to be
+analyzed.
 
@@
 
-\textcolor{red}{[This section needs some proofreading. The main issue here is
-	that as the number of sensors $m$ goes to infinity, the number $k$ should
-	also go to infinity. i.e., what is constant is the location of the sensor,
-	not its ``number''. So we should say something along the lines of ``the SNR
-	of the sensor placed at the point $s_0$, with size determined by the number
-	of sensors, is proportional to $1/m$''.]}
+In the integrator model of sensors defined in Section~\ref{sec:sensor-model},
+recall that the samples are given by equation~\eqref{eq:samples-int-model}.
+Consider a sensor located at the point $s_0 \in [0, S)$ and with a width of
+$S/m$. That is, we assume each of the $m$ sensors occupies the maximum area
+that it can, $1/m$ of the total. As $m$ grows large, the size of each sensor
+must shrink in order to accommodate their larger number.
 
-In the integrator model of sensors, recall that the samples are given by
-equation~\eqref{eq:samples-int-model}. We compute the SNR approximately at the
-$k$-th sensor as follows. The power of the signal is given by
+In order to remain consistent with our previous notation, we first define the
+\emph{index}, $k$, of the sensor located at $s_0$. (Note that as $m$ increases,
+the index $k$ must grow while keeping the position of the sensor fixed, so that
+we're seeing how the SNR changes at the same point).
+\begin{equation}
+	k = \round*{\frac{m s_0}{S}},
+\end{equation}
+where $\round{z}$ is read as ``round of $z$'', denoting the closest integer to
+the point $z \in \mathbb{R}$. Note that as $m$ grows large, $kS/m \to s_0$.
+
+We now compute the approximate SNR of the sensor located at $s_0$ as follows.
+The power of the signal is given by the squared absolute value of the samples,
 \begin{align}
-	\abs{x_k(\theta)}^2 &= \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds\bigg)^2 \\
-	&\approx \bigg(\frac{S}{m} \; x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 = \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \label{eq:signal-power-k},
+	\abs{x_k(\theta)}^2 &= \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds\bigg)^2 \label{eq:int-sensor-power} \\
+	&\overset{(a)}{\approx} \bigg(\frac{S}{m} \; x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \\
+	&\overset{(b)}{\approx} \frac{S^2}{m^2} \big(x(s_0; \theta)\big)^2 \label{eq:signal-power-k},
 \end{align}
-where in the approximation, we have assumed that the signal is roughly constant
-in a small interval, taking the value of the signal at $s = kS/m$. The constant
-itself is not relevant; it suffices to note at this point that the signal power
-diminishes as $1/m^2$ since the sensor size \emph{must} diminish as $1/m$, if
-the number of sensors has to increase to infinity.
+where in approximation (a), we have assumed that the signal is roughly constant
+in the small interval $\big((k{-}\frac{1}{2})S/m, (k{+}\frac{1}{2})S/m\big)$,
+taking the value of the signal at $s = kS/m$. In approximation (b), we make use
+of the fact that for sufficiently large $m$, $kS/m \approx s_0$. Note a key
+step in the power computation: the integrand in
+equation~\eqref{eq:int-sensor-power} is \emph{not} $\abs{x(s; \theta)}^2$,
+because the sensor will average out the signal as a part of its sensing
+process.
 
-The noise variance at the $k$-th sensor is computed similarly:
+Hence, irrespective of the location of the sensor, $s_0$, the signal power
+diminishes as $1/m^2$ since the sensor size \emph{must} diminish at least as
+fast as $1/m$, if the number of sensors has to increase to infinity.
+
+The noise variance of the sensor located at $s_0$ is computed similarly:
 \begin{align}
@@
 
-We can understand how the SNR at the $k$-th sensor scales with $m$, therefore,
-by taking the ratio of~\eqref{eq:signal-power-k} and~\eqref{eq:noise-var-k}
+We can understand how the SNR of the sensor at $s_0$ scales with $m$,
+therefore, by taking the ratio of~\eqref{eq:signal-power-k}
+and~\eqref{eq:noise-var-k}
 \begin{align}
-	\text{SNR}(k) &= \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \cdot \frac{m}{S\sigma^2} \\
-	&= \frac{S}{m\sigma^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \propto 1/m.
+	\text{SNR}(s_0) &= \frac{S^2}{m^2} \big(x(s_0; \theta)\big)^2 \cdot \frac{m}{S\sigma^2} \\
+	&= \frac{S}{m\sigma^2} \big(x(s_0; \theta)\big)^2 \propto \frac{1}{m}.
 \end{align}
 Hence, as the number of sensors $m$ grows to infinity, their sizes must
-necessarily reduce inversely with $m$, and as a result, their SNR also falls
-inversely with $m$, when we view these sensors as integrators.
+necessarily reduce at least as fast as $1/m$, and as a result, their SNR also
+falls at least as fast as $1/m$, when we view these sensors as integrators.
 
